### 2019-12-31 2019_edits/R/fecundity_code/egg_models_2.Rmd
big backup

---
title: "August-ish Manuscript Edits"
author: "Adam A Kemberling"
date: "10/1/2019"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    mathjax: null
editor_options: 
  chunk_output_type: console
---

# Crab Mass x Carapace Width

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      comment = NA, 
                      message = FALSE, 
                      warning = FALSE)
```

```{r}
#Load Packages
library(tidyverse, quietly = TRUE)
library(broom)
library(knitr)
library(here)
library(rnaturalearth)
library(sf)
library(scales)
library(magrittr)
library(statmod)

#Spatial Polygons
usmap <- ne_states(country = "united states of america") %>% 
  st_as_sf() %>% 
  filter(region == "South")
mex <- ne_states(country = "mexico") %>% 
  st_as_sf()

#Load Data

#Egg Data
eggdat <- read_csv(here("data/repo/seamap_summerandfall2017_crabs.csv"), guess_max = 10000, col_types = cols())
eggdat <- eggdat %>% 
  mutate(Egg_stage = factor(eggdat$Egg_stage),
         molt_stage = factor(molt_stage),
         Estimated_fecundity = ifelse(Estimated_fecundity == "#DIV/0!", NA, Estimated_fecundity),
         Estimated_fecundity = as.numeric(Estimated_fecundity))

#Stations
stat_dat <- read_csv(here("data/repo/2017_allcrabs_onerow_withstationdata.csv"), guess_max = 10000, col_types = cols())
eggdat <- stat_dat %>%  
  select(Unique_ID, Agency, STA_TIME, END_TIME,STA_LON, STA_LAT) %>% 
  right_join(eggdat, by = "Unique_ID")

#Regions and Statzones
# Add the statzone using statzone polygon - use this to make regions consistent between models
szones <- read_sf(here("data/gis_files","NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)

# Add a better StatZone ID by spatial overlap with NMFS Zones
eggdat <- eggdat %>% 
  st_as_sf(coords = c("STA_LON", "STA_LAT"), crs = 4326, remove = FALSE) %>% 
  st_join(szones["StatZone"]) %>% 
  st_set_geometry(NULL) %>% 
  as.data.frame() %>% 
  mutate(StatZone = factor(StatZone),
         StatZone = fct_rev(StatZone))

#Regions That are less arbitrary
eggdat <- eggdat %>% 
  mutate(region = ifelse(StatZone %in% seq("21", "18"), "Texas", "Louisiana"),
         region = ifelse(StatZone %in% seq("12", "10"), "MS Bight", region),
         region = ifelse(StatZone %in% seq("1", "9"), "Florida", region),
         region = factor(region),
         #Make bins for egg stage
         es_bins = ifelse(Egg_stage %in% c(1,3), "early", "late"),
         es_bins = ifelse(Egg_stage %in% c(4:6), "middle", es_bins),
         es_bins = factor(es_bins, levels = c("early", "middle", "late"))
  )

#Fix egg volume issue
eggdat <- eggdat %>% 
  mutate(new_vol = (4/3) * pi * ((diam1_mm + diam2_mm) / 4) ^ 3) %>%
  filter(is.na(Egg_stage) == FALSE)

#Write egg data out as final analysis set
write_csv(eggdat, 
          here::here("data", "repo", "analysis_sets", "seamap_repro_eggs.csv"), 
          col_names = TRUE)

#Make a separate DF for just the ovigerous crabs
# #Take the mean value of each egg measurement so theres one value per crab
fecunddat_means <- eggdat %>%
  filter(ovigerous == "yes") %>%
  group_by(Unique_ID) %>%
  summarise(Estimated_fecundity = mean(Estimated_fecundity, na.rm = T),
            egg_volume = mean(new_vol, na.rm = T)) %>%
  ungroup()

#Pull crab specific details and combine
fecunddat <- eggdat %>% 
  filter(ovigerous == "yes") %>% 
  distinct(Unique_ID, .keep_all = TRUE) %>% 
  select(Unique_ID, ovigerous, STA_LON, STA_LAT, Season, region, Crab_weight, Carapace_width, Standard_cw, molt_stage, Eggmass_weight, Egg_stage, Percent_fert, es_bins) %>% 
    left_join(fecunddat_means, by = "Unique_ID")

#Write that out for crab specific means
write_csv(fecunddat, 
          here::here("data", "repo", "analysis_sets", "seamap_repro_eggmass_avg.csv"), 
          col_names = TRUE)

```

## Total Carapace Width

```{r crab condition}

#Total Carapace Width
model_corr <- fecunddat %>% filter(is.na(Carapace_width) == FALSE, is.na(Crab_weight) == FALSE) %$% 
  cor(.$Carapace_width, .$Crab_weight) %>% round(3)

fecunddat %>% 
  ggplot(aes(Carapace_width, Crab_weight)) + 
  geom_point() +
  geom_smooth(method = "glm",
              formula = y~x,
              method.args = list(family = gaussian(link = 'identity')),
              color = "black", linetype = 2) +
  labs(x = "Total Carapace Width", 
       y = "Total Crab Mass (g)") +
  annotate(geom = "text", x = 130, y = 300, label = str_c("Correllation: \n", model_corr))
```

### Fits - Total CW

```{r}
t_cw_mod <- glm(Crab_weight ~ Carapace_width, 
                data = fecunddat, 
                family = gaussian(link = "identity"))

t1 <- qresid(t_cw_mod)
qqnorm(t1)
abline(0, 1, col = "red")

hist(t_cw_mod$residuals, main = "Total Carapace Width Residuals")

```

## Standard Carapace Width

```{r}

# Standard Carapace Width
model_corr <- fecunddat %>% filter(is.na(Standard_cw) == FALSE, is.na(Crab_weight) == FALSE) %$% 
  cor(.$Standard_cw, .$Crab_weight) %>% round(3)

fecunddat %>% 
  ggplot(aes(Standard_cw, Crab_weight)) + 
  geom_point() +
  geom_smooth(method = "glm",
              formula = y~x,
              method.args = list(family = gaussian(link = 'identity')),
              color = "black", linetype = 2) +
  labs(x = "Standard Carapace Width", y = "Total Crab Mass (g)") +
  annotate(geom = "text", x = 100, y = 300, label = str_c("Correllation: \n", model_corr))
```

### Fits - Standard CW

```{r}
s_cw_mod <- glm(Crab_weight ~ Standard_cw, 
                data = fecunddat, 
                family = gaussian(link = "identity"))

t1 <- qresid(s_cw_mod)
qqnorm(t1)
abline(0, 1, col = "red")

hist(s_cw_mod$residuals, main = "Standard Carapace Width Residuals")
```

# Fecundity x crab mass

```{r}

# Standard Carapace Width
model_corr <- fecunddat %>% 
  filter(is.na(Crab_weight) == FALSE, is.na(Estimated_fecundity) == FALSE) %$% 
  cor(.$Crab_weight, .$Estimated_fecundity) %>% round(3)

fecunddat %>% 
  ggplot(aes(Crab_weight, Estimated_fecundity)) + 
  geom_point() +
  geom_smooth(method = "glm",
              formula = y~x,
              method.args = list(family = gaussian(link = 'identity')),
              color = "black", linetype = 2) +
  labs(x = "Crab Weight (w/o eggmass in g)", y = "Estimated Fecundity (Total Eggs)") +
  scale_y_continuous(labels = comma_format()) +
  annotate(geom = "text", x = 130, y = 6250000, label = str_c("Correllation: \n", model_corr))

```

### Fits

```{r}
fecund_weight_mod <- glm(Estimated_fecundity ~ Crab_weight, 
                data = fecunddat, 
                family = gaussian(link = "identity"))

t1 <- qresid(fecund_weight_mod)
qqnorm(t1)
abline(0, 1, col = "red")

hist(fecund_weight_mod$residuals, main = "Fecundity ~ Crab Weight - Residuals")
```

# Fecundity x Carapace Width

## Standard Identity link
```{r, eval = FALSE}

plot_mod <- glm(data = fecunddat, Estimated_fecundity ~ Carapace_width, family = gaussian(link = "identity"))
summary(plot_mod)
```

```{r}
fecunddat %>% 
  ggplot(aes(Carapace_width, Estimated_fecundity)) + 
  geom_point() +
  geom_smooth(method = "glm",
              formula = y~x,
              method.args = list(family = gaussian(link = 'identity')),
              color = "black", linetype = 2) +
  labs(x = "Total Carapace Width (mm)", y = "Estimated Fecundity (Total Eggs)") +
  scale_y_continuous(labels = comma_format()) 
```

### Fits

```{r}
plot_mod <- glm(data = fecunddat, Estimated_fecundity ~ Carapace_width, family = gaussian(link = "identity"))
t1 <- qresid(plot_mod)
qqnorm(t1)
abline(0, 1, col = "red")

hist(plot_mod$residuals, main = "Identity-link residuals")

```

## Log-link

```{r, eval = FALSE}

plot_mod <- glm(data = fecunddat, Estimated_fecundity ~ Carapace_width, family = gaussian(link = "log"))
summary(plot_mod)
```

```{r}
fecunddat %>% 
  ggplot(aes(Carapace_width, Estimated_fecundity)) + 
  geom_point() +
  geom_smooth(method = "glm",
              formula = y~x,
              method.args = list(family = gaussian(link = 'log')),
              color = "black", linetype = 2) +
  labs(x = "Total Carapace Width (mm)", y = "Estimated Fecundity (Total Eggs)") +
  scale_y_continuous(labels = comma_format()) 
```

### Fits

```{r}
plot_mod <- glm(data = fecunddat, Estimated_fecundity ~ Carapace_width, family = gaussian(link = "log"))
t1 <- qresid(plot_mod)
qqnorm(t1)
abline(0, 1, col = "red")

hist(plot_mod$residuals, main = "log-link residuals")

```

# Egg Size x Body Size * Developmental Bins

```{r egg size and carapace width}

library(ggpirate)
fecunddat %>% 
  ggplot(aes(x = es_bins, y = egg_volume, color = egg_volume, fill = egg_volume)) +
  geom_pirate(bars = FALSE) +
  labs(
    x = "Egg Development Stage",
    y = "Egg Volume"
  )
```

### Anova - Egg Development

```{r}
anova_mod <- lm(egg_volume ~ es_bins, data = fecunddat)
anova(anova_mod)
```

### 2019-12-31 2019_edits/R/fecundity_code/eggmodels_markdown.Rmd
big backup

---
title: "Egg Analyses Model Markup"
author: "Adam A Kemberling"
date: "2/4/2019"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    mathjax: null
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE, warning = FALSE)

library(tidyverse, quietly = TRUE)
library(broom)
library(knitr)
library(here)
library(rnaturalearth)
library(sf)
library(scales)

#Mixed Modeling PAckages
library(lme4)
library(afex)
library(broom.mixed)
library(emmeans)

## squash panels together
zero_margin <- theme(panel.spacing=grid::unit(0,"lines")) 
library(lattice)
library(dotwhisker)  ## coefficient plots
library(broom.mixed)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")
conflicted::conflict_prefer("lmer", "lme4")

#Format ggplot for rest of document
theme_set(theme_bw() + theme(panel.grid.major = element_blank(), 
                             panel.grid.minor = element_blank(), 
                             panel.border = element_rect(fill = NA)))

```

# Load and clean data

```{r}
#crabdat <- read_csv("~/Dropbox (The Craboratory)/The Craboratory/Kemberling/SEAMAP_2017/2017_allcrabs_onerow_withstationdata.csv",
# guess_max = 10000, col_types = cols()) 
# eggdat <- read_csv("~/Dropbox (The Craboratory)/The Craboratory/Kemberling/SEAMAP_2017/Reproductive_analysis/seamap_summerandfall2017_crabs.csv", guess_max = 10000, col_types = cols())

crabdat <- read_csv(here("data/repo/2017_allcrabs_onerow_withstationdata.csv"), guess_max = 10000, col_types = cols())
eggdat <- read_csv(here("data/repo/seamap_summerandfall2017_crabs.csv"), guess_max = 10000, col_types = cols())

eggdat <- eggdat %>% 
  mutate(Egg_stage = factor(eggdat$Egg_stage),
         molt_stage = factor(molt_stage),
         Estimated_fecundity = ifelse(Estimated_fecundity == "#DIV/0!", NA, Estimated_fecundity),
         Estimated_fecundity = as.numeric(Estimated_fecundity))

#Zack wants to see if regions matter, so lets add them in now, gonna need the station info data though
#stat_dat <- read_csv("~/Dropbox (The Craboratory)/The Craboratory/Kemberling/SEAMAP_2017/2017_allcrabs_onerow_withstationdata.csv", guess_max = 10000, col_types = cols())

stat_dat <- read_csv(here("data/repo/2017_allcrabs_onerow_withstationdata.csv"), guess_max = 10000, col_types = cols())

# #verify that the unique ID's are the same, they were made in a separate script
# stat_dat$Unique_ID %in% eggdat$Unique_ID
# eggdat$Unique_ID %in% stat_dat$Unique_ID

#Pull the columns we want out, merge them to eggdat by the station info
eggdat <- stat_dat %>%  
  select(Unique_ID, Agency, STA_TIME, END_TIME,STA_LON, STA_LAT) %>% 
  right_join(eggdat, by = "Unique_ID")

```

# Add Regions + Explore Data {.tabset .tabset-fade .tabset-pills}

Regions:

 * S. Texas (Matagorda Bay south)     
 * TX/LA: (between Matagorda Bay and MS River delta)      
 * MS Bight: LA east of MS River, MS, AL     
 * Florida

```{r}

#basemap for reference
#usmap <- map_data("state")

usmap <- ne_states(country = "united states of america") %>% 
  st_as_sf() %>% 
  filter(region == "South")

mex <- ne_states(country = "mexico") %>% 
  st_as_sf()

# Add the statzone using statzone polygon - use this to make regions consistent between models
#szones <- read_sf(here("GIS_objects",  "NMFS_Fishing_Grids_GOM_2013", "NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)
szones <- read_sf(here("data/gis_files","NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)

# Add a better StatZone ID by spatial overlap with NMFS Zones
eggdat <- eggdat %>% 
  st_as_sf(coords = c("STA_LON", "STA_LAT"), crs = 4326, remove = FALSE) %>% 
  st_join(szones["StatZone"]) %>% 
  st_set_geometry(NULL) %>% 
  as.data.frame() %>% 
  mutate(StatZone = factor(StatZone),
         StatZone = fct_rev(StatZone))
```

## Map Stations with Repro Data

```{r}
# #show where they are
# ggplot() + 
#   geom_point(data = eggdat, aes(STA_LON, STA_LAT)) + 
#   geom_sf(data = usmap, fill = "antiquewhite1") + 
#   geom_sf(data = mex, fill = "antiquewhite1") +
#   coord_sf(xlim = c(-80.5, -97.5), ylim = c(24.75, 31)) +
#   labs(x= "", y = "") +
#   theme_minimal() +
#   ggtitle("Raw Data")

# #Make regions
# eggdat <- eggdat %>% 
#   mutate(region = ifelse(STA_LAT < 28.387595 & STA_LON < -96, "South Texas", "TX/LA"),
#          region = ifelse(STA_LON > -89.2, "MS Bight", region),
#          region = ifelse(STA_LON > -87.5, "FL", region),
#          region = factor(region))
# 
# eggdat %>% count(region, StatZone)
# 
# 
# 
# #check by plotting
# ggplot() + 
#   geom_point(data = eggdat, aes(STA_LON, STA_LAT, color = region)) + 
#   geom_sf(data = usmap, fill = "antiquewhite1") + 
#   geom_sf(data = mex, fill = "antiquewhite1") +
#   coord_sf(xlim = c(-80.5, -97.5), ylim = c(24.75, 31)) +
#   labs(x= "", y = "") +
#   theme_minimal() + theme(legend.position = "bottom",
#                           panel.border = element_rect(fill = NA)) +
#   ggtitle("Color by Region")

#Regions That are less arbitrary
eggdat <- eggdat %>% 
  mutate(region = ifelse(StatZone %in% seq("21", "18"), "Texas", "Louisiana"),
         region = ifelse(StatZone %in% seq("12", "10"), "MS Bight", region),
         region = ifelse(StatZone %in% seq("1", "9"), "Florida", region),
         region = factor(region))

#check by plotting
ggplot() + 
  geom_point(data = eggdat, aes(STA_LON, STA_LAT, color = StatZone, shape = region)) + 
  geom_sf(data = usmap, fill = "antiquewhite1") + 
  geom_sf(data = mex, fill = "antiquewhite1") +
  coord_sf(xlim = c(-80.5, -97.5), ylim = c(24.75, 31)) +
  labs(x= "", y = "") +
  theme_minimal() + theme(legend.position = "bottom",
                          panel.border = element_rect(fill = NA)) +
  guides(shape = guide_legend(title = "Region", title.position = "top", title.hjust = 0.5),
         color = guide_legend(title = "Stat Zone", title.position = "top", title.hjust = 0.5)) +
  ggtitle("Sample Regions and Corresponding Stat Zones")

```

***

##  Fix Egg Volume Measurement

I noticed a few crabs had egg sizes that were much higher than others, so going to recalculate the volume from the egg dimensions to compare.

```{r}
#Looks like the calculated volumes might be deviating from 4/3*pi*r^3, so I'm gonna check that here
eggdat <- eggdat %>% 
  mutate(new_vol = (4/3) * pi * ((diam1_mm + diam2_mm) / 4) ^ 3) %>%
  filter(is.na(Egg_stage) == FALSE)

p1 <- eggdat %>% 
  ggplot() + 
  geom_point(aes(egg_volume, new_vol, color = Unique_ID), show.legend = FALSE) +
  ggtitle("Raw volume vs. Corrected")
p1
#plotly::ggplotly(p1)

```

So the excel file on the dropbox has some inconsistencies with the estimated fecundity, and other columns that were drag-down in excel.

The values that appeared much higher have the correct volume calculations, the others have something different.

finish analysis with new_vol.

**Pull Crab Specific Fecundity Details: **

For analyses relating to egg characteristics (egg volume, estimated fecundity), measurements will be the mean value for each crab to avoid dealing with repeated measures.

```{r pull fecundity data}

# #Check to see if hand calculations (Estimated_fecundity) = programatic estimates (mean_fecundity)
# eggdat %>% 
#   filter(ovigerous == "yes") %>% 
#   group_by(Unique_ID) %>% 
#   summarise(mean_fecundity = mean(Estimated_fecundity, na.rm = TRUE),
#             mean_volume    = mean(new_vol, na.rm = TRUE)) %>% 
#   right_join(eggdat, by = "Unique_ID") %>% 
#   select(Unique_ID, Estimated_fecundity, mean_fecundity)

# # We cool, just use Estimated_fecundity, but pull one entry for each crab

# #Take the mean value of each egg measurement so theres one value per crab
fecunddat_means <- eggdat %>%
  filter(ovigerous == "yes") %>%
  group_by(Unique_ID) %>%
  summarise(Estimated_fecundity = mean(Estimated_fecundity, na.rm = T),
            egg_volume = mean(new_vol, na.rm = T)) %>%
  ungroup()

#Pull crab specific details and combine
fecunddat <- eggdat %>% 
  filter(ovigerous == "yes") %>% 
  distinct(Unique_ID, .keep_all = TRUE) %>% 
  select(Unique_ID, ovigerous, STA_LON, STA_LAT, Season, region, Crab_weight, Carapace_width, Standard_cw,                   molt_stage, Eggmass_weight, Egg_stage, Percent_fert) %>%

    left_join(fecunddat_means, by = "Unique_ID")  %>%
  mutate(
    #Make bins for egg stage
    es_bins = ifelse(Egg_stage %in% c(1,3), "early", "late"),
    es_bins = ifelse(Egg_stage %in% c(4:6), "middle", es_bins),
    es_bins = factor(es_bins, levels = c("early", "middle", "late"))
  )

#Fecundity Summary Stats
fecundity_max <-  round(max(fecunddat$Estimated_fecundity) / 1e6, 3)
fecundity_min <-  round(min(fecunddat$Estimated_fecundity) / 1e6, 3)
fecundity_mean <- round(mean(fecunddat$Estimated_fecundity) / 1e6, 3)
fecundity_se <-   round( 
  (sd(fecunddat$Estimated_fecundity) / sqrt(nrow(fecunddat))  / 1e6), 
  3)

```

***

## Exploratory Plots

### 1. egg volume ~ carapace width

```{r}
p1 <- ggplot(eggdat) +
  geom_point(aes(Carapace_width, new_vol, color = Unique_ID), alpha = 0.5, show.legend = FALSE) +
  facet_wrap(~Egg_stage)

p1
#plotly::ggplotly(p1)

```

### 2. Egg Volume ~ Egg Stage

```{r}
eggdat %>% 
  ggplot(aes(Egg_stage, new_vol)) + 
  geom_boxplot() +ylab("Volume mm^3")

```

***

# Estimated Fecundity Models {.tabset .tabset-fade .tabset-pills}

### Fecundity Range :

Estimated fecundity ranged from `r fecundity_min` - `r fecundity_max` million eggs.

With mean fecundity of `r fecundity_mean` +/- `r fecundity_se`  millions of eggs.

## Gaussian w/ identity link

```{r}
#Plot relationships with different link functions
#Gaussian
m1_g <- glm(Estimated_fecundity ~ Carapace_width, data = fecunddat)

fecunddat %>% 
  ggplot(aes(Carapace_width, Estimated_fecundity)) + 
  geom_point() + geom_smooth(method = "glm", 
                             formula = y~x,
                             method.args = list(family = gaussian(link = 'identity'))) +
  scale_y_continuous(labels = comma_format())

tidy(m1_g) %>% kable()

```

***

## Gaussian w/ log link

```{r}
#Log link
m1_log <- glm(Estimated_fecundity ~ Carapace_width, data = fecunddat, family = gaussian(link = "log"))

fecunddat %>% 
  ggplot(aes(Carapace_width, Estimated_fecundity)) + 
  geom_point(color = "gray20") + 
  geom_smooth(method = "glm", 
              formula = y~x,
              method.args = list(family = gaussian(link = 'log')),
              color = "black",
              linetype = 2) +
  scale_y_continuous(labels = comma_format()) +
  #theme_classic() +
  xlab("Carapace Width (mm)") +
  ylab("Estimated Fecundity (Number of Eggs)")

tidy(m1_log) %>% kable()

daic <- round(AIC(m1_g) - AIC(m1_log), 2)

```

Delta AIC for log-link - gaussian models = `r daic`

***

## Region intercepts (ANCOVA)

```{r fecundity ancova}

#Zack wants to see if regions matter, so lets add them in now
m1_ancova <- glm(Estimated_fecundity ~ Carapace_width + region, data = fecunddat, family = gaussian(link = "log"))
#summary(m1)

#Make a prediction dataset to plot them individually
xrange <- seq(min(fecunddat$Carapace_width), max(fecunddat$Carapace_width), by = .1)
# pred.df <- data.frame("Carapace_width" = rep(xrange, 4), 
#                       "region" = c(rep("FL",          length(xrange)),
#                                    rep("MS Bight",    length(xrange)),
#                                    rep("South Texas", length(xrange)),
#                                    rep("TX/LA",       length(xrange)))
# )
# 
# pred.df$fits <- predict(m1, newdata =  pred.df, type = "response")
# ms <- dplyr::filter(pred.df, region == "MS Bight")
# tx <- dplyr::filter(pred.df, region == "South Texas")
# la <- dplyr::filter(pred.df, region == "TX/LA")
# fl <- dplyr::filter(pred.df, region == "FL")

pred.df <- data.frame("Carapace_width" = rep(xrange, 4), 
                      "region" = c(rep("Florida",         length(xrange)),
                                   rep("MS Bight",        length(xrange)),
                                   rep("Texas",           length(xrange)),
                                   rep("Louisiana",       length(xrange)))
)

pred.df$fits <- predict(m1_ancova, newdata =  pred.df, type = "response")
ms <- dplyr::filter(pred.df, region == "MS Bight")
tx <- dplyr::filter(pred.df, region == "Texas")
la <- dplyr::filter(pred.df, region == "Louisiana")
fl <- dplyr::filter(pred.df, region == "Florida")

# #That was a yuge pain
# p1 <- ggplot() +
#   geom_point(data = fecunddat, aes(Carapace_width, Estimated_fecundity)) +
#   geom_line(data = fl, aes(Carapace_width, fits, color = "FL", group = 1)) +
#   geom_line(data = ms, aes(Carapace_width, fits, color = "Ms Bight", group = 1)) +
#   geom_line(data = tx, aes(Carapace_width, fits, color = "South Texas", group = 1)) +
#   geom_line(data = la, aes(Carapace_width, fits, color = "TX/LA", group = 1))  +
#   theme_classic() +
#   xlab("Carapace Width (mm)") +
#   ylab("Estimated Fecundity (Number of Eggs)")
# 
# p1

#That was a yuge pain
p1 <- ggplot() +
  geom_point(data = fecunddat, aes(Carapace_width, Estimated_fecundity)) +
  geom_smooth(data = fecunddat,
              aes(Carapace_width, Estimated_fecundity),
              method = "glm",
              formula = y~x,
              method.args = list(family = gaussian(link = 'log')),
              color = "black",
              linetype = 2) +
  scale_y_continuous(labels = comma_format()) +
  geom_line(data = fl, aes(Carapace_width, fits, color = "Florida", group = 1)) +
  geom_line(data = ms, aes(Carapace_width, fits, color = "MS Bight", group = 1)) +
  geom_line(data = tx, aes(Carapace_width, fits, color = "Texas", group = 1)) +
  geom_line(data = la, aes(Carapace_width, fits, color = "Louisiana", group = 1))  +
  theme_classic() + theme(legend.title = element_blank()) +
  xlab("Carapace Width (mm)") +
  ylab("Estimated Fecundity (Number of Eggs)")

p1

tidy(m1_ancova) %>% kable()

```

***

## Carapace width region interaction

If we include region in the model we get kind of a weird result, that being that carapace width is no longer significant:

```{r fecundity interaction}
m1_r <- glm(Estimated_fecundity ~ Carapace_width * region, 
          data = fecunddat,
          family = gaussian(link = "log"))

#and plot
fecunddat %>% 
  ggplot(aes(Carapace_width, Estimated_fecundity,)) + 
  geom_point(aes(color = region)) + 
  geom_smooth(method = "glm", 
              formula = y ~ x,
              method.args = list(family = gaussian(link = 'log')),
              color = "black",
              linetype = 2) +
  scale_y_continuous(labels = comma_format()) +
  facet_wrap(~region) +
  theme_classic() + theme(legend.title = element_blank()) +
  xlab("Carapace Width (mm)") +
  ylab("Estimated Fecundity (Number of Eggs)")

tidy(m1_r) %>% kable()

```

Which is confusing because its pretty clear on its own.

***

## Carapace Width & Season

Check Season as well just to be sure.

```{r}
m1_s <- glm(Estimated_fecundity ~ Carapace_width + Season, 
          data = fecunddat,
          family = gaussian(link = "log"))

#Prediction dataframe
pred.df <- data.frame("Carapace_width" = rep(xrange, 4), 
                      "Season" = c(rep("Summer", length(xrange)),
                                   rep("Fall",   length(xrange)))
)

pred.df$fits <- predict(m1_s, newdata =  pred.df, type = "response")
summer <- dplyr::filter(pred.df, Season == "Summer")
fall <-   dplyr::filter(pred.df, Season == "Fall")

#That was a yuge pain
p1 <- ggplot() +
  geom_point(data = fecunddat, aes(Carapace_width, Estimated_fecundity)) +
  geom_line(data = summer, aes(Carapace_width, fits, color = "Summer", group = 1)) +
  geom_line(data = fall,   aes(Carapace_width, fits, color = "Fall", group = 1)) + 
  scale_y_continuous(labels = comma_format()) +
  theme_classic() + theme(legend.title = element_blank()) +
  xlab("Carapace Width (mm)") +
  ylab("Estimated Fecundity (Number of Eggs)")

p1

tidy(m1_s) %>% kable()

```

## Model Comparison Table

```{r}
#Comparison Table
summ.table <- do.call(rbind, lapply(list(m1_g, m1_log, m1_ancova, m1_r), broom::glance))

table.cols <- c("df.residual", "deviance", "AIC")
reported.table <- summ.table[table.cols]
names(reported.table) <- c("Resid. Df", "Resid. Dev", "AIC")

reported.table[['dAIC']] <-  with(reported.table, AIC - min(AIC))
reported.table[['weight']] <- with(reported.table, exp(- 0.5 * dAIC) / sum(exp(- 0.5 * dAIC)))
reported.table$AIC <- NULL
reported.table$weight <- round(reported.table$weight, 2)
reported.table$dAIC <- round(reported.table$dAIC, 1)
row.names(reported.table) <- c("base : Gaussian", "base : Log-link", "region : no interaction", "region : interaction")

reported.table %>% 
  arrange(dAIC) %>% 
  kable()
```

# Egg size models {.tabset .tabset-fade .tabset-pills}

## Investigate Seasons  - individual eggs

(if we have fall egg sizes), we do **not** have enough (n = 5)

We also have repeated measures for measurements on each egg mass, so gonna have the eggmass/crabID as a random effect as they are likely correlated. Otherwise we could use the average egg measurements for each crab.

```{r}
p1 <- ggplot(eggdat) +
  geom_point(aes(Carapace_width, new_vol, color = Season), alpha = 0.5, show.legend = FALSE) +
  #facet_grid(Egg_stage ~ Season) +
  labs(
    x = "Carapace Width",
    y = "Egg Volume (mm^3)"
  )

p1
#plotly::ggplotly(p1)

```

***

## GLM - individual eggs

```{r}
m1 <- lm(new_vol ~ Carapace_width, data = eggdat)

ggplot(eggdat, aes(x = Carapace_width, y = new_vol)) +
  #facet_wrap(~Unique_ID, nrow = 5) +
  geom_point() +
  theme_classic() +
  geom_hline(yintercept = mean(eggdat$new_vol), linetype = 2, 
             aes(color = "Overall Mean")) + 
  geom_smooth(data = eggdat, 
              aes(x = Carapace_width, y = new_vol, group = 1), 
              method = "glm") +
  scale_color_manual(#name = "",
                     values = c("Overall Mean"     = "gray")) +
  labs(
    x = "Carapace Width (mm)",
    y = "Egg Volume",
    title = "Base Model"
    )

#Model Results
tidy(m1) %>% kable()

#qqplots
qqnorm(resid(m1))
qqline(resid(m1))
```

***

## GLM - eggmass means

```{r}
m1 <- lm(egg_volume ~ Carapace_width, data = fecunddat)

ggplot(fecunddat, aes(x = Carapace_width, y = egg_volume)) +
  #facet_wrap(~Unique_ID, nrow = 5) +
  geom_point() +
  theme_classic() +
  geom_hline(yintercept = mean(eggdat$new_vol), linetype = 2, 
             aes(color = "Overall Mean")) + 
  geom_smooth(data = eggdat, 
              aes(x = Carapace_width, y = new_vol, group = 1), 
              method = "glm") +
  scale_color_manual(#name = "",
                     values = c("Overall Mean"     = "gray")) +
  labs(
    x = "Carapace Width (mm)",
    y = "Egg Volume",
    title = "Base Model"
    )

#Model Results
tidy(m1) %>% kable()

```

***

## Mixed Model - individual eggs

```{r, warning = FALSE, message = FALSE}

#guide: http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#model-specification

# Carapace width plus unique id intercept
m2 <- lme4::lmer(new_vol ~ Carapace_width + (1 | Unique_ID), data = eggdat)

#summary(m2)

# # Confidence intervals
# confint(m2)

# # Random Effects
# lme4::ranef(m2)

#Variance Partitioning - From summary(m2)
re_var <- 2.904e-06
resid_var_total <- 2.904e-06 + 1.000e-06 #Total residual variance *AFTER* Fixed effects
re_varpart <- re_var / resid_var_total * 100

#Fixed Effects Plot
(fe_plot <- ggplot(eggdat, aes(x = Carapace_width, y = new_vol)) +
  #facet_wrap(~Unique_ID, nrow = 5) +
  geom_point() +
  theme_classic() +
  geom_hline(yintercept = mean(eggdat$new_vol), linetype = 2,
             aes(color = "Overall Mean")) + 
  geom_smooth(data = eggdat, 
              aes(x = Carapace_width, y = new_vol, group = 1), 
              method = "glm") +
  geom_point(data = cbind(eggdat, pred = predict(m2)), 
             aes(y = pred, color = "Individual Means"), 
             size = 2) +
  scale_color_manual(name = "",
                     values = c("Individual Means" = "red",
                                "Overall Mean"     = "gray")
                     ) +
  theme(legend.position = "right") +
  labs(
    x = "Carapace Width (mm)",
    y = "Egg Volume",
    title = "Overall Effect"
    )   
  )

#Model Results
tidy(m2) %>% kable() #not significant

# #Save this code for other MEM ****
# #Random Effects Plot - No line because single x value for each one
# (mm_plot <- ggplot(eggdat, aes(x = Carapace_width, y = new_vol)) +
#   facet_wrap(~Unique_ID, nrow = 5) +
#   geom_point() +
#   theme_classic() +
#   geom_line(data = cbind(eggdat, pred = predict(m2)), aes(y = pred)) +
#   theme(legend.position = "none") +
#   labs(
#     x = "Carapace Width (mm)",
#     y = "Egg Volume",
#     title = "Individual - Level Effect"
#     ) +
#     zero_margin
#   )

```

### Mixed Model Diagnostics

```{r}
# Diagnostics

#qqplots
qqnorm(resid(m2))
qqline(resid(m2))
```

```{r, fig.height=8}
# tt <- tidy(m2, effects="ran_vals")
# ggplot(tt,aes(level,estimate))+
#     geom_pointrange(aes(ymin=estimate-1.96*std.error,
#                         ymax=estimate+1.96*std.error))+
#     coord_flip()

# #Fitted vs. residuals + qq
# plot(m2)
# qqmath(m2)

# #group residuals
# plot(m2, Unique_ID ~ resid(.))

# #can also use augment from broom + ggplot
# aa <- broom.mixed::augment(m2)
# ggplot(aa, aes(Unique_ID, .resid)) +
#   geom_boxplot() + 
#   coord_flip()

# #Plot random effects to look for outliers:
# dotplot(ranef(m2, condVar=TRUE))

#or again with ggplot arranged in ascending order
tt <- tidy(m2, effects = "ran_vals") %>% 
  arrange(estimate) %>% 
  mutate(level = fct_inorder(level) #Order by ascending estimate
         # , 
         # significance = if_else(between(0, 
         #                               estimate - 1.96 * std.error, 
         #                               estimate + 1.96 * std.error),
         #                       "Not Significant",
         #                       "Significant")
         )

tt$significance <- NA

for (i in 1:nrow(tt)) {
  tt$significance[i] <- if_else(between(0, 
                                       tt$estimate[i] - 1.96 * tt$std.error[i],
                                       tt$estimate[i] + 1.96 * tt$std.error[i]),
                               "Not Significant",
                               "Significant")

}

ggplot(tt, aes(level, estimate))+
  geom_hline(yintercept = 0, linetype = 2, color = "navy", alpha = 0.5) +
  geom_pointrange(aes(ymin = estimate - 1.96 * std.error,
                      ymax = estimate + 1.96 * std.error,
                      alpha = significance)) + 
  scale_alpha_manual("", values = c("Significant" = 1,
                                    "Not Significant" = 0.3)) +

  coord_flip()

# #Use merTools to plot interval estimates
# library(merTools)
# merTools::plotREsim(REsim(m2))  # plot the interval estimates
```

### Mixed Model Inference

```{r}

####  Inference

#coefficient Plot
dwplot(m2) + geom_vline( xintercept = 0, lty = 2)

#P-values - 
library("lmerTest")
lmer2R <- lmer(new_vol ~ Carapace_width + (1 | Unique_ID), data = eggdat)
detach("package:lmerTest")

#Now get p=values with summary
#summary(lmer2R) #default uses the Satterthwaite approximation to the degrees of freedom. You can

#also use

#summary(lmer2R, ddf="Kenward-Roger") #for Kenward-roger which are more accurrate, take longer
#They are the same here

#Here are the type II (sequential) ANOVA results:
anova(lmer2R) #done withlmerTest gives you denominator DF
#anova(m2)     #regular lmer does not

#afex mixed can also be used to get the kenward-roger p-value
#afex::mixed(new_vol ~ Carapace_width + (1 | Unique_ID), data = eggdat)

#### Testing random effect
#If we want to test the random effect, we would in principle remove the random effect and test with anova, '

m1 <- glm(new_vol ~ Carapace_width, data = eggdat)
anova(m2, m1)

```

### Variance Explained By Random Effect

This is the variance explained after the fixed effects : `r round(re_varpart, 2)`

***

## Egg size ~ CW * region  - eggmass mean

Plot the overall relationship first

```{r}
# #Individual eggs
# eggdat %>% 
#   ggplot(aes(Carapace_width, new_vol)) +
#   geom_point(aes(color = region)) +
#   geom_smooth(method = "glm",
#               formula = y~x,
#               method.args = list(family = gaussian(link = 'identity'))) +
#   labs(
#     x = "Carapace Width",
#     y = "Egg Volume (mm^3)"
#   )

#mean eggmass values
fecunddat %>% 
  ggplot(aes(Carapace_width, egg_volume)) +
  geom_point(aes(color = region)) +
  geom_smooth(method = "glm",
              formula = y~x,
              method.args = list(family = gaussian(link = 'identity'))) +
  labs(
    x = "Carapace Width",
    y = "Egg Volume (mm^3)"
  )
```

Region seems to have a viable impact, but it may just look that way because of an interaction effect with egg size.

```{r}
# #individual eggs
# eggdat %>% #facet region and egg stage
#   ggplot(aes(Carapace_width, new_vol)) +
#   geom_point(aes(color = Egg_stage), show.legend = FALSE) +
#   facet_grid(region ~ Egg_stage) +
#   theme(axis.text.x = element_text(angle = 90)) +
#   labs(
#     x = "Carapace Width",
#     y = "Egg Volume (mm^3)"
#   )

fecunddat %>% #facet region and egg stage
  ggplot(aes(Carapace_width, egg_volume)) +
  geom_point(aes(color = Egg_stage), show.legend = FALSE) +
  facet_grid(region ~ Egg_stage) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Carapace Width",
    y = "Egg Volume (mm^3)"
  )

```

I don't think we will be able to tease this out with so many combinations with no data unless we re-bin into more general groups or drop regions like florida.

When you look at the interactions you get this mess:

```{r}
# m1 <- glm(new_vol ~ Carapace_width + Egg_stage * region, 
#           data = eggdat,
#           family = gaussian(link = "identity"))

m1 <- glm(egg_volume ~ Carapace_width + Egg_stage * region, 
          data = fecunddat,
          family = gaussian(link = "identity"))

tidy(m1) %>% kable()
```

***

## Egg Stage Bins

### Egg Volume ~ Egg Bins

```{r}

fecunddat %>% #facet region and egg stage
  ggplot(aes(Carapace_width, egg_volume)) +
  geom_point(aes(color = Egg_stage), show.legend = FALSE) +
  facet_grid(region ~ es_bins) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Carapace Width",
    y = "Egg Volume (mm^3)"
  )

fecunddat %>% 
  ggplot(aes(es_bins, egg_volume)) +
  geom_boxplot() +
  labs(
    x = "Egg Development Stage",
    y = "Egg Volume (mm^3)"
  )

anova1 <- lm(egg_volume ~ es_bins, data = fecunddat) 
summary(anova1)
# anova1 <- aov(egg_volume ~ es_bins, data = fecunddat) 
# tidy(anova1) %>% kable()

```

### Egg Volume ~ Region + Egg Bins

```{r}

fecunddat %>% 
  ggplot(aes(Carapace_width, egg_volume)) +
  geom_point(aes(color = es_bins)) +
  geom_smooth(method = "glm",
              formula = y~x,
              method.args = list(family = gaussian(link = 'identity'))) +
  facet_wrap(~region) +
  labs(
    x = "Carapace Width",
    y = "Egg Volume (mm^3)"
  ) + theme_minimal() + zero_margin

```

## Mean Egg Volume GLM - Final

 * Carapace Width     
 * Region (not enough sampling)      
 * Season

```{r}
ggplot(fecunddat, aes(Carapace_width, egg_volume)) +
  geom_point(aes(color = es_bins)) +
  geom_smooth(method = "glm") +
  facet_wrap(~es_bins)

m1 <- glm(egg_volume ~ Carapace_width * es_bins, data = fecunddat)
tidy(m1) %>% kable()

```

***

# Percent development Models

## Percent developing normally ~ molt stage

This one is nice and cut-and-dry, just an ANOVA to test the group differences.

```{r}
fecunddat %>% 
  ggplot(aes(molt_stage, Percent_fert)) +
  geom_boxplot(aes(color = molt_stage))

anova1 <- lm(Percent_fert ~ molt_stage, data = fecunddat)
summary(anova1)
#anova1 <- aov(Percent_fert ~ molt_stage, data = fecunddat)
#tidy(anova1) %>% kable()

```

Groups are unbalanced, and it throws a warning, but we're probably ok.

```{r}
fecunddat %>% count(molt_stage) %>% kable()
```

***

## Percent developing normally ~ Egg stage

```{r}
fecunddat %>% 
  ggplot(aes(fct_rev(es_bins), Percent_fert)) +
  #geom_jitter(aes(color = region), height = 0, width = 0.1) + 
  #geom_boxplot(aes(color = region)) + 
  geom_boxplot(aes(color = es_bins)) + 
  #coord_flip() +
  ylim(c(0,1)) +
  labs(
    x = "Egg Stage",
    y = "% Fertilized"
  )

anova1 <- lm(Percent_fert ~ es_bins, data = fecunddat)
summary(anova1)
#tidy(anova1) %>% kable()

```

***

## Percent developing normally ~ region

```{r}
fecunddat %>% 
  ggplot(aes(region, Percent_fert)) +
  #geom_jitter(aes(color = region), height = 0.1, width = 0.1)
  geom_boxplot(aes(color = region))

anova1 <- lm(Percent_fert ~ region, data = fecunddat)
summary(anova1)
#tidy(anova1) %>% kable()

```

***

## Percent Development - All

This is a two-way crossed ANOVA comparing percent fertilization between egg stage bins and region with interactions.

```{r}

fecunddat %>% 
  ggplot(aes(es_bins, Percent_fert)) +
  #geom_jitter(aes(color = region), height = 0.1, width = 0.1)
  geom_boxplot(aes(color = es_bins)) +
  facet_wrap(~region) +
  labs(caption = "Too much going on...")

fecunddat %>% 
  group_by(region, es_bins) %>% 
  summarise(n = n(),
            mean_fert = mean(Percent_fert))

# anova1 <- aov(Percent_fert ~ region * es_bins * molt_stage, data = fecunddat)
# tidy(anova1) %>% kable()

anova1 <- lm(Percent_fert ~ region * es_bins, data = fecunddat)
summary(anova1)
#tidy(anova1) %>% kable()

```

***

### 2019-12-31 2017_scrap/Offshore_mods/DistOffshore_DataExplo.R

@@ -1,0 +1,191 @@
+#Phase 2 of seamap data wrangle
+#bring in clean data and set it up for analyses, perform analyses
+library(tidyverse)
+
+#raw catch info and trawl info before merge
+catch <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_catchdata.csv')
+trawl.info <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_trawlinfo.csv')
+
+#all the data together
+seamap <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_sapidus_consolidation_2018.csv')
+
+
+####################  rename things  ####################
+names(seamap)
+seamap <- seamap %>% rename(CTD_Depth = DEPTH_EMAX,
+                  Temp_S = TEMPSURF,
+                  Temp_B = TEMPMAX,
+                  Salinity_S = SALSURF,
+                  Salinity_B = SALMAX,
+                  DO_S = OXYSURF,
+                  DO_B = OXYMAX,
+                  Chlor_S = CHLORSURF,
+                  Chlor_B = CHLORMAX,
+                  Turb_S = TURBSURF,
+                  Turb_B = TURBMAX,
+                  Start_Lat = DECSLAT,
+                  Start_Long = DECSLON,
+                  End_Lat = DECELAT,
+                  End_Long = DECELON,
+                  Start_Depth = DEPTH_SSTA,
+                  End_Depth = DEPTH_ESTA,
+                  Survey_Year = YR,
+                  Date = MO_DAY_YR)
+
+
+###################  Restrict to just 40ft trawls  #############
+seamap <- seamap %>% filter(GEAR_TYPE %in% c("ST","FT"),
+                            GEAR_SIZE %in% c(20,40)) #20 and 40ft.
+
+#still have 2017
+
+seamap$Start_Lat <- as.numeric(as.character(seamap$Start_Lat)); seamap$Start_Long <- as.numeric(as.character(seamap$Start_Long))
+seamap <- seamap[complete.cases(seamap$Start_Long),]
+seamap <- seamap[complete.cases(seamap$Start_Lat),]
+
+#coordinate references
[…]

### 2019-12-31 2017_scrap/Offshore_mods/Seamap_Data_Wrangle.R

@@ -1,0 +1,147 @@
+#SEAMAP DATA WRANGLING, August 2018
+#Adam A. Kemberling
+
+#Packages
+library(maps)
+library(sp)
+library(mapproj)
+library(raster)
+library(gstat)
+library(gdistance)
+library(rgdal)
+library(rgeos)
+library(sf)
+library(tidyverse)
+
+
+#Data import, data uploaded from GSMFC February 2018
+BGSREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/BGSREC.csv")
+ENVREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/ENVREC.csv")
+CRUISES <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/CRUISES.csv") 
+STAREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/STAREC.csv")
+INVREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/INVREC.csv")
+# GLFREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/GLFREC.csv")  #GLFREC has SEX of catch
+
+# #Data Cleanup, GLFREC has weight and length info of individuals
+# names(GLFREC)
+# GLFREC <- GLFREC %>% filter(SPEC_GLF == "SAPIDU")
+
+
+#Cruise/Survey Info
+names(CRUISES) #cruise ID, Year, Survey Title, Data collector
+CRUISES <- CRUISES %>% dplyr::select(CRUISEID, YR, TITLE, SOURCE)
+
+
+#Trawl info
+names(STAREC) #Station ID, Cruise ID, MM/DD/YY, Start Lat, Start Lon, End Lat, End Lon, Vessel Speed, start depth, end depth
+STAREC <- STAREC %>% dplyr::select(STATIONID, CRUISEID, MO_DAY_YR, STAT_ZONE, FAUN_ZONE, DECSLAT, DECSLON, DECELAT, DECELON, VESSEL_SPD, DEPTH_SSTA, DEPTH_ESTA)
+
+
+#Tow time and gear type
+names(INVREC)
+INVREC <- INVREC[,c("STATIONID","GEAR_SIZE","GEAR_TYPE","MESH_SIZE","MIN_FISH")]
+tail(INVREC)
+
+
+#Join cruise information with station vessel speed and depth
[…]

### 2019-12-31 2017_scrap/Offshore_mods/greta_crab_IOA.R

@@ -1,0 +1,233 @@
+############
+#Bayesian estimation of indices of abundance using JAGS/GRETA
+#8/30/2018
+
+#packages
+#library(greta)
+library(DiagrammeR)
+library(bayesplot)
+library(ggplot2)
+library(MASS)
+library(R2jags)
+library(tidyverse)
+
+
+#read in data
+seamap <- read_csv("~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_cpue_2018.csv")
+
+#Set up Season Column
+seamap[str_detect(seamap$TITLE, "Fall"),"Season"] <- "Fall"
+seamap[str_detect(seamap$TITLE, "Winter"),"Season"] <- "Winter"
+seamap[str_detect(seamap$TITLE, "Summer"),"Season"] <- "Summer"
+
+#Order stat zones west to east
+#Make presence absence column
+#Make numeric survey year column
+#Make seasons a factor
+#Make month column
+#Filter out stat zones that are NA
+seamap <- seamap %>% 
+  mutate(STAT_ZONE = factor(STAT_ZONE, levels = c(22:11)),
+         Crab_presence = ifelse(Sapidus_Catch > 0, 1, 0),
+         Survey_Year = as.numeric(Survey_Year),
+         Season = factor(Season, levels = c("Summer","Fall","Winter")),
+         Survey_Month = lubridate::month(Date),
+         Survey_Month = factor(Survey_Month)) %>% 
+  filter(!is.na(STAT_ZONE), STAT_ZONE != "NA")
+
+#going to look from Destin West
+seamap <- seamap %>% filter(Start_Long < -86.16607)
+
+#diagnosing crazy high cpue
+seamap <- seamap %>% filter(Spd_kmh != 0)  #these are infinite cpue
+
+#Make positive catch only subset
+crabs <- filter(seamap, Crab_presence == 1) #positive catch subset
+
+
+########  Seamap test model  ############
+
+seamap %>% filter(CPUE_towspd > 100) %>% dplyr::select(Sapidus_Catch, MIN_FISH, Spd_kmh)  #these are probably similis, can't make that call objectively
+seamap %>% filter(Sapidus_Catch > 0) %>% ggplot(aes(Start_Depth, CPUE_towspd)) + geom_point() + geom_smooth(method = "lm")
[…]

### 2019-12-31 2019_edits/R/fecundity_code/bayesian_fecundity.R

@@ -1,0 +1,448 @@
+
+################################### Set up and run in bayesian ###################################
+# set WD to location where post.summ function exists
+# session > set working disrectory > To project location
+
+#load packages
+library(R2OpenBUGS)
+library(rjags)
+library(coda)
+
+source("L:/Dropbox (The Craboratory)/The Craboratory/Kemberling/Rwork/reproductive_analysis/Repro_analysis/post_summ_function.R")
+
+
+#read and prepare data
+#seamap reproductive analyses
+repros <- read.csv("L:/Dropbox (The Craboratory)/The Craboratory/Kemberling/SEAMAP_2017/Reproductive_analysis/seamap_frozencrabs.csv")
+
+head(repros)
+sapply(repros, class)
+
+#select by unique ID for one row per crab, top rows contain the mean egg diameters and mean egg volumes
+repros <- repros[!duplicated(repros$Unique_ID),]
+#write.csv(repros,"L:/Dropbox (The Craboratory)/The Craboratory/Kemberling/SEAMAP_2017/Reproductive_analysis/seamap_onerow.csv")
+
+eggs <- repros[which(repros$ovigerous == 'yes'),]
+eggs$Estimated_fecundity <- as.numeric(as.character(eggs$Estimated_fecundity))
+noeggs <- repros[which(repros$ovigerous != 'no'),]
+
+eggs$Estimated_fecundity <- eggs$Estimated_fecundity/1e+06
+
+
+
+eggs[which(eggs$Estimated_fecundity < 2),]
+
+#only using eggs for any fecundity analysis
+dat <- eggs
+head(dat); tail(dat)
+
+# start with fecundity and carapace width
+#check classes
+sapply(dat, class)
+
+plot(Estimated_fecundity ~ Carapace_width, data = dat)
+pred.x <- seq(min(dat$Carapace_width), max(dat$Carapace_width), length = 30)
+
+
+
+
+
+########################## Making Jags List ################################
+
+# compile data into a list to pass to BUGS
+jags.dat = list(n.obs = nrow(dat), y = dat$Estimated_fecundity, x1 = dat$Carapace_width, 
[…]

### 2019-12-31 2019_edits/R/fecundity_code/egg_analyses_2.R

@@ -1,0 +1,296 @@
+#New analyses to add
+#This script has been transferred to eggmodels_markdown, newest updates are there
+
+"Analyses I’d like to add:
+Egg size ~ CW*season (if we have fall egg sizes)
+Egg size ~ CW*region (depending on if we got ovig crabs from all regions
+Fecundity ~ CW*region
+	Regions:  	S. Texas (Matagorda Bay south)
+			TX/LA: (between Matagorda Bay and MS River delta)
+			MS Bight: LA east of MS River, MS, AL
+			Florida
+Percent developing normally ~ molt stage
+"
+
+library(tidyverse, quietly = TRUE)
+library(broom)
+library(here)
+library(rnaturalearth)
+library(sf)
+
+#Here is the crab data, one row per crab
+#crabdat <- read_csv("~/Dropbox (The Craboratory)/The Craboratory/Kemberling/SEAMAP_2017/2017_allcrabs_onerow_withstationdata.csv", guess_max = 10000, col_types = cols())
+crabdat <- read_csv(here("data/repo/2017_allcrabs_onerow_withstationdata.csv"), guess_max = 10000, col_types = cols())
+
+#Or the data pre processed with a row for each egg measurement
+#eggdat <- read_csv("~/Dropbox (The Craboratory)/The Craboratory/Kemberling/SEAMAP_2017/Reproductive_analysis/seamap_summerandfall2017_crabs.csv", guess_max = 10000, col_types = cols())
+eggdat <- read_csv(here("data/repo/seamap_summerandfall2017_crabs.csv"), guess_max = 10000, col_types = cols())
+eggdat <- eggdat %>% 
+  mutate(Egg_stage = factor(eggdat$Egg_stage),
+         molt_stage = factor(molt_stage)
+         )
+
+#######################  Model 1 -  Estimated Fecundity non-bayesian ###################
+
+
+#Some quick formatting
+eggdat <- eggdat %>% 
+  mutate(Estimated_fecundity = ifelse(Estimated_fecundity == "#DIV/0!", NA, Estimated_fecundity),
+         Estimated_fecundity = as.numeric(Estimated_fecundity))
+
+#Zack wants to see if regions matter, so lets add them in now, gonna need the station info data though
[…]

### 2019-12-31 2019_edits/R/fecundity_code/hierarchical_size_at_maturity.R

@@ -1,0 +1,234 @@
+############################################################################################
+######################Length at Maturity Hierarchical model C. sapidus######################
+############################################################################################
+setwd("L:/Dropbox (The Craboratory)/The Craboratory/Kemberling/Rwork/reproductive_analysis/Repro_analysis")
+# clear the workspace
+rm(list = ls(all = T))
+
+# load packages
+library(R2OpenBUGS)
+library(rjags)
+library(coda)
+library(lubridate)
+library(chron)
+
+source("L:/Dropbox (The Craboratory)/The Craboratory/Kemberling/Rwork/reproductive_analysis/Repro_analysis/post_summ_function.R")
+#Bring in Data
+
+#raw tagging
+#tag <- read_excel("~/Dropbox (The Craboratory)/The Craboratory/craboratory_shared/tagging/tagging_data_master.xlsx")
+
+#or after cleanup for most up to date data
+#tag <- read.csv(paste("~/Dropbox (The Craboratory)/The Craboratory/Kemberling/TaggingCSV/R_troubleshoot/tags_",Sys.Date(),".csv",sep = ""))
+
+#9-14 final data
+tag <- read.csv('L:/Dropbox (The Craboratory)/The Craboratory/Kemberling/TaggingCSV/Final_Data/tagging_final_2017-09-14.csv')
+
+
+dat <- tag[,c('date','cw','Tag_state')]
+dat$cw <- as.numeric(as.character(dat$cw))
+dat <- dat[!is.na(dat$cw),] #get rid of NA rows
+class(dat$date)
+dat$date <- as.Date(dat$date, "%m/%d/%Y")
+dat$year <- year(dat$date)
+hist(dat$year)
+dat$year <- (dat$year - 2016) +1
+dat$state <- as.factor(dat$Tag_state)
+dat <- dat[which(dat$Tag_state != '0'),]
+dat$state <- as.numeric(as.factor(dat$state))
+
+##### MODEL 2, STATE SPECIFIC, GULF MEAN #####
+
+####Put it in a list to send to jags####
+#pred.x = seq(3, 6, 0.5)
+
[…]

### 2019-12-31 2019_edits/R/fecundity_code/post_summ_function.R

@@ -1,0 +1,115 @@
+# Posterior Summary for Requested Parameters
+
+# AUTHOR: BEN STATON
+# DATE: 8/7/17
+
+# This function allows you to pull out single variables by name from a mcmc.list and plot if desired
+  # post.samp: an object of class 'mcmc.list'
+  # var: the variable you wish to view
+  # do.post: logical. Return the whole posterior along with summary? Default is FALSE
+  # do.plot: logical. Plot the posterior and trace plots? Default is FALSE
+
+post.summ = function(post.samp, var, do.post = F, do.plot = F){
+  require(coda)
+  
+  if (!is.mcmc.list(post.samp)) stop("post.samp is not of class mcmc.list")
+  
+  #coerce to matrix
+  nchains = length(post.samp)
+  post.samp = as.matrix(post.samp)
+
+  # 1.) EXTRACT AND SUMMARIZE POSTERIOR SAMPLES
+  if (substr(var, nchar(var), nchar(var)) == "[") { # if the parameter has subscripts
+    post = post.samp[,substr(colnames(post.samp), 1, nchar(var)) == var]
+    post.est = apply(post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))
+  } else { # if the parameter doesn't have subscripts
+    post = post.samp[,var] 
+    post.est = c(mean = mean(post), sd = sd(post), quantile(post, c(0.5, 0.025, 0.975)))
+  } 
+
+  # IF PLOTTING MCMC DIAGNOSTICS
+  if (do.plot) {
+    
+    if (is.matrix(post)) { # if the extracted posterior has multiple parameters
+      # number of iterations per chain
+      n.iterations = nrow(post)/nchains
+      
+      windows(record = T)
+      par(mfrow = c(4,2), mar = c(2, 2, 1.5, 1.5), oma = c(1,1,1,1))
+      
+      # split the posterior into chains
+      chain = list()
+      chain[[1]] = post[1:n.iterations,]
+      for(i in 2:nchains){
+        chain[[i]] = post[(((i-1) * n.iterations)+1) : (n.iterations * i),]
+      }
+      
+      # calculate the max density for each parameter, for ylim in density plot
+      max.dens = matrix(NA, nrow = nchains, ncol = ncol(post))
+      for(j in 1:nchains){
+        for(i in 1:ncol(post)){
[…]

### 2019-12-31 2019_edits/R/gsmfc_digging/sex_ratios.R

@@ -1,0 +1,110 @@
+# Getting to Sex Ratios from GSMFC data
+
+#Load Packages
+library(here)
+library(tidyverse)
+library(readxl)
+library(odbc)
+library(dbplyr)
+library(ggridges)
+
+name_match <- function(df1, df2) {names(df1)[which(names(df1) %in% names(df2))]}
+
+#Load and format data
+mycon <- dbConnect(odbc::odbc(),
+                   DBQ = here("data/ms_access_db", "public_seamap.mdb"),
+                   Driver = "{Microsoft Access Driver (*.mdb, *.accdb)};")
+
+# # To disconnect database :
+# dbDisconnect(mycon)
+
+
+# Catch Data
+bgsrec <- tbl(mycon, "BGSREC") %>% collect() %>%  rename_all(tolower)
+bgsrec <- bgsrec %>% rename(biocode = bio_bgs)
+
+# Cruise Data
+cruises <- tbl(mycon, "CRUISES") %>% collect() %>% rename_all(tolower)
+cruises <- cruises %>%
+  select(vessel, cruiseid, cruise_no,  yr, title, source) %>% 
+  filter(str_detect(tolower(title), "groundfish"), 
+         str_detect(tolower(title), "fall") | str_detect(tolower(title), "summer"))
+
+# Indv. Measurements
+glfrec <- tbl(mycon, "GLFREC") %>% collect() %>% rename_all(tolower)
+glfrec <- glfrec %>% 
+  select(vessel,
+         cruise_no,
+         stationid,
+         p_sta_no,
+         biocode = bio_glf,
+         indvl_wt,
+         meas_cd = meascd_glf,
+         indvl_len = len_glf,
+         indvl_sex = sex_glf)
+
+
+new_biocodes <- tbl(mycon, "NEWBIOCODESBIG") %>% collect() %>% rename_all(tolower)
+new_biocodes <- new_biocodes %>% select(
+  biocode = code,
+  taxonomic,
+  common_name
+)
+
+
+name_match(bgsrec, new_biocodes)
+bgsrec <- left_join(bgsrec, new_biocodes, by = "biocode")
+
+
+
+
+####  Make merges  ####
+name_match(glfrec, bgsrec)
+bgs_glf <- bgsrec %>% full_join(glfrec, by = c("vessel", "cruise_no",  "stationid", "p_sta_no", "biocode")) %>% 
[…]

### 2019-12-31 2019_edits/R/mapping/GOM_equal_area_crs.R

@@ -1,0 +1,26 @@
+#### Coordinate Reference System for GOM Equal Area  ####
+
+library(sf)
+library(tidyverse)
+
+# Working with custom CRS for Gulf of Mexico
+
+
+# found a resource fo4r selecting a crs for gulf oil spill work, pretty relevant to this work*
+# for more details on naming crs objects go here https://proj4.org/operations/projections/aea.html
+gulf_crs <- "+proj=aea +lat_1=23.000000 +lat_2=28.000000 +x_0=1200000.000000 +units=km"
+# proj=aea : projection equals albers equal area
+# lat_1    : first standard parallel = 23N
+# lat_2    : second standard parallel = 28N
+# x_0      : false easting
+# units    : units = km
+
+
+#Load a wgs1984 geographic coordinate system shapefile
+usa_poly <- usa_adam <- read_sf("Y:/GIS Files/GIS shapefiles/Gulf of Mexico/gom_states.shp") %>% 
+  st_set_crs(4326)
+
+
+
+# Transform to our albers equal area projection
+usa_poly_km <- st_transform(usa_poly, gulf_crs)

### 2019-12-31 2019_edits/R/mapping/rnaturalearth_vignette.R

@@ -1,0 +1,122 @@
+
+
+#R Natural Earth Data Mapping
+#From : https://cran.r-project.org/web/packages/rnaturalearth/vignettes/rnaturalearth.html
+
+#install.packages("rnaturalearth")
+#install.packages(rnaturalearth)
+
+#load necessary packages
+library(rnaturalearth)
+library(sp)
+library(sf)
+library(tidyverse)
+
+
+# world at small scale (low resolution)
+sp::plot(ne_countries(type = 'countries', scale = 'small'))
+
+
+# countries, UK undivided
+sp::plot(ne_countries(country = 'united kingdom', type='countries'))
+
+# map_units, UK divided into England, Scotland, Wales and Northern Ireland
+sp::plot(ne_countries(country = 'united kingdom', type='map_units'))
+
+# countries, small scale
+sp::plot(ne_countries(country = 'united kingdom', scale = 'small'))   
+
+# countries, medium scale
+sp::plot(ne_countries(country = 'united kingdom', scale = 'medium'))
+
+# countries, large scale
+sp::plot(ne_countries(country = 'united kingdom', scale = 'large'))
+
+# states country='united kingdom'
+sp::plot(ne_states(country = 'united kingdom'))  
+# states geounit='england'
+sp::plot(ne_states(geounit = 'england')) 
+
+# states country='france'
+sp::plot(ne_states(country = 'france'))
+
+
+# coastline of the world
+# subsetting of coastline is not possible because the Natural Earth data are not attributed in that way
+sp::plot(ne_coastline())
+
+
+
+
+####  Applying the vignette to Gulf of Mexico Study area  ####
+
+#Loading them in stores them as SpatialPolygonsDataFrame
+usa <- ne_states(country = "united states of america")
+plot(usa)
+
+#convert to sf
+usa_sf <- st_as_sf(usa)
+ggplot() +
+  geom_sf(data = usa_sf, aes(fill = region))
+
+#Pull out Southern States
+us_south <- usa_sf %>% filter(region == "South")
+ggplot() +
+  geom_sf(data = us_south, aes(fill = name), show.legend = FALSE)
+
+
+#Grab Mexico
+mexico <- ne_states(country = "mexico")
+plot(mexico)
+
+#convert to sf
+mex_sf <- st_as_sf(mexico)
+ggplot() +
[…]

### 2019-12-31 2019_edits/R/mapping/tags_spatial_bins.R

@@ -1,0 +1,94 @@
+# Aggregating Tagging Coverage for NOAA final report Maps
+# 10/17/2019
+
+
+#Packages
+library(tidyverse)
+library(here)
+library(sf)
+library(rnaturalearth)
+library(gridExtra)
+
+#Data
+tagging <- read_csv(here("data", "noaa_report", "tags_clean_final.csv"))
+recaps <- read_csv(here("data", "noaa_report", "tags_recaps_clean_final.csv"))
+usa_poly <- ne_states("united states of america") %>% st_as_sf() %>% filter(region == "South")
+mexico_poly <- ne_states("mexico") %>% st_as_sf()
+
+#Reduce resolution and then group by lat/long coordinates, count the rows for each for number tagged
+tag_bins <- tagging %>% 
+  mutate(long_decdeg = round(long_decdeg, 2),
+         lat_decdeg  = round(lat_decdeg, 2)) %>%
+  group_by(long_decdeg, lat_decdeg) %>% 
+  summarise(n_tagged = n()) %>% 
+  st_as_sf(coords = c("long_decdeg", "lat_decdeg"), crs = 4326)
+
+
+ggplot() +
+  geom_sf(data = usa_poly) +
+  geom_sf(data = tag_bins, aes(size = n_tagged), color = "royalblue", fill = "royalblue", alpha = 0.6) + 
+  coord_sf(xlim = c(-97.5, -82.5), ylim = c(25.8, 30.8)) +
+  theme_bw() + 
+  ggtitle("Rounded to 2-digit(s)")
+
+
+#Will want to do custom bins and shape sizes and add them to the dataframe  
+
+
+
+#Side-by-side comparison
+no_agg <- tagging %>% 
+    filter(between(long_decdeg, left = -91.2, right = -89)) %>% 
+    st_as_sf(coords = c("long_decdeg", "lat_decdeg"), crs = 4326) %>% 
+    ggplot() +
+    geom_sf(data = usa_poly) +
+    geom_sf(color = "royalblue", fill = "royalblue", alpha = 0.6) + 
+    coord_sf(xlim = c(-91.2, -89), ylim = c(29, 30.5)) +
+    theme_bw() + theme(legend.position = "bottom") +
+    ggtitle("Original Data")
+
+
+
+agg_plot <- ggplot() +
[…]

### 2019-12-31 Bernoulli_Jags.R

@@ -1,119 +1,0 @@
-#### SEAMAP JAGS Bernoulli & Gamma model code
-library(tidyverse)
-library(lattice)
-library(R2jags)
-source("~/Dropbox (The Craboratory)/The Craboratory/Kemberling/Rwork/Zuur_books/Zuuretal_2016_ZIM_AllData/MCMCSupportHighstatV4.R")
-
-seamap <- read_csv("SEAMAP_model_ready.csv")
-
-
-#Jags Model Setup
-
-############## sample model matrices, and jags.dat prep ######
-seamap.test <- seamap %>% filter(Survey_Year > 2000) #try one year to start
-MyStd <- function(x) { (x - mean(x)) / sd(x)} #Standardizaton function
-
-# Define 0-1 data
-seamap.test$Crab_presence <- as.numeric(seamap.test$Crab_presence)
-
-# Step 1: Standardize any continuous covariates & format factors
-#seamap$temp.std <- MyStd(seamap$Temp)
-seamap.test$Survey_Year <- factor(seamap.test$Survey_Year)
-seamap.test$Survey_Month <- factor(seamap.test$Survey_Month)
-seamap.test$STAT_ZONE <- factor(seamap.test$STAT_ZONE , levels = c(22:11))
-
-# Step 2: Prepare data for JAGS
-X <- model.matrix( ~ 1 + Survey_Year + Survey_Month + STAT_ZONE, 
-                   data = seamap.test)
-K    <- ncol(X)
-
-JAGS.data <- list(Y = seamap.test$Crab_presence,  #Response
-                  X = X,                          #Covariates
-                  K = K,                          #Number of betas
-                  N = nrow(seamap.test)           #Sample size
-)                 
-
-JAGS.data
-
-####  Not Run -- What I thought we'd need to do with random effects  ####
-#I0    <- as.numeric(seamap.test$Crab_presence)
-#re1    <- as.numeric(as.factor(seamap.test$STAT_ZONE))
-#NumRE1 <- length(unique(seamap.test$STAT_ZONE))
-#re2    <- as.numeric(as.factor(seamap.test$Survey_Month))
-#NumRE2 <- length(unique(seamap.test$Season))
-# 
-# 
-# ######## Jags data ####
-# JAGS.data <- list(Y = seamap.test$CPUE_towspd,  #Response
-#                   Xc = Xc,                      #Covariates
[…]

### 2019-12-31 R_scripts/Offshore_mods/DistOffshore_DataExplo.R

@@ -1,191 +1,0 @@
-#Phase 2 of seamap data wrangle
-#bring in clean data and set it up for analyses, perform analyses
-library(tidyverse)
-
-#raw catch info and trawl info before merge
-catch <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_catchdata.csv')
-trawl.info <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_trawlinfo.csv')
-
-#all the data together
-seamap <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_sapidus_consolidation_2018.csv')
-
-
-####################  rename things  ####################
-names(seamap)
-seamap <- seamap %>% rename(CTD_Depth = DEPTH_EMAX,
-                  Temp_S = TEMPSURF,
-                  Temp_B = TEMPMAX,
-                  Salinity_S = SALSURF,
-                  Salinity_B = SALMAX,
-                  DO_S = OXYSURF,
-                  DO_B = OXYMAX,
-                  Chlor_S = CHLORSURF,
-                  Chlor_B = CHLORMAX,
-                  Turb_S = TURBSURF,
-                  Turb_B = TURBMAX,
-                  Start_Lat = DECSLAT,
-                  Start_Long = DECSLON,
-                  End_Lat = DECELAT,
-                  End_Long = DECELON,
-                  Start_Depth = DEPTH_SSTA,
-                  End_Depth = DEPTH_ESTA,
-                  Survey_Year = YR,
-                  Date = MO_DAY_YR)
-
-
-###################  Restrict to just 40ft trawls  #############
-seamap <- seamap %>% filter(GEAR_TYPE %in% c("ST","FT"),
-                            GEAR_SIZE %in% c(20,40)) #20 and 40ft.
-
-#still have 2017
-
-seamap$Start_Lat <- as.numeric(as.character(seamap$Start_Lat)); seamap$Start_Long <- as.numeric(as.character(seamap$Start_Long))
-seamap <- seamap[complete.cases(seamap$Start_Long),]
-seamap <- seamap[complete.cases(seamap$Start_Lat),]
-
-#coordinate references
[…]

### 2019-12-31 R_scripts/Offshore_mods/Seamap_Data_Wrangle.R

@@ -1,147 +1,0 @@
-#SEAMAP DATA WRANGLING, August 2018
-#Adam A. Kemberling
-
-#Packages
-library(maps)
-library(sp)
-library(mapproj)
-library(raster)
-library(gstat)
-library(gdistance)
-library(rgdal)
-library(rgeos)
-library(sf)
-library(tidyverse)
-
-
-#Data import, data uploaded from GSMFC February 2018
-BGSREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/BGSREC.csv")
-ENVREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/ENVREC.csv")
-CRUISES <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/CRUISES.csv") 
-STAREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/STAREC.csv")
-INVREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/INVREC.csv")
-# GLFREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/GLFREC.csv")  #GLFREC has SEX of catch
-
-# #Data Cleanup, GLFREC has weight and length info of individuals
-# names(GLFREC)
-# GLFREC <- GLFREC %>% filter(SPEC_GLF == "SAPIDU")
-
-
-#Cruise/Survey Info
-names(CRUISES) #cruise ID, Year, Survey Title, Data collector
-CRUISES <- CRUISES %>% dplyr::select(CRUISEID, YR, TITLE, SOURCE)
-
-
-#Trawl info
-names(STAREC) #Station ID, Cruise ID, MM/DD/YY, Start Lat, Start Lon, End Lat, End Lon, Vessel Speed, start depth, end depth
-STAREC <- STAREC %>% dplyr::select(STATIONID, CRUISEID, MO_DAY_YR, STAT_ZONE, FAUN_ZONE, DECSLAT, DECSLON, DECELAT, DECELON, VESSEL_SPD, DEPTH_SSTA, DEPTH_ESTA)
-
-
-#Tow time and gear type
-names(INVREC)
-INVREC <- INVREC[,c("STATIONID","GEAR_SIZE","GEAR_TYPE","MESH_SIZE","MIN_FISH")]
-tail(INVREC)
-
-
-#Join cruise information with station vessel speed and depth
[…]

### 2019-12-31 R_scripts/Offshore_mods/greta_crab_IOA.R

@@ -1,233 +1,0 @@
-############
-#Bayesian estimation of indices of abundance using JAGS/GRETA
-#8/30/2018
-
-#packages
-#library(greta)
-library(DiagrammeR)
-library(bayesplot)
-library(ggplot2)
-library(MASS)
-library(R2jags)
-library(tidyverse)
-
-
-#read in data
-seamap <- read_csv("~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_cpue_2018.csv")
-
-#Set up Season Column
-seamap[str_detect(seamap$TITLE, "Fall"),"Season"] <- "Fall"
-seamap[str_detect(seamap$TITLE, "Winter"),"Season"] <- "Winter"
-seamap[str_detect(seamap$TITLE, "Summer"),"Season"] <- "Summer"
-
-#Order stat zones west to east
-#Make presence absence column
-#Make numeric survey year column
-#Make seasons a factor
-#Make month column
-#Filter out stat zones that are NA
-seamap <- seamap %>% 
-  mutate(STAT_ZONE = factor(STAT_ZONE, levels = c(22:11)),
-         Crab_presence = ifelse(Sapidus_Catch > 0, 1, 0),
-         Survey_Year = as.numeric(Survey_Year),
-         Season = factor(Season, levels = c("Summer","Fall","Winter")),
-         Survey_Month = lubridate::month(Date),
-         Survey_Month = factor(Survey_Month)) %>% 
-  filter(!is.na(STAT_ZONE), STAT_ZONE != "NA")
-
-#going to look from Destin West
-seamap <- seamap %>% filter(Start_Long < -86.16607)
-
-#diagnosing crazy high cpue
-seamap <- seamap %>% filter(Spd_kmh != 0)  #these are infinite cpue
-
-#Make positive catch only subset
-crabs <- filter(seamap, Crab_presence == 1) #positive catch subset
-
-
-########  Seamap test model  ############
-
-seamap %>% filter(CPUE_towspd > 100) %>% dplyr::select(Sapidus_Catch, MIN_FISH, Spd_kmh)  #these are probably similis, can't make that call objectively
-seamap %>% filter(Sapidus_Catch > 0) %>% ggplot(aes(Start_Depth, CPUE_towspd)) + geom_point() + geom_smooth(method = "lm")
[…]

### 2019-12-31 2019_edits/R/offshore_analyses/IOA_report.Rmd
renaming and file movement

---
title: "Offshore Indices of Abundance for <br/> Blue Crabs"
author: "Adam A Kemberling"
date: "2/19/2019"
output: 
  html_document:
    toc: true
    toc_float: true
    mathjax: null
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#packages
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(gridExtra)
library(broom)
library(statmod)
library(rnaturalearth)
library(sf)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")

#Format ggplot for rest of document
theme_set(theme_bw() + theme(panel.grid.major = element_blank(), 
                             panel.grid.minor = element_blank(), 
                             panel.border = element_rect(fill = NA)))

`%not in%` <- purrr::negate(`%in%`)
```

# Data Used in this report

**Large-scale filtering**

Data used to create these indices were taken from the [GSMFC website](seamap.gsmfc.com) in March of 2019. Data was then limited to 40 ft trawls, and any tows with no operation codes (indicating a bad station) or an op code of "W" (water tow, aka no catch but otherwise fine). Data was also limited to summer and fall groundfish cruises specifically. Stations with no Stat zone or tow speed records were also removed.

A survey design change ocurred in 2008 between the summer and fall groundfish surveys. This change expanded the area sampling into Florida waters, an area previously unsampled, and changed from a dapth stratified sampling design where multiple tows longer than 30min were common. The new (current) sampling design covers the entire Gulf from Brownsville TX to the Florida Keyes, and each station consists of a single 30 minute tow.

It was recommended to me by the analyst group at the Pascagoula Laboratory to use groundfish data from 2010* forward for consistency as the design change was not uniformly applied until then, with some state partners sampling differently.

# Additional filters from data exploration

Based on exploration of the data, and in the interest of looking at Gulfwide or atleast East/West trends several additional filters were added. Data was limited to years after 2009 for consistency in the sampling methods and for a Gulfwide coverage. Additionally statzones 0 (not a real zone), 1 (The Keyes), 12 (MS Sound, inside Chandy), and 22 (Brownsville/MX) were not included due to a lack of observations. Stat zones 6 & 9 were also excluded from the model, as they have no observed *C. sapidus* catch for the timeseries and thus have no expected catch.

There was an initial concern with abnormally high catch values being potential mis-identifications. This is less of a concern with the reduced time-series

```{r}
# Read in data
#seamap <- read_csv(here("data_processed/gsmfc_processed", "seamap_cpue_2019.csv"),
seamap <- read_csv(here("data/offshore", "seamap_cpue_2019.csv"),
                   guess_max = 1e6, 
                   col_types = cols())

#Set up Season Column, using survey titles
seamap[str_detect(seamap$TITLE, "Fall"),"Season"] <- "Fall"
seamap[str_detect(seamap$TITLE, "Winter"),"Season"] <- "Winter"
seamap[str_detect(seamap$TITLE, "Summer"),"Season"] <- "Summer"
seamap[str_detect(seamap$TITLE, "Spring"),"Season"] <- "Spring"

# Make any setup changes
seamap <- seamap %>% 
  mutate(STAT_ZONE     = factor(STAT_ZONE),
         Crab_presence = ifelse(Sapidus_Catch > 0, 1, 0),
         Survey_Year   = as.numeric(Survey_Year),
         Season        = factor(Season, levels = c("Summer","Fall","Winter")),
         Survey_Month  = lubridate::month(Date),
         Survey_Month  = factor(Survey_Month),
         Survey_design = ifelse(Survey_Year < 2009, "Original", "Updated"),
         Survey_design = ifelse(Survey_Year == 2008 & Season == "Fall", "Updated", Survey_design),
         Survey_design = factor(Survey_design, levels = c("Original", "Updated")),
         ####  More changes from DE
         Year_f             =  factor(Survey_Year),
         Month_f            =  factor(Survey_Month),
         Depth              =  (Start_Depth + End_Depth)/2,
         Temp_std           =  (Temp_B- mean(Temp_B))/ mean(Temp_B),
         Salinity_std       =  (Salinity_B- mean(Salinity_B))/ mean(Salinity_B),
         Depth_std          =  (Depth- mean(Depth))/ mean(Depth))

# Do all filtering
seamap <- seamap %>% 
  filter(#is.na(STAT_ZONE)  ==  FALSE, 
         #STAT_ZONE         !=  "NA",
         Season            !=  "Winter",
         Survey_Year     %in%  c(2009:2018),
         #STAT_ZONE   %not in%  c(0, 1, 22, 12),      #Not enough Obs
         #STAT_ZONE   %not in%  c(6,9),
         Spd_kmh           !=  0,                    #these are infinite cpue
         Depth             <=  110
         )

# Should we remove catch outliers?
seamap %>% 
  mutate(`Outlier Status` = ifelse(Sapidus_Catch > 80, "Large Outlier", "Plausible Catch"),
         `Outlier Status` = ifelse(Sapidus_Catch <= 25, "No Concern", `Outlier Status`),
         `Outlier Status` = factor(`Outlier Status`, levels = c("No Concern", "Plausible Catch", "Large Outlier"))) %>% 
  ggplot() + 
    geom_point(aes(x = Year_f, y = Sapidus_Catch, color = `Outlier Status`)) +
    scale_color_manual(values = c("gray", "orange", "darkred")) +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
    xlab("") + ylab("C. sapidus Catch")

#Look at catch only
crabs <- seamap %>% filter(Sapidus_Catch > 0)

crabs %>% 
  filter(Survey_Year >= 2009) %>% 
  mutate(STAT_ZONE = fct_rev(STAT_ZONE)) %>% 
  ggplot(aes(STAT_ZONE, Sapidus_Catch)) + 
  geom_boxplot(aes(group = STAT_ZONE)) + 
  labs(title    = "Blue Crab Catch by Stat Zone", 
       subtitle = "Stat zones ordered West to East - 2010 to 2018", 
       x        = "Statistical Zone",
       y        = "C. sapidus Single Station Catch")

overall_mean <- mean(seamap$Sapidus_Catch, na.rm = T)
percent_zeros <- seamap %>% filter(Sapidus_Catch == 0) %>% count()
station_count <- seamap %>% count()
```

# Data Set Summary

 * Total Number of Stations = `r nrow(seamap)`

 * Starting in `r min(as.numeric(as.character(seamap$Survey_Year)))` and continuing through `r max(as.numeric(as.character(seamap$Survey_Year)))`

 * Total Sapidus Caught was `r sum(seamap$Sapidus_Catch, na.rm = T)`

 * Overall Frequency of Occurrence was `r mean(seamap$Crab_presence, na.rm = TRUE) * 100`

# Factor Summaries

## Yearly Summaries {.tabset .tabset-fade .tabset-pills}

**Overall Mean Catch: `r overall_mean`**
**Stations with no catch: `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`**

```{r}
year_sums <- seamap %>% 
  group_by(Survey_Year) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(Sapidus_Catch)),
            `Mean Catch`      = mean(Sapidus_Catch, na.rm = T),
            `SD`              = sd(Sapidus_Catch, na.rm = T),
            `Var`             = var(Sapidus_Catch),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(Sapidus_Catch, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
  ungroup() %>% 
    mutate(Survey_Year        = factor(Survey_Year),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )

year_sums %>% select(Survey_Year, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
#knitr::kable(year_sums)
```

***

### Yearly Catch Plot

```{r}

year_plot_1 <- year_sums %>% 
  ggplot() +
    geom_col(aes(Survey_Year, `Mean Catch`)) +
    geom_errorbar(aes(x = Survey_Year, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  labs(x = "Survey Year",
       y = "Mean Catch (C. sapidus / 30 min. tow)") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

year_plot_1
#ggsave(plot =  year_plot_1, here("figures", "yearly_catch.png"), dpi = 600)

```

***

### Yearly Frequency of Occurrence

```{r}

year_plot_2 <- year_sums %>% 
  ggplot() +
    geom_col(aes(Survey_Year, `% Occurrence`)) +
    geom_errorbar(aes(x = Survey_Year, 
                      ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  size = .25) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Survey Year",
       y = "Percent Occurrence") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

year_plot_2
#ggsave(plot = year_plot_2, here("figures", "yearly_occurrence.png"), dpi = 600)

```

***

### Yearly Side-by

```{r}
gridExtra::grid.arrange(
  grobs = list(year_plot_1, year_plot_2),
  nrow = 1)
```

***

## Stat Zone Summaries {.tabset .tabset-fade .tabset-pills}

```{r}
#Assign Stat Zone from NMFS grid
#szones <- read_sf(here("GIS_objects",  "NMFS_Fishing_Grids_GOM_2013", "NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)
szones <- read_sf(here("data/gis_files","NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)

# Add a better StatZone ID by spatial overlap
seamap <- seamap %>% 
  st_as_sf(coords = c("Start_Long", "Start_Lat"), crs = 4326, remove = FALSE) %>% 
  st_join(szones["StatZone"]) %>% 
  st_set_geometry(NULL) %>% 
  as.data.frame() %>% 
  dplyr::select(-STAT_ZONE) %>%  #Remove default/incorrect one
  mutate(StatZone = factor(StatZone))

szone_summary <- seamap %>% 
  filter(is.na(StatZone)      == FALSE) %>% 
  group_by(StatZone) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(Sapidus_Catch)),
            `Mean Catch`      = mean(Sapidus_Catch, na.rm = T),
            `SD`              = sd(Sapidus_Catch, na.rm = T),
            `Var`             = var(Sapidus_Catch),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(Sapidus_Catch, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(StatZone           = factor(StatZone),
           StatZone           = fct_rev(StatZone),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )

szone_summary %>% select(StatZone, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
#knitr::kable(szone_summary)
```

***

### Stat Zone Catch Plot

```{r}

szones_plot_1 <- szone_summary %>% 
  ggplot() +
    geom_col(aes(StatZone, `Mean Catch`)) +
    geom_errorbar(aes(x = StatZone, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
  geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
  #annotate(geom = "text", x = 7, y = 2.0, label = "LA + MS") +
  #annotate(geom = "text", x = 16, y = 2.0, label = "East of Mobile Bay") +
  annotate(geom = "text", x = 16.5, y = -0.1, label = "East of Mobile Bay") +
  annotate(geom = "text", x = 8, y = -0.1, label = "LA & MS") +
  annotate(geom = "text", x = 2.5, y = -0.1, label = "Texas") +
    labs(x= "Statistical Zone",
         y = "Mean Catch (C. sapidus / 30 min. tow)")

szones_plot_1 
#ggsave(plot = szones_plot_1, here("figures", "statzones_catch.png"), dpi = 600)

```

***

### Stat Zone Frequency of Occurrence

```{r}

szones_plot_2 <- szone_summary %>% 
  ggplot() +
    geom_col(aes(StatZone, `% Occurrence`)) +
    geom_errorbar(aes(x = StatZone, 
                      ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  size = .25) +
  geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
  geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
  annotate(geom = "text", x = 16.5, y = 0.75, label = "East of Mobile Bay") +
  annotate(geom = "text", x = 8, y = 0.75, label = "LA & MS") +
  annotate(geom = "text", x = 2.5, y = 0.75, label = "Texas") +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Statistical Zone",
       y = "Percent Occurrence")

szones_plot_2
#ggsave(plot = szones_plot_2, here("figures", "statzones_occurrence.png"), dpi = 600)
```

***

### Stat Zone Side-by

```{r}
gridExtra::grid.arrange(
  grobs = list(szones_plot_1, szones_plot_2),
  nrow = 1)
```

***

## Region Summary {.tabset .tabset-fade .tabset-pills}

```{r}
seamap <- seamap %>% 
  mutate(
    # region = ifelse(Start_Lat < 28.387595 & Start_Long < -96, "South Texas", "TX/LA"),
    #      region = ifelse(Start_Long > -89.2, "MS Bight", region),
    #      region = ifelse(Start_Long > -87.5, "FL", region),
    #      region = factor(region)
    region = ifelse(StatZone %in% seq("21", "18"), "Texas", "Louisiana"),
    region = ifelse(StatZone %in% seq("12", "10"), "MS Bight", region),
    region = ifelse(StatZone %in% seq("1", "9"), "Florida", region),
    region = factor(region, levels = c("Texas", "Louisiana", "MS Bight", "Florida"))
    )

#Output seamap analysis file
write_csv(seamap, here::here("data/offshore", "seamap_cpue_2019_analysis.csv"), 
          col_names = TRUE)

region_summary <- seamap %>% 
  filter(is.na(region)      == FALSE) %>% 
  group_by(region) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(Sapidus_Catch)),
            `Mean Catch`      = mean(Sapidus_Catch, na.rm = T),
            `SD`              = sd(Sapidus_Catch, na.rm = T),
            `Var`             = var(Sapidus_Catch),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(Sapidus_Catch, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(region             = factor(region, 
                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
           #region             = fct_rev(region),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
    )

region_summary %>% select(region, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
#knitr::kable(region_summary)
```

***

### Regional Catch Plot

```{r}

region_plot_1 <- region_summary %>% 
  ggplot() +
    geom_col(aes(region, `Mean Catch`)) +
    geom_errorbar(aes(x = region, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
    labs(x= "Sampling Region",
         y = "Mean Catch (C. sapidus / 30 min. tow)")

region_plot_1 
#ggsave(plot = region_plot_1, here("figures", "regions_catch.png"), dpi = 600)
```

***

### Regional Frequency of Occurrence

```{r}

region_plot_2 <- region_summary %>% 
  ggplot() +
    geom_col(aes(region, `% Occurrence`)) +
    geom_errorbar(aes(x = region, 
                      ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  size = .25) +
  # geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
  # geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
  # annotate(geom = "text", x = 16.5, y = 0.75, label = "East of Mobile Bay") +
  # annotate(geom = "text", x = 8, y = 0.75, label = "LA & MS") +
  # annotate(geom = "text", x = 2.5, y = 0.75, label = "Texas") +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Sampling Region",
       y = "Percent Occurrence")

region_plot_2
#ggsave(plot = region_plot_2, here("figures", "regions_occurrence.png"), dpi = 600)

```

***

### Regional Side-by

```{r}
gridExtra::grid.arrange(
  grobs = list(region_plot_1, region_plot_2),
  nrow = 1)
```

***

## Region - Season {.tabset .tabset-fade .tabset-pills}

```{r}
rs_summary <- seamap %>% 
  filter(is.na(region)      == FALSE) %>% 
  group_by(region, Season) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(Sapidus_Catch)),
            `Mean Catch`      = mean(Sapidus_Catch, na.rm = T),
            `SD`              = sd(Sapidus_Catch, na.rm = T),
            `Var`             = var(Sapidus_Catch),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(Sapidus_Catch, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(Season             = factor(Season, levels = c("Summer", "Fall")),
           region             = factor(region, 
                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
           #region             = fct_rev(region),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
    )

rs_summary %>% select(region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
```

***

### Region - Season Catch

```{r}
rs_plot_1 <- rs_summary %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = "Survey Year",
       y = "Mean Catch (C. sapidus / 30 min. tow)") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

rs_plot_1 
```

***

### Region - Season FOO

```{r}

rs_plot_2 <- rs_summary %>% 
  ggplot(aes(region, `% Occurrence`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Survey Year",
       y = "Percent Occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

rs_plot_2

```

***

### Region - Season Side-by

```{r}

gridExtra::grid.arrange(
  grobs = list(rs_plot_1 + theme(legend.position = "none"), rs_plot_2),
  nrow = 1)

```

***

## Seasonal Summary {.tabset .tabset-fade .tabset-pills}

```{r}

season_summary <- seamap %>% 
  group_by(Survey_Year, Season) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(Sapidus_Catch)),
            `Mean Catch`      = mean(Sapidus_Catch, na.rm = T),
            `SD`              = sd(Sapidus_Catch, na.rm = T),
            `Var`             = var(Sapidus_Catch),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(Sapidus_Catch, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(Crab_presence, na.rm = T),
            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(Survey_Year        = factor(Survey_Year),
           # StatZone         = factor(StatZone),
           # StatZone         = fct_rev(StatZone),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )

season_summary%>% select(Survey_Year, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
#knitr::kable(season_summary)
```

***

### Seasonal Catch Plot

```{r}

season_plot_1 <- season_summary %>% 
  ggplot(aes(Survey_Year, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = "Survey Year",
       y = "Mean Catch (C. sapidus / 30 min. tow)") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

season_plot_1 
#ggsave(plot =  year_plot_1, here("figures", "yearly_catch.png"), dpi = 600)

```

***

### Seasonal Frequency of Occurrence

```{r}

season_plot_2 <- season_summary %>% 
  ggplot(aes(Survey_Year, `% Occurrence`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Survey Year",
       y = "Percent Occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    axis.text.x = element_text(angle = 45, vjust = 0.5)
    )

season_plot_2

```

***

### Seasonal Side-by

```{r}
gridExtra::grid.arrange(
  grobs = list(season_plot_1 + theme(legend.position = "none"), season_plot_2),
  nrow = 1)
```

***

## Combining Figures {.tabset .tabset-fade .tabset-pills}

### 1x2

```{r, message = FALSE, warning = FALSE, comment = NA}
year_plots <- grid.arrange(grobs = list(year_plot_1 + xlab(""), year_plot_2), nrow = 2, ncol = 1)
year_plots
season_plots <- grid.arrange(grobs = list(season_plot_1 + xlab(""), season_plot_2), nrows = 2, ncol = 1)
season_plots
szone_plots <- grid.arrange(grobs = list(szones_plot_1 + xlab(""), szones_plot_2), nrows = 2, ncol = 1)
szone_plots

```

### 3x2 A.

```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}
super_plot_tall <- grid.arrange(
  grobs = list(year_plot_1, year_plot_2+ ylab(""),
               season_plot_1, season_plot_2+ ylab(""),
               szones_plot_1, szones_plot_2+ ylab("")), 
  nrow = 3)
super_plot_tall
```

### 3x2 B.

```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}

super_plot_wide <- grid.arrange(
  grobs = list(year_plot_1 + xlab(""), season_plot_1 + xlab("") + ylab(""), szones_plot_1 + xlab("") + ylab(""),
               year_plot_2,            season_plot_2 + ylab(""), szones_plot_2 + ylab("")),
  nrow = 2
)

super_plot_wide
```

# Index of Abundance

## Negative Binomial IOA {.tabset .tabset-fade .tabset-pills}

A negative binomial generalized linear model was used to estimate an index of abundance for the time series. The factors considered in the model were Year, Season, and Stat Zone.

### Model Selection

**Method :** Move from the simplest model of catch and year to the most complex with year, season, statzone, depth, temp, and salinity.

```{r}
#don't want empty statzones here if we are using them in model
seamap_sz <- seamap %>% filter(StatZone %not in% c(0,1,6,9,12,22)) #Don't need this if we use region

#simple -> complex models
#mod1 <- glm.nb(Sapidus_Catch ~ Year_f, data = seamap)
#mod2 <- glm.nb(Sapidus_Catch ~ Year_f + Season, data = seamap)
mod3 <- glm.nb(Sapidus_Catch ~ Year_f + Season + StatZone, data = seamap_sz)
#mod3 <- glm.nb(Sapidus_Catch ~ Year_f + Season + region, data = seamap)
#mod4 <- glm.nb(Sapidus_Catch ~ Year_f + Season + STAT_ZONE + Depth_std, data = seamap)
#mod4 <- glm.nb(Sapidus_Catch ~ Year_f + Season + STAT_ZONE + Depth_std, data = seamap)
#mod5 <- glm.nb(Sapidus_Catch ~ Year_f + Season + STAT_ZONE + Depth_std + Salinity_std, data = seamap)
#mod6 <- glm.nb(Sapidus_Catch ~ Year_f + Season + STAT_ZONE + Depth_std + Salinity_std + Temp_std, data = seamap)
# mod7 <- glm.nb(Sapidus_Catch ~ Year_f + Season + Survey_design + STAT_ZONE + Depth_std + Salinity_std + Temp_std, data = seamap)

# model_list <- list("year" = mod1, 
#                    "year + season" = mod2, 
#                    "year + season + statzone" = mod3, 
#                    "year + season + statzone + depth" = mod4, 
#                    "year + season + statzone + depth + salinity" = mod5, 
#                    "year + season + statzone + depth + salinity + temp" = mod6)
# map(model_list, AIC)
```

**Most parsimonious model (AIC) : **

year + season + stat zone

OR

year + season + region

### significant predictors:
```{r}
#salinity and temp significant, but are they
best_mod <- mod3

#Inserting the offset model here
#best_mod <- glm.nb(Sapidus_Catch ~ Year_f + Season + StatZone + offset(log(MIN_FISH)), data = seamap_sz)

tidy(best_mod) %>% kable()

#glance(best_mod) %>% kable()
```

### qqplot

I've seen worse, obviously not perfect though.

```{r}

#qqplot for model fit of best model (AIC)
t1 <- qres.nbinom(best_mod)
qqnorm(t1)
abline(0, 1, col = "red")

```

## Predicting abundance indices (Statzone - mod) {.tabset .tabset-fade .tabset-pills}

Generate the data for a timeline using estimated marginal means. Then plot that timeline with Confidence interval.

```{r}
#Predicted abundance dataframe
best_mod.dat <- emmeans(best_mod, 
                        specs = "Year_f" , 
                        by = "Year_f", 
                        type = "response") %>% 
  as.data.frame()

mean_pred <- mean(best_mod.dat$response)
best_mod.dat <- best_mod.dat %>% mutate(Std_Index = response/mean_pred,
                                CV = SE/response,
                                LCI = asymp.LCL/mean_pred,
                                UCI = asymp.UCL/mean_pred,
                                Year_n = as.numeric(as.character(Year_f)))

#make scale_x_discrete breaks b/c ggplot is dumb
ystart <- min(as.numeric(seamap$Survey_Year))
yend <- max(as.numeric(seamap$Survey_Year))
ynames <- lubridate::year(seq.Date(as.Date(paste(ystart), "%Y"), 
                   as.Date(paste(yend), "%Y"), 
                   by = "year"))

#ggplot of standardized index of abundance
p <- best_mod.dat %>% ggplot(aes(Year_n, Std_Index)) +
      geom_ribbon(aes(Year_n, ymin = LCI, ymax = UCI), fill = "gray80") +
      geom_line(aes(Year_n, Std_Index, group = 1)) +
      geom_point(aes(Year_n, Std_Index)) +
      geom_hline(aes(yintercept = 1), color = "darkred", linetype = 2) +
      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
      xlab("") + ylab("Scaled Index Value") +
      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom")
p
```

### Observed vs. Predicted

Model prediction (black) & observed mean values (blue), both standardized by overall mean

```{r}
#Observed data
mean_obs <- mean(seamap$Sapidus_Catch)
obs_timeline <- seamap %>% 
  group_by(Survey_Year) %>% 
  summarise(Nobs = n(),
            PercentPos = mean(Crab_presence),
            Mean_Catch = mean(Sapidus_Catch)) %>% 
  mutate(Index_Obs = Mean_Catch/mean_obs)

#Plot again with observed data set on top in blue 
p + geom_line(data = obs_timeline, 
              aes(Survey_Year, Index_Obs, group = 1), 
              col = "royalblue", linetype = 2) +
    geom_point(data = obs_timeline, 
               aes(Survey_Year, Index_Obs), col = "royalblue") +
  labs(title = "Model Estimates and Yearly observed means")
```

### Compare to state catch

State landings data taken from GEDAR assesment and covers years 2000-2011. The values were divided by the overall mean for the timeseries for each state then plotted. They aren't weighted according to which State catches more so this plot isn't great.

Pretty noisy, and gives you a sense that either the landings reflect the population poorly, or that the population is resilient to some.

```{r}
#Compare to GEDAR01 data, raw catch
gedar <- tibble(Year_f         = c(2000:2011),
                Texas          = c(1.19, 1.72, 1.82, 2.08, 1.90, 1.05, 1.05, 2.27, 1.88, 1.61, 1.65, 1.22),
                Louisiana      = c(2.48, 1.53, 2.63, 1.61, 1.95, 3.95, 8.37, 3.78, 2.41, 3.90, 2.77, 3.73),
                Mississippi    = c(1.70, 2.70, 1.19, 1.07, 1.13, 0.70, 1.37, 1.42, 0.44, 1.28, 2.49, 0.47),
                Alabama        = c(3.95, 4.83, 3.96, 7.73, 8.45, 1.99, 3.62, 1.61, 1.54, 2.12, 5.43, 4.41),
                `Western Gulf` = c(1.98, 1.97, 2.43, 2.33, 2.44, 2.29, 4.21, 3.01, 2.25, 2.75, 2.44, 2.48))

#Standardize by each state's mean and reformat
gedar_std <- gedar %>% 
  mutate(Texas = Texas/ mean(Texas),
         Louisiana = Louisiana / mean(Louisiana),
         Mississippi = Mississippi / mean(Mississippi),
         Alabama = Alabama / mean(Alabama),
         `Western Gulf` = `Western Gulf` / mean(`Western Gulf`)) %>% 
  gather(Texas:`Western Gulf`, key = "State", value = Std_index)

ystart <- 2000
yend <- max(as.numeric(seamap$Survey_Year))
ynames <- lubridate::year(seq.Date(as.Date(paste(ystart), "%Y"), 
                   as.Date(paste(yend), "%Y"), 
                   by = "year"))

#look at individual state trends
p <- best_mod.dat %>% ggplot(aes(Year_n, Std_Index)) +
      geom_ribbon(aes(Year_n, ymin = LCI, ymax = UCI), fill = "gray80") +
      geom_line(aes(Year_n, Std_Index, group = 1)) +
      geom_point(aes(Year_n, Std_Index)) +
      geom_hline(aes(yintercept = 1), color = "darkred", linetype = 2) +
      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
      xlab("") + ylab("Scaled Index Value") +
      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom")

p + geom_line(data = gedar_std, aes(Year_f, Std_index, color = State)) +
    geom_point(data = gedar_std, aes(Year_f, Std_index, color = State))

```

### Looking at the other factors

```{r}
#Breakdown by Year season and statzone
factor_brkdwn <- emmeans(best_mod, 
                         specs = "Year_f", by = c("Year_f", "Season", "StatZone"), 
                         type = "response") %>% as.data.frame()

factor_brkdwn %>% ggplot(aes(fct_rev(StatZone), response, fill = Season)) +
  #geom_line(aes(group = STAT_ZONE)) +
  #geom_point() +
  geom_col(position = "dodge")+
  facet_wrap(~Year_f) +
  xlab("Stat Zone - West -> East") + ylab("Mean Predicted Catch") +
  guides(fill = guide_legend(title = "Season",
                              title.position = "top", title.hjust = 0.5)) +
  theme(#axis.text.x=element_text(angle=45, hjust = 1, vjust=1), 
        legend.position = "bottom")

```

Statzones start counting at 1 (FL Keyes) and continue through brownsville Texas (22), 12 is around the Chandeleurs, and 13 is Terrebonne Bay and the MS Birdfoot.

## NB GLM - Year + Season + Region FINAL

**Update 10/3/2019**

Need To account for catch rates not being discrete with either an offset or with weights

 Formula for using an offset:

 $$Log(Catch)_{y,s,r}\ \sim  \lambda + \lambda^{Year}_{y} + \lambda^{Season}_{s} +\ \lambda^{Region}_{r} + Log(Towtime)$$

Link to Reference:
https://stats.stackexchange.com/questions/66791/where-does-the-offset-go-in-poisson-negative-binomial-regression/66878#66878

Link to formula for GLM
https://newonlinecourses.science.psu.edu/stat504/node/216/

Use emmeans on year + season + region

```{r}

#nbmod <- glm.nb(Sapidus_Catch ~ Year_f + Season + region, data = seamap)

#Add effort offset
nbmod <- glm.nb(Sapidus_Catch ~ Year_f + Season + region + offset(log(MIN_FISH)), data = seamap)

#qqplot for model fit
t1 <- qres.nbinom(nbmod)
qqnorm(t1)
abline(0, 1, col = "red")

tidy(nbmod) %>% kable()

```

### Table of emmeans

```{r}
nbmod_est <- emmeans(nbmod, specs = c("Year_f", "Season", "region"), type = "response") %>% as.data.frame()

nbmod_est %>% kable()

#Make your own plots to compare to the raw means

```

### Full Term Plot

```{r}
nbmod_est %>% mutate(
  Year = as.numeric(as.character(Year_f))
) -> nbmod_est

ggplot(nbmod_est) +
  geom_ribbon(aes(Year, ymin = asymp.LCL, ymax = asymp.UCL, fill = Season), alpha = 0.2) +
  geom_line(aes(x = Year, y = response, color = Season, linetype = Season)) +
  geom_line(aes(x = Year, y = asymp.LCL, color = Season), linetype = 2) +
  geom_line(aes(x = Year, y = asymp.UCL, color = Season), linetype = 2) +
  facet_wrap(~ region) +
  scale_color_manual(values = c("Summer" = "black", "Fall" = "black")) +   #
  scale_fill_manual(values = c("Summer" = "gray50", "Fall" = "gray30")) +
  scale_x_discrete(limits = c(2009:2018),
                   labels = c(2009:2018)) +
  labs(
    y = "Estimated Crabs per Tow",
    x = "Survey Year"
  ) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5),
        legend.position = c(1, .4),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(0, 6, 2, 2),
        legend.background = element_rect(fill = NA)
    )

#Pointrange Plot
ggplot(nbmod_est) +
  geom_pointrange(aes(x = Year, 
                      y = response, 
                      ymin = asymp.LCL, 
                      ymax = asymp.UCL, 
                      shape = Season,
                      color = Season), alpha = 0.8) +
  geom_errorbar(aes(x = Year,
                    ymin = asymp.LCL,
                    ymax = asymp.UCL,
                    color = Season), 
                alpha = 0.8, width = 0.2, show.legend = FALSE) +
  geom_line(aes(x = Year, y = response, color = Season), linetype = 3, alpha = 0.4) +
  geom_line(aes(x = Year, y = response, color = Season), linetype = 3) +
  facet_wrap(~ region) +
  scale_color_manual(values = c("Summer" = "black", "Fall" = "gray40")) +
  scale_x_discrete(limits = c(2009:2018),
                   labels = c(2009:2018)) +
  labs(
    y = "Estimated Crabs per Tow",
    x = "Survey Year"
  ) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5),
        legend.position = c(1, .4),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(0, 6, 2, 2),
        legend.background = element_rect(fill = NA))
```

### Interaction plot Year & Season
```{r}
emmeans::emmip(nbmod, formula = Season ~ Year_f, type = "response")
```

### Interaction Plot Year & Region

```{r}
emmeans::emmip(nbmod, formula = region ~ Year_f, type = "response")

```

### Interaction Plot Season & Region

```{r}
emmeans::emmip(nbmod, formula = Season ~ region, type = "response")

```

# Effort Mapping {.tabset .tabset-fade .tabset-pills}

These maps are made using only the model data so years 2010-2018 and only the stat zones with enough samples and some catch. The gaps around Pensacola and Tampa are those areas I took out because there was no catch and they made the models confidence intervals absurd.

## Stations w/ Stat Zone Numbers

```{r}
#pull model coef
mod_coef <- tidy(best_mod)

sz_coef <- mod_coef %>% 
  filter(str_detect(term, "StatZone")) %>%         #Take only the STAT_ZONE rows
  mutate(term = `str_sub<-`(term, 1,8, value = "")) %>%  #Strip out the text
  #mutate(term = str_sub(term, 1,9, value = "")) %>%  #Strip out the text
  rename(SZ = term)

sz_df <- tribble(

~"SZ", ~"long",  ~"lat",
21,    -97,     26.5,
20,    -96.75,  27.5,
19,    -95.75,  28.25,
18,    -94.5,   28.8,
17,    -93.5,   28.9,
16,    -92.5,   28.85,
15,    -91.5,   28.8,
14,    -90.5,   28.75,
13,    -89.75,  28.9,
12,    -89.25,  29.65,
11,    -88.5,   29.75,
10,    -87.5,   29.80,
 8,    -85.5,   29.35,
 7,    -84.5,   29.25,
 5,    -83.5,   27.55,
 4,    -83.35,   26.75,
 3,    -83.25,   25.75,

) %>% 
  mutate(SZ = as.character(SZ))

sz_df <- right_join(sz_df, sz_coef, by = "SZ")

#pull us map
#usa_map <- map_data("usa")

#rnaturalearth coastlines
usmap <- ne_states(country = "united states of america") %>% 
  st_as_sf() %>% 
  filter(region == "South")

mex <- ne_states(country = "mexico") %>% 
  st_as_sf()

ggplot() +
  geom_point(data = seamap, aes(Start_Long, Start_Lat, color = StatZone), alpha = 0.3, show.legend = FALSE) +

  #geom_polygon(data = usa_map, aes(long, lat, group = group)) +
  # coord_cartesian(xlim = c(-97.2, -82),
  #                 ylim = c(25.75, 32)) +
  geom_sf(data = usmap, fill = "antiquewhite1") + 
  geom_sf(data = mex, fill = "antiquewhite1") +
  coord_sf(xlim = c(-80.5, -97.5), ylim = c(24.75, 31)) +
  geom_text(data = sz_df, aes(long, lat, label = SZ)) +
  xlab("") + ylab("") +
  theme_minimal()

pos_dat <- seamap %>% filter(Sapidus_Catch > 0)
```

```{r}
#Catch grid
# catch.plot <- ggplot() +
#   xlab("") + ylab("") +
#   geom_bin2d(data = pos_dat, aes(Start_Long, Start_Lat), bins = 100)  +
#   scale_fill_gradient("Total Catch", low = "Yellow", high = "red") +
#   coord_cartesian(xlim = c(-97.2, -82),
#                   ylim = c(25.75, 32)) +
#   geom_polygon(data = usa_map, aes(long, lat, group = group)) +
#   #geom_text(data = sz_df, aes(long, lat, label = SZ), color = "black") +
#   guides(fill = guide_colorbar(title = "Total Catch",
#                              title.position = "top",
#                              title.hjust = 0.5)) +
#   ggtitle("Catch Map") +
#   theme(legend.position = "bottom")

catch.plot <- ggplot() +
  xlab("") + ylab("") +
  geom_bin2d(data = pos_dat, aes(Start_Long, Start_Lat))  +
  scale_fill_gradient("Total Catch", low = "Yellow", high = "red") +
  geom_sf(data = usmap, fill = "antiquewhite1") + 
  geom_sf(data = mex, fill = "antiquewhite1") +
  coord_sf(xlim = c(-80.5, -97.5), ylim = c(24.75, 31)) +
  #geom_text(data = sz_df, aes(long, lat, label = SZ), color = "black") +
  guides(fill = guide_colorbar(title = "Total Catch",
                             title.position = "top",
                             title.hjust = 0.5)) +
  ggtitle("Total Catch of C. sapidus") +
  theme_minimal() + theme(legend.position = "bottom")

#station Map
# station.plot <- ggplot() +
#   xlab("") + ylab("") +
#   geom_bin2d(data = seamap, aes(Start_Long, Start_Lat), bins = 100)  +
#   scale_fill_gradient("# of Stations", low = "lightblue", high = "blue") +
#   coord_cartesian(xlim = c(-97.2, -82),
#                   ylim = c(25.75, 32)) +
#   geom_polygon(data = usa_map, aes(long, lat, group = group)) +
#   #geom_text(data = sz_df, aes(long, lat, label = SZ), color = "black") +
#   guides(fill = guide_colorbar(title = "Number of Stations",
#                              title.position = "top",
#                              title.hjust = 0.5)) +
#   ggtitle("Station Map") +
#   theme(legend.position = "bottom")

station.plot <- ggplot() +
  xlab("") + ylab("") +
  geom_bin2d(data = seamap, aes(Start_Long, Start_Lat))  +
  scale_fill_gradient("# of Stations", low = "lightblue", high = "blue") +
  geom_sf(data = usmap, fill = "antiquewhite1") + 
  geom_sf(data = mex, fill = "antiquewhite1") +
  coord_sf(xlim = c(-80.5, -97.5), ylim = c(24.75, 31)) +
  guides(fill = guide_colorbar(title = "Number of Stations",
                             title.position = "top",
                             title.hjust = 0.5)) +
  ggtitle("Number of Stations") +
  theme_minimal() + theme(legend.position = "bottom")

#grid.arrange(station.plot, catch.plot, ncol = 2)

```

## Effort Heatmap

```{r}
station.plot
```

## Catch Heatmap

```{r}
catch.plot
```

# Comments

I have polygons for the stat zones and was thinking I would make a map with those polygons shaded by predicted catch or with the mean catch visible within them. That file is too big for my laptop to process though so I couldn't add it here. There's really three big things with the data.

 1. years are fairly variable with little consistency or things I would consider long-term trends.      
 2. there is pretty consistently more crabs in the Western half of the Gulf, Particularly off Louisiana.     3. There are less crabs in the Fall Survey than the Summer.

 If the goal was to explain why this is so I'd say that its likely the difference in bottom types in these two offshore areas sand/hard bottom vs. mud and then coupled with more crabs inshore off Louisiana so you are just starting with more crabs to begin with. But, for this paper I'm thinking we point out

  * Offshore population, as predicted from SEAMAP is noisy, and that it would make sense to split it East and West based on the locations where we see them and how different the habitats become     
  * Point out that we see less as we sampling moves East and the largest offshore population in off Louisiana     
  * Point out that there are many fewer in the Fall

### 2020-01-05 2019_edits/R/noaa_report/noaa_report.Rmd

---
title: "NOAA Tagging Final Report"
author: "Adam A Kemberling"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    mathjax: null
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#Packages
library(tidyverse)
library(here)
library(stargazer)
library(sf)
library(rnaturalearth)
library(gridExtra)
library(circular)

#Data
tagging <- read_csv(here("data", "noaa_report", "tags_clean_final.csv"), 
                    col_types = cols())
recaps <- read_csv(here("data", "noaa_report", "tags_recaps_clean_final.csv"), 
                   col_types = cols())
both <- read_csv(here("data", "noaa_report", "tags_recaps_clean_final.csv"), 
                 col_types = cols())
usa_poly <- ne_states("united states of america") %>% st_as_sf() %>% filter(region == "South")
mexico_poly <- ne_states("mexico") %>% st_as_sf()
```

# Gulf Scale

##  Summary Statistics

o   Total numbers tagged recaptured

o   Time at liberty

o   Distance travelled (water only)

o   Travel rates

```{r}
both %>% 
  group_by(tag_state) %>% 
  summarise(`Average Time at Liberty` = mean(time_at_large, na.rm = T),
            `Average Distance Travelled (by water*)` = mean())
```

##   Tagging State and Recapture State (Table or alluvial Plot)

# State Scale

##   Summary Statistics

o   Total numbers tagged recaptured

o   Time at liberty

o   Distance travelled (water only)

o   Travel rates

```{r}

```

##   Tagging State and Recapture State (Table or alluvial Plot)

```{r}

```

# Basin Scale

##   Summary Statistics

o   Total numbers tagged when (maybe a figure with calendar month and numbers tagged

o   Maps of tagging and recaptures

```{r}

```

##   Directions travelled (exclude crabs that travelled < 5km for this)

o   Rao’s test for each

o   Crabs recaptured within home estuary

o   Crabs captured somewhere else

##  Travel rates (Maybe exclude crabs that have long times at liberty? Start with 1 month)

o   What patterns stand out: mean and variance etc. by season

```{r}

```

# Crabs outside of Estuaries

##   Map of just them

```{r}

```

##   Any recaptures

```{r}

```

### 2020-01-05 2019_edits/R/offshore_analyses/IOA_report.Rmd

@@
 library(gridExtra)
+library(patchwork)
 library(broom)
@@
 #seamap <- read_csv(here("data_processed/gsmfc_processed", "seamap_cpue_2019.csv"),
-seamap <- read_csv(here("data/offshore", "seamap_cpue_2019.csv"),
+#seamap <- read_csv(here("data/offshore", "seamap_cpue_2019.csv"),
+seamap <- read_csv("~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019.csv",
                    guess_max = 1e6, 
@@
 year_plot_1
-#ggsave(plot =  year_plot_1, here("figures", "yearly_catch.png"), dpi = 600)
+#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)
 
@@
 year_plot_2
-#ggsave(plot = year_plot_2, here("figures", "yearly_occurrence.png"), dpi = 600)
+#ggsave(plot = year_plot_2, here("2019_edits/figures", "yearly_occurrence.png"), dpi = 600)
 
@@
 ```{r}
-gridExtra::grid.arrange(
-  grobs = list(year_plot_1, year_plot_2),
-  nrow = 1)
+year_plot_1 + year_plot_2
 ```
@@
 #szones <- read_sf(here("GIS_objects",  "NMFS_Fishing_Grids_GOM_2013", "NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)
-szones <- read_sf(here("data/gis_files","NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)
+szones <- read_sf("~/Dropbox/SEAMAP_2019/data/gis_files/NMFS_Fishing_Grids_GOM_2013.shp", crs = 4326)
 
@@
 szones_plot_1 
-#ggsave(plot = szones_plot_1, here("figures", "statzones_catch.png"), dpi = 600)
+#ggsave(plot = szones_plot_1, here("2019_edits/figures", "statzones_catch.png"), dpi = 600)
 
@@
 szones_plot_2
-#ggsave(plot = szones_plot_2, here("figures", "statzones_occurrence.png"), dpi = 600)
+#ggsave(plot = szones_plot_2, here("2019_edits/figures", "statzones_occurrence.png"), dpi = 600)
 ```
@@
 ```{r}
-gridExtra::grid.arrange(
-  grobs = list(szones_plot_1, szones_plot_2),
-  nrow = 1)
+szones_plot_1 + szones_plot_2
 ```
@@
 #Output seamap analysis file
-write_csv(seamap, here::here("data/offshore", "seamap_cpue_2019_analysis.csv"), 
+write_csv(seamap, 
+          "~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019_analysis.csv", 
+          #here::here("data/offshore", "seamap_cpue_2019_analysis.csv"), 
           col_names = TRUE)
@@
 region_plot_1 
-#ggsave(plot = region_plot_1, here("figures", "regions_catch.png"), dpi = 600)
+#ggsave(plot = region_plot_1, here("2019_edits/figures", "regions_catch.png"), dpi = 600)
 ```
@@
 region_plot_2
-#ggsave(plot = region_plot_2, here("figures", "regions_occurrence.png"), dpi = 600)
+#ggsave(plot = region_plot_2, here("2019_edits/figures", "regions_occurrence.png"), dpi = 600)
 
@@
 ```{r}
-gridExtra::grid.arrange(
-  grobs = list(region_plot_1, region_plot_2),
-  nrow = 1)
+region_plot_1 + region_plot_2
 ```
@@
 
-gridExtra::grid.arrange(
-  grobs = list(rs_plot_1 + theme(legend.position = "none"), rs_plot_2),
-  nrow = 1)
+rs_plot_1 + theme(legend.position = "none") + rs_plot_2
 
@@
 
-season_summary%>% select(Survey_Year, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
+season_summary %>% select(Survey_Year, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
 #knitr::kable(season_summary)
@@
 season_plot_1 
-#ggsave(plot =  year_plot_1, here("figures", "yearly_catch.png"), dpi = 600)
+#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)
 
@@
 ```{r}
-gridExtra::grid.arrange(
-  grobs = list(season_plot_1 + theme(legend.position = "none"), season_plot_2),
-  nrow = 1)
+season_plot_1 + theme(legend.position = "none") + season_plot_2
 ```
@@
   nrow = 3)
-super_plot_tall
+#super_plot_tall
 ```
@@
 
-super_plot_wide
+#super_plot_wide
 ```

### 2020-01-05 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd

---
title: "Offshore Crabs/Hectare Modeling"
---
title: "Offshore Indices of Abundance for <br/> Blue Crabs"
author: "Adam A Kemberling"
date: "1/4/2020"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#packages
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(patchwork)
library(broom)
library(statmod)
library(sf)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")

#Format ggplot for rest of document
theme_set(theme_bw() + theme(panel.grid.major = element_blank(), 
                             panel.grid.minor = element_blank(), 
                             panel.border = element_rect(fill = NA)))

`%not in%` <- purrr::negate(`%in%`)
```

```{r data}
seamap <- read_csv("~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019.csv",
                   guess_max = 1e6, 
                   col_types = cols())

#Set up Season Column, using survey titles
seamap[str_detect(seamap$TITLE, "Fall"),"Season"] <- "Fall"
seamap[str_detect(seamap$TITLE, "Winter"),"Season"] <- "Winter"
seamap[str_detect(seamap$TITLE, "Summer"),"Season"] <- "Summer"
seamap[str_detect(seamap$TITLE, "Spring"),"Season"] <- "Spring"

# Make any setup changes
seamap <- seamap %>% 
  mutate(STAT_ZONE     = factor(STAT_ZONE),
         Crab_presence = ifelse(Sapidus_Catch > 0, 1, 0),
         Survey_Year   = as.numeric(Survey_Year),
         Season        = factor(Season, levels = c("Summer","Fall","Winter")),
         Survey_Month  = lubridate::month(Date),
         Survey_Month  = factor(Survey_Month),
         Survey_design = ifelse(Survey_Year < 2009, "Old Design", "Current Design"),
         Survey_design = ifelse(Survey_Year == 2008 & Season == "Fall", "Current Design", Survey_design),
         Survey_design = factor(Survey_design, levels = c("Old Design", "Current Design")),
         ####  More changes from DE
         Year_f             =  factor(Survey_Year),
         Month_f            =  factor(Survey_Month),
         Depth              =  (Start_Depth + End_Depth)/2,
         Temp_std           =  (Temp_B- mean(Temp_B))/ mean(Temp_B),
         Salinity_std       =  (Salinity_B- mean(Salinity_B))/ mean(Salinity_B),
         Depth_std          =  (Depth- mean(Depth))/ mean(Depth))

# Do all filtering
seamap <- seamap %>% 
  filter(Season            !=  "Winter",
         Survey_Year     %in%  c(2000:2018),
         Spd_kmh           !=  0,                    #these are infinite cpue
         Depth             <=  110)

# Catch only set
crabs <- seamap %>% filter(Sapidus_Catch > 0)

crabs %>% 
  mutate(STAT_ZONE = fct_rev(STAT_ZONE)) %>% 
  ggplot(aes(STAT_ZONE, Sapidus_Catch)) + 
  geom_boxplot(aes(group = STAT_ZONE)) + 
  labs(title    = "Blue Crab Catch by Stat Zone", 
       subtitle = "Stat zones ordered West to East - 2000 to 2018", 
       x        = "Statistical Zone",
       y        = "C. sapidus Single Station Catch") +
  facet_wrap(~Survey_design)

overall_mean <- mean(seamap$Sapidus_Catch, na.rm = T)
percent_zeros <- seamap %>% filter(Sapidus_Catch == 0) %>% count()
station_count <- seamap %>% count()
```

### 2020-01-05 2019_edits/R/gsmfc_data_wrangling/DistOffshore_DataExplo.R
data wrangling and old jags models added

@@ -1,0 +1,218 @@
+#Phase 2 of seamap data wrangle
+#bring in clean data and set it up for analyses, perform analyses
+library(tidyverse)
+library(here)
+
+# # Raw catch info and trawl info before merge - 2018
+# catch <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_catchdata.csv')
+# trawl.info <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_trawlinfo.csv')
+# seamap <- read_csv('~/Documents/KrackN/Seamap_man/Historic_cleaned/seamap_sapidus_consolidation_2018.csv')
+
+# 2019 load
+catch <- read_csv(here("data_processed/gsmfc_processed", "seamap_catchdata.csv"), 
+                  guess_max = 1e6,
+                  col_types = cols())
+trawl.info <- read_csv(here("data_processed/gsmfc_processed", "seamap_trawlinfo.csv"), 
+                       guess_max = 1e6, 
+                       col_types = cols())
+seamap <- read_csv(here("data_processed/gsmfc_processed", "seamap_sapidus_consolidation_2019.csv"), 
+                   guess_max = 1e6, 
+                   col_types = cols())
+
+
+
+
+####################  rename things  ####################
+names(seamap)
+seamap <- seamap %>% 
+  rename(CTD_Depth   = DEPTH_EMAX,
+         Temp_S      = TEMPSURF,
+         Temp_B      = TEMPMAX,
+         Salinity_S  = SALSURF,
+         Salinity_B  = SALMAX,
+         DO_S        = OXYSURF,
+         DO_B        = OXYMAX,
+         Chlor_S     = CHLORSURF,
+         Chlor_B     = CHLORMAX,
+         Turb_S      = TURBSURF,
+         Turb_B      = TURBMAX,
+         Start_Lat   = DECSLAT,
+         Start_Long  = DECSLON,
+         End_Lat     = DECELAT,
+         End_Long    = DECELON,
+         Start_Depth = DEPTH_SSTA,
+         End_Depth   = DEPTH_ESTA,
+         Survey_Year = YR,
+         Date        = MO_DAY_YR)
+
+
[…]

### 2020-01-05 2019_edits/R/gsmfc_data_wrangling/Seamap_Data_Wrangle.R

@@ -1,0 +1,152 @@
+#SEAMAP DATA WRANGLING, MArch 2019
+#Adam A. Kemberling
+
+#Packages
+library(tidyverse)
+library(here)
+
+
+#Data import, data uploaded from GSMFC March 23, 2019
+BGSREC <- read_csv(here("GSMFC_data_raw", "BGSREC.csv"),col_types = cols())
+ENVREC <- read_csv(here("GSMFC_data_raw", "ENVREC.csv"), col_types = cols())
+CRUISES <- read_csv(here("GSMFC_data_raw", "CRUISES.csv"), col_types = cols()) 
+STAREC <- read_csv(here("GSMFC_data_raw", "STAREC.csv"), col_types = cols())
+INVREC <- read_csv(here("GSMFC_data_raw", "INVREC.csv"), col_types = cols())
+# GLFREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/GLFREC.csv", guess_max = 10e6, col_types = cols())  #GLFREC has SEX of catch
+
+# #Data Cleanup, GLFREC has weight and length info of individuals
+# names(GLFREC)
+# GLFREC <- GLFREC %>% filter(SPEC_GLF == "SAPIDU")
+
+
+#Cruise/Survey Info
+names(CRUISES) #cruise ID, Year, Survey Title, Data collector
+CRUISES <- CRUISES %>% dplyr::select(CRUISEID, YR, TITLE, SOURCE)
+
+
+#Trawl info
+names(STAREC) #Station ID, Cruise ID, MM/DD/YY, Start Lat, Start Lon, End Lat, End Lon, Vessel Speed, start depth, end depth
+STAREC <- STAREC %>% dplyr::select(STATIONID, CRUISEID, MO_DAY_YR, STAT_ZONE, FAUN_ZONE, DECSLAT, DECSLON, DECELAT, DECELON, VESSEL_SPD, DEPTH_SSTA, DEPTH_ESTA)
+
+
+#Tow time and gear type
+names(INVREC)
+INVREC <- INVREC %>% select(STATIONID, GEAR_SIZE, GEAR_TYPE, MESH_SIZE, MIN_FISH, OP)
+tail(INVREC)
+
+
+#Join cruise information with station vessel speed and depth
+CRUISES$CRUISEID <- as.character(CRUISES$CRUISEID)
+STAREC$CRUISEID <- as.character(STAREC$CRUISEID)
[…]

### 2020-01-05 2019_edits/R/offshore_analyses/Mean_catch_estimates.R

@@ -1,0 +1,238 @@
+
+
+####  Characterizing Offshore habitat use, means by area, survey, and year
+# Data 4/30/2019
+# Author : Adam Kemberling
+
+#packages
+library(MASS)
+library(here)
+library(tidyverse)
+library(knitr)
+library(emmeans)
+library(gridExtra)
+library(broom)
+library(statmod)
+
+#Format ggplot for rest of document
+theme_set(theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
+
+`%not in%` <- purrr::negate(`%in%`)
+
+
+#Load and clean up data - from IOA_report
+# Read in data
+seamap <- read_csv(here("data_processed/gsmfc_processed", "seamap_cpue_2019.csv"),
+                   guess_max = 1e6, 
+                   col_types = cols())
+
+#Set up Season Column, using survey titles
+seamap[str_detect(seamap$TITLE, "Fall"),"Season"] <- "Fall"
+seamap[str_detect(seamap$TITLE, "Winter"),"Season"] <- "Winter"
+seamap[str_detect(seamap$TITLE, "Summer"),"Season"] <- "Summer"
+seamap[str_detect(seamap$TITLE, "Spring"),"Season"] <- "Spring"
+
+# Make any setup changes
+seamap <- seamap %>% 
+  mutate(STAT_ZONE     = factor(STAT_ZONE),
+         Crab_presence = ifelse(Sapidus_Catch > 0, 1, 0),
+         Survey_Year   = as.numeric(Survey_Year),
+         Season        = factor(Season, levels = c("Summer","Fall","Winter")),
+         Survey_Month  = lubridate::month(Date),
+         Survey_Month  = factor(Survey_Month),
+         Survey_design = ifelse(Survey_Year < 2009, "Original", "Updated"),
+         Survey_design = ifelse(Survey_Year == 2008 & Season == "Fall", "Updated", Survey_design),
+         Survey_design = factor(Survey_design, levels = c("Original", "Updated"))) 
+
+# Do all filtering
+seamap <- seamap %>%        #More changes from DE
+  mutate(Year_f             =  factor(Survey_Year),
+         Month_f            =  factor(Survey_Month),
+         Depth              =  (Start_Depth + End_Depth)/2,
[…]

### 2020-01-05 2019_edits/R/offshore_analyses/dlnorm_functions.R

@@ -1,0 +1,384 @@
+# Created 10/23/2018
+# Authors : David Hanisko & Adam A. Kemberling
+
+
+#Inputs :
+# 1. "bin_model" a glm(, family = quasibinomial(link = "logit") model using all data, response is binary success/fail
+# 2. "Ln_model" a glm(, family = "gaussian") model, using the positive only subset, performed on log transformed data
+
+
+
+dlnorm_lo_method <- function(bin_model, Ln_model) {
+  
+  ####  lsmeans from model 1 - Proportion Positive  ####
+  # get lsmeans for proportion positive using bin_model
+  qb_lsm_om <- lsmeans(bin_model, specs = "Year_f" , by = "Year_f")   #extract lsmeanas
+  qb_lsm_om_df <- as.data.frame(summary(qb_lsm_om))            #save summary as dataframe
+  
+  
+  #get lsmeans for proportion positive on response (proportional scale)
+  qb_lsmt_om_df <- as.data.frame(summary(qb_lsm_om, type = "response"))
+  rm(qb_lsm_om)                                                #remove intermediate to obj
+  
+  #add prob from response on response scale to modeled lsmeans
+  qb_lsm_om_df$prob <- qb_lsmt_om_df$prob
+  
+  #######################################################################################
+  
+  ####  lsmeans from model 2 - lognormal glm  ####
+  # get lsmeans on model scale
+  p_lsm_om <- lsmeans(Ln_model, "Year_f",weights="proportional")
+  p_lsm_om <- as.data.frame(summary(p_lsm_om))
+  #p_lsm_om
+  
+  # create bias corrected backtransfomed to calculate correlation coefficient
+  p_lsm_om$LSM_bcpos <- exp(p_lsm_om$lsmean + (p_lsm_om$SE**2/2))
+  
+  
+  
+  #######################################################################################
+  
+  
+  ####  Bias Corrected Back Transformation
+  
+  
+  # Estimate the annual standardized index as the product:  LSMeans ProPos * LSMeans Pos
+  # apply bias correction to estimates
+  
+  ######## modifid by dsh to match up with MOrtiz bias correction functions and final index calculations
+  
+  # 1.
[…]

### 2020-01-05 2019_edits/R/offshore_analyses/hurdlemod_jags.R

@@ -1,0 +1,120 @@
+# Jags IOA model code
+
+library(tidyverse)
+library(R2jags)
+
+
+#Or if you hate your life try jags
+write_csv(seamap, "SEAMAP_model_ready.csv")
+read_csv("SEAMAP_model_ready.csv")
+
+#Jags Model Setup
+
+############## sample model matrices, and jags.dat prep ######
+seamap.test <- seamap %>% filter(Survey_Year > 2000) #try one year to start
+MyStd <- function(x) { (x - mean(x)) / sd(x)} #Standardizaton function
+
+# Define 0-1 data
+seamap.test$Crab_presence <- as.numeric(seamap.test$Crab_presence)
+
+# Step 1: Standardize any continuous covariates & format factors
+#seamap$temp.std <- MyStd(seamap$Temp)
+seamap.test$Survey_Year <- factor(seamap.test$Survey_Year)
+seamap.test$Survey_Month <- factor(seamap.test$Survey_Month)
+seamap.test$STAT_ZONE <- factor(seamap.test$STAT_ZONE , levels = c(22:11))
+
+# Step 2: Prepare data for JAGS
+X <- model.matrix( ~ 1 + Survey_Year + Survey_Month + STAT_ZONE, 
+                   data = seamap.test)
+K    <- ncol(X)
+
+JAGS.data <- list(Y = seamap.test$Crab_presence,  #Response
+                  X = X,                          #Covariates
+                  K = K,                          #Number of betas
+                  N = nrow(seamap.test)           #Sample size
+)                 
+
+JAGS.data
+
+####  Not Run -- What I thought we'd need to do with random effects  ####
+#I0    <- as.numeric(seamap.test$Crab_presence)
+#re1    <- as.numeric(as.factor(seamap.test$STAT_ZONE))
+#NumRE1 <- length(unique(seamap.test$STAT_ZONE))
+#re2    <- as.numeric(as.factor(seamap.test$Survey_Month))
+#NumRE2 <- length(unique(seamap.test$Season))
+# 
+# 
+# ######## Jags data ####
+# JAGS.data <- list(Y = seamap.test$CPUE_towspd,  #Response
+#                   Xc = Xc,                      #Covariates
+#                   Kc = Kc,                      #Number of betas
+#                   N = nrow(seamap.test),          #Sample Size
[…]

### 2020-01-05 2019_edits/R/gsmfc_data_wrangling/DistOffshore_DataExplo.R
wrangle check

@@ -1,5 +1,6 @@
 #Phase 2 of seamap data wrangle
 #bring in clean data and set it up for analyses, perform analyses
+
 library(tidyverse)
 library(here)
 

### 2020-01-05 2019_edits/R/gsmfc_data_wrangling/Seamap_Data_Wrangle.R

@@ -3,16 +3,22 @@
 
 #Packages
 library(tidyverse)
-library(here)
+#library(here)
 
 
 #Data import, data uploaded from GSMFC March 23, 2019
-BGSREC <- read_csv(here("GSMFC_data_raw", "BGSREC.csv"),col_types = cols())
-ENVREC <- read_csv(here("GSMFC_data_raw", "ENVREC.csv"), col_types = cols())
-CRUISES <- read_csv(here("GSMFC_data_raw", "CRUISES.csv"), col_types = cols()) 
-STAREC <- read_csv(here("GSMFC_data_raw", "STAREC.csv"), col_types = cols())
-INVREC <- read_csv(here("GSMFC_data_raw", "INVREC.csv"), col_types = cols())
-# GLFREC <- read_csv("~/Documents/KrackN/Seamap_man/GSMFC_data/GLFREC.csv", guess_max = 10e6, col_types = cols())  #GLFREC has SEX of catch
+BGSREC <- read_csv("/Users/adamkemberling/Dropbox (The Craboratory)/SEAMAP_2019/data/GSMFC_raw/BGSREC.csv", 
+                   col_types = cols(), guess_max = 1e5)
+ENVREC <- read_csv("/Users/adamkemberling/Dropbox (The Craboratory)/SEAMAP_2019/data/GSMFC_raw/ENVREC.csv", 
+                   col_types = cols(), guess_max = 1e5)
+CRUISES <- read_csv("/Users/adamkemberling/Dropbox (The Craboratory)/SEAMAP_2019/data/GSMFC_raw/CRUISES.csv", 
+                    col_types = cols(), guess_max = 1e5)
+STAREC <- read_csv("/Users/adamkemberling/Dropbox (The Craboratory)/SEAMAP_2019/data/GSMFC_raw/STAREC.csv", 
+                   col_types = cols(), guess_max = 1e5)
+INVREC <- read_csv("/Users/adamkemberling/Dropbox (The Craboratory)/SEAMAP_2019/data/GSMFC_raw/INVREC.csv", 
+                   col_types = cols(), guess_max = 1e5)
+# GLFREC <- read_csv("/Users/adamkemberling/Dropbox (The Craboratory)/SEAMAP_2019/data/GSMFC_raw/GLFREC.csv", 
+                   # col_types = cols(), guess_max = 1e5)  #GLFREC has SEX of catch
 
 # #Data Cleanup, GLFREC has weight and length info of individuals
 # names(GLFREC)
[…]

### 2020-01-06 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
tweedie mod

@@
 library(patchwork)
+library(gridExtra)
 library(broom)
@@
 
-overall_mean <- mean(seamap$Sapidus_Catch, na.rm = T)
+overall_mean <- mean(seamap$CPUE_towspd, na.rm = T)
 percent_zeros <- seamap %>% filter(Sapidus_Catch == 0) %>% count()
@@
 ```
+
+# Data Set Summary
+
+ * Total Number of Stations = `r nrow(seamap)`
+
+ * Starting in `r min(as.numeric(as.character(seamap$Survey_Year)))` and continuing through `r max(as.numeric(as.character(seamap$Survey_Year)))`
+
+ * Total Sapidus Caught was `r sum(seamap$Sapidus_Catch, na.rm = T)`
+
+ * Overall Frequency of Occurrence was `r mean(seamap$Crab_presence, na.rm = TRUE) * 100`
+
+# Factor Summaries
+
+## Yearly Summaries {.tabset .tabset-fade .tabset-pills}
+
+**Overall Mean Catch Crabs/Hectare: `r overall_mean`**
+**Stations with no catch: `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`**
+
+```{r}
+year_sums <- seamap %>% 
+  group_by(Survey_Year) %>% 
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(CPUE_towspd)),
+            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
+            `SD`              = sd(CPUE_towspd, na.rm = T),
+            `Var`             = var(CPUE_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+            `% Occurrence`    = mean(Crab_presence, na.rm = T),
+            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+  ungroup() %>% 
+    mutate(Survey_Year        = factor(Survey_Year),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+         )
+
+year_sums %>% select(Survey_Year, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
+#knitr::kable(year_sums)
+```
+
+***
+
+### Yearly Catch Plot
+
+```{r}
+
+year_plot_1 <- year_sums %>% 
+  ggplot() +
+    geom_col(aes(Survey_Year, `Mean Catch`)) +
+    geom_errorbar(aes(x = Survey_Year, 
+                      ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  size = .25) +
+  labs(x = "Survey Year",
+       y = "Mean Catch (C. sapidus / Hectare)") +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
+
+year_plot_1
+#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)
+
+```
+
+***
+
+### Yearly Frequency of Occurrence
+
+```{r}
+
+year_plot_2 <- year_sums %>% 
+  ggplot() +
+    geom_col(aes(Survey_Year, `% Occurrence`)) +
+    geom_errorbar(aes(x = Survey_Year, 
+                      ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  size = .25) +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = "Survey Year",
+       y = "Percent Occurrence") +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
+
+year_plot_2
+#ggsave(plot = year_plot_2, here("2019_edits/figures", "yearly_occurrence.png"), dpi = 600)
+
+```
+
+***
+
+### Yearly Side-by
+
+```{r}
+year_plot_1 + year_plot_2
+```
+
+***
+
+## Stat Zone Summaries {.tabset .tabset-fade .tabset-pills}
+
+```{r}
+#Assign Stat Zone from NMFS grid
+szones <- read_sf("~/Dropbox/SEAMAP_2019/data/gis_files/NMFS_Fishing_Grids_GOM_2013.shp", 
+                  crs = 4326)
+
+# Add a better StatZone ID by spatial overlap
+seamap <- seamap %>% 
+  st_as_sf(coords = c("Start_Long", "Start_Lat"), crs = 4326, remove = FALSE) %>% 
+  st_join(szones["StatZone"]) %>% 
+  st_set_geometry(NULL) %>% 
+  as.data.frame() %>% 
+  dplyr::select(-STAT_ZONE) %>%  #Remove default/incorrect one
+  mutate(StatZone = factor(StatZone))
+
+szone_summary <- seamap %>% 
+  filter(is.na(StatZone)      == FALSE) %>% 
+  group_by(StatZone) %>% 
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(CPUE_towspd)),
+            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
+            `SD`              = sd(CPUE_towspd, na.rm = T),
+            `Var`             = var(CPUE_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+            `% Occurrence`    = mean(Crab_presence, na.rm = T),
+            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+    ungroup() %>% 
+    mutate(StatZone           = factor(StatZone),
+           StatZone           = fct_rev(StatZone),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+         )
+
+szone_summary %>% 
+  select(StatZone, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
+  knitr::kable()
+
+```
+
+***
+
+### Stat Zone Catch Plot
+
+```{r}
+
+szones_plot_1 <- szone_summary %>% 
+  ggplot() +
+    geom_col(aes(StatZone, `Mean Catch`)) +
+    geom_errorbar(aes(x = StatZone, 
+                      ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  size = .25) +
+  geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
+  geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
+  #annotate(geom = "text", x = 7, y = 2.0, label = "LA + MS") +
+  #annotate(geom = "text", x = 16, y = 2.0, label = "East of Mobile Bay") +
+  annotate(geom = "text", x = 16.5, y = -0.1, label = "East of Mobile Bay") +
+  annotate(geom = "text", x = 8, y = -0.1, label = "LA & MS") +
+  annotate(geom = "text", x = 2.5, y = -0.1, label = "Texas") +
+    labs(x= "Statistical Zone",
+         y = "Mean Catch (C. sapidus / Hectare)")
+
+szones_plot_1 
+#ggsave(plot = szones_plot_1, here("2019_edits/figures", "statzones_catch.png"), dpi = 600)
+
+```
+
+***
+
+### Stat Zone Frequency of Occurrence
+
+```{r}
+
+szones_plot_2 <- szone_summary %>% 
+  ggplot() +
+    geom_col(aes(StatZone, `% Occurrence`)) +
+    geom_errorbar(aes(x = StatZone, 
+                      ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  size = .25) +
+  geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
+  geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
+  annotate(geom = "text", x = 16.5, y = 0.75, label = "East of Mobile Bay") +
+  annotate(geom = "text", x = 8, y = 0.75, label = "LA & MS") +
+  annotate(geom = "text", x = 2.5, y = 0.75, label = "Texas") +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = "Statistical Zone",
+       y = "Percent Occurrence")
+
+szones_plot_2
+#ggsave(plot = szones_plot_2, here("2019_edits/figures", "statzones_occurrence.png"), dpi = 600)
+```
+
+***
+
+### Stat Zone Side-by
+
+```{r}
+szones_plot_1 + szones_plot_2
+```
+
+***
+
+## Region Summary {.tabset .tabset-fade .tabset-pills}
+
+```{r}
+seamap <- seamap %>% 
+  mutate(
+    # region = ifelse(Start_Lat < 28.387595 & Start_Long < -96, "South Texas", "TX/LA"),
+    #      region = ifelse(Start_Long > -89.2, "MS Bight", region),
+    #      region = ifelse(Start_Long > -87.5, "FL", region),
+    #      region = factor(region)
+    region = ifelse(StatZone %in% seq("21", "18"), "Texas", "Louisiana"),
+    region = ifelse(StatZone %in% seq("12", "10"), "MS Bight", region),
+    region = ifelse(StatZone %in% seq("1", "9"), "Florida", region),
+    region = factor(region, levels = c("Texas", "Louisiana", "MS Bight", "Florida"))
+    )
+
+#Output seamap analysis file
+write_csv(seamap, 
+          "~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019_analysis.csv", 
+          col_names = TRUE)
+
+region_summary <- seamap %>% 
+  filter(is.na(region)      == FALSE) %>% 
+  group_by(region) %>% 
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(CPUE_towspd)),
+            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
+            `SD`              = sd(CPUE_towspd, na.rm = T),
+            `Var`             = var(CPUE_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+            `% Occurrence`    = mean(Crab_presence, na.rm = T),
+            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+    ungroup() %>% 
+    mutate(region             = factor(region, 
+                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
+           #region             = fct_rev(region),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+    )
+
+region_summary %>% 
+  select(region, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
+  knitr::kable()
+
+```
+
+***
+
+### Regional Catch Plot
+
+```{r}
+
+region_plot_1 <- region_summary %>% 
+  ggplot() +
+    geom_col(aes(region, `Mean Catch`)) +
+    geom_errorbar(aes(x = region, 
+                      ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  size = .25) +
+    labs(x= "Sampling Region",
+         y = "Mean Catch (C. sapidus / Hectare)")
+
+region_plot_1 
+#ggsave(plot = region_plot_1, here("2019_edits/figures", "regions_catch.png"), dpi = 600)
+```
+
+***
+
+### Regional Frequency of Occurrence
+
+```{r}
+
+region_plot_2 <- region_summary %>% 
+  ggplot() +
+    geom_col(aes(region, `% Occurrence`)) +
+    geom_errorbar(aes(x = region, 
+                      ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  size = .25) +
+  # geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
+  # geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
+  # annotate(geom = "text", x = 16.5, y = 0.75, label = "East of Mobile Bay") +
+  # annotate(geom = "text", x = 8, y = 0.75, label = "LA & MS") +
+  # annotate(geom = "text", x = 2.5, y = 0.75, label = "Texas") +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = "Sampling Region",
+       y = "Percent Occurrence")
+
+region_plot_2
+#ggsave(plot = region_plot_2, here("2019_edits/figures", "regions_occurrence.png"), dpi = 600)
+
+```
+
+***
+
+### Regional Side-by
+
+```{r}
+region_plot_1 + region_plot_2
+```
+
+***
+
+## Region - Season {.tabset .tabset-fade .tabset-pills}
+
+```{r}
+rs_summary <- seamap %>% 
+  filter(is.na(region)      == FALSE) %>% 
+  group_by(region, Season) %>% 
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(CPUE_towspd)),
+            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
+            `SD`              = sd(CPUE_towspd, na.rm = T),
+            `Var`             = var(CPUE_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+            `% Occurrence`    = mean(Crab_presence, na.rm = T),
+            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+    ungroup() %>% 
+    mutate(Season             = factor(Season, levels = c("Summer", "Fall")),
+           region             = factor(region, 
+                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
+           #region             = fct_rev(region),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+    )
+
+rs_summary %>% 
+  select(region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
+  knitr::kable()
+```
+
+***
+
+### Region - Season Catch
+
+```{r}
+rs_plot_1 <- rs_summary %>% 
+  ggplot(aes(region, `Mean Catch`, fill = Season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  position = "dodge",
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  labs(x = "Survey Year",
+       y = "Mean Catch (C. sapidus / Hectare)") + theme(
+    legend.position = c(1, .95),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA),
+    axis.text.x = element_text(angle = 45, vjust = 0.5)
+    )
+
+rs_plot_1 
+```
+
+***
+
+### Region - Season FOO
+
+```{r}
+
+rs_plot_2 <- rs_summary %>% 
+  ggplot(aes(region, `% Occurrence`, fill = Season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  position = "dodge",
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = "Survey Year",
+       y = "Percent Occurrence") + theme(
+    legend.position = c(1, .95),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA),
+    axis.text.x = element_text(angle = 45, vjust = 0.5)
+    )
+
+rs_plot_2
+
+```
+
+***
+
+### Region - Season Side-by
+
+```{r}
+
+rs_plot_1 + theme(legend.position = "none") + rs_plot_2
+
+```
+
+***
+
+## Seasonal Summary {.tabset .tabset-fade .tabset-pills}
+
+```{r}
+
+season_summary <- seamap %>% 
+  group_by(Survey_Year, Season) %>% 
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(CPUE_towspd)),
+            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
+            `SD`              = sd(CPUE_towspd, na.rm = T),
+            `Var`             = var(CPUE_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+            `% Occurrence`    = mean(Crab_presence, na.rm = T),
+            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+    ungroup() %>% 
+    mutate(Survey_Year        = factor(Survey_Year),
+           # StatZone         = factor(StatZone),
+           # StatZone         = fct_rev(StatZone),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+         )
+
+season_summary %>% select(Survey_Year, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
+#knitr::kable(season_summary)
+```
+
+***
+
+### Seasonal Catch Plot
+
+```{r}
+
+season_plot_1 <- season_summary %>% 
+  ggplot(aes(Survey_Year, `Mean Catch`, fill = Season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  position = "dodge",
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  labs(x = "Survey Year",
+       y = "Mean Catch (C. sapidus / Hectare)") + theme(
+    legend.position = c(1, .95),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA),
+    axis.text.x = element_text(angle = 45, vjust = 0.5)
+    )
+
+season_plot_1 
+#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)
+
+```
+
+***
+
+### Seasonal Frequency of Occurrence
+
+```{r}
+
+season_plot_2 <- season_summary %>% 
+  ggplot(aes(Survey_Year, `% Occurrence`, fill = Season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  position = "dodge",
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = "Survey Year",
+       y = "Percent Occurrence") + theme(
+    legend.position = c(1, .95),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA),
+    axis.text.x = element_text(angle = 45, vjust = 0.5)
+    )
+
+season_plot_2
+
+```
+
+***
+
+### Seasonal Side-by
+
+```{r}
+season_plot_1 + theme(legend.position = "none") + season_plot_2
+```
+
+***
+
+## Combining Figures {.tabset .tabset-fade .tabset-pills}
+
+### 1x2
+
+```{r, message = FALSE, warning = FALSE, comment = NA}
+year_plots <- grid.arrange(grobs = list(year_plot_1 + xlab(""), year_plot_2), nrow = 2, ncol = 1)
+year_plots
+season_plots <- grid.arrange(grobs = list(season_plot_1 + xlab(""), season_plot_2), nrows = 2, ncol = 1)
+season_plots
+szone_plots <- grid.arrange(grobs = list(szones_plot_1 + xlab(""), szones_plot_2), nrows = 2, ncol = 1)
+szone_plots
+
+```
+
+### 3x2 A.
+
+```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}
+super_plot_tall <- grid.arrange(
+  grobs = list(year_plot_1, 
+               year_plot_2 + ylab(""),
+               season_plot_1, 
+               season_plot_2 + ylab(""),
+               szones_plot_1, 
+               szones_plot_2 + ylab("")), 
+  nrow = 3)
+#super_plot_tall
+```
+
+### 3x2 B.
+
+```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}
+
+super_plot_wide <- grid.arrange(
+  grobs = list(year_plot_1 + xlab(""), 
+               season_plot_1 + xlab("") + ylab(""), 
+               szones_plot_1 + xlab("") + ylab(""),
+               year_plot_2,            
+               season_plot_2 + ylab(""), 
+               szones_plot_2 + ylab("")),
+  nrow = 2
+)
+
+#super_plot_wide
+```
+
+# Crab/hectare Models
+
+## Tweedie Models {.tabset .tabset-pills}
+
+Tweedie distributions are similar to a negative-binomial in their application for datasets that exhibit zero inflation.
+Tweedie models are applicable in cases where the response is continuous i.e.
+catch/area.
+
+### Model 1a. 2000-2018 w/ interaction
+
+This model uses crabs per hectare as the response over the period of 18 years (2000-2018). Data is limited to statzones that were consistently sampled over the time period (i.e. West of Mobile Bay).
+
+```{r}
+seamap <- seamap %>% rename_all(tolower)
+seamap_west <- seamap %>% 
+  filter(statzone != 12,
+         statzone %in% 11:21)
+
+mod1a <- glm(cpue_towspd ~ year_f + region + season + survey_design +  #Additive covariates
+            year_f * region,                                           #Interaction terms
+            family = tweedie(),
+            data = seamap_west)
+
+# summary(mod1a)
+# 
+# emmeans::emmip(mod1a, region ~ year_f) 
+```
+
+#### Model Summary
+
+```{r}
+tidy(mod1a) %>% 
+  mutate(`signif.` = ifelse(p.value <= .05, "*", "")) %>% 
+  kable()
+```
+
+#### Fit Diagnostics
+
+```{r}
+broom::glance(mod1a) %>% kable()
+```
+
+##### CPUE Timeline
+
+```{r}
+#Predicted abundance dataframe
+mod1a.dat <- emmeans(mod1a, 
+                        specs = "year_f" , 
+                        by    = "region", 
+                        type  = "response") %>% 
+  as.data.frame()
+
+#Try this
+emm <- update(emmeans(m1, "am"), tran = "log")
+summary(emm, type = "response")
+
+#Standardize to mean
+mean_pred <- mean(mod1a.dat$response)
+mod1a.dat <- mod1a.dat %>% mutate(Std_Index = response/mean_pred,
+                                CV = SE/response,
+                                LCI = asymp.LCL/mean_pred,
+                                UCI = asymp.UCL/mean_pred,
+                                Year_n = as.numeric(as.character(year_f)))
+
+#make scale_x_discrete breaks b/c ggplot is dumb
+ystart <- min(as.numeric(seamap$survey_year))
+yend   <- max(as.numeric(seamap$survey_year))
+ynames <- lubridate::year(seq.Date(as.Date(paste(ystart), "%Y"), 
+                   as.Date(paste(yend), "%Y"), 
+                   by = "year"))
+
+#ggplot of standardized index of abundance
+p <- mod1a.dat %>% 
+  ggplot(aes(year_f, response)) +
+      geom_ribbon(aes(Year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
+      geom_line(aes(Year_n, response, group = 1)) +
+      geom_point(aes(Year_n, response)) +
+      geom_hline(aes(yintercept = 0), color = "darkred", linetype = 2) +
+      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
+      xlab("") + ylab("Crabs per Hectare") +
+      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
+      facet_wrap(~region)
+p
+
+emmeans(mod1a, specs = "year_f", by = c("region", "season", "survey_design"))
+```
+
+## Negative Binomial Models {.tabset .tabset-fade .tabset-pills}

### 2020-01-06 2019_edits/R/offshore_analyses/Mean_catch_estimates.R

@@ -22,7 +22,7 @@ theme_set(theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.mino
 
 #Load and clean up data - from IOA_report
 # Read in data
-seamap <- read_csv(here("data_processed/gsmfc_processed", "seamap_cpue_2019.csv"),
+seamap <- read_csv("~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019.csv",
                    guess_max = 1e6, 
                    col_types = cols())
 
@@ -234,5 +234,7 @@ grid.arrange(p5, p6, ncol = 2)
 # Include the number of observations, mean, and standard deviation
 
 
-#The plumber package has a function for these frequency tables, I don't remember what it is called though
-library(plumber)
+#The janitor package has a function for these frequency tables, I don't remember what it is called though
+library(janitor)
+tabyl(seamap, STAT_ZONE, Survey_design) %>% adorn_title() %>% kable()
+

### 2020-01-07 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
nb model with offset

@@
 
-## Tweedie Models {.tabset .tabset-pills}
-
-Tweedie distributions are similar to a negative-binomial in their application for datasets that exhibit zero inflation.
-Tweedie models are applicable in cases where the response is continuous i.e.
-catch/area.
+## NEgbin w/ Offset {.tabset .tabset-pills}
 
@@
   filter(statzone != 12,
-         statzone %in% 11:21)
+         statzone %in% 11:21) %>% 
+  mutate(statzone = factor(statzone))
 
-mod1a <- glm(cpue_towspd ~ year_f + region + season + survey_design +  #Additive covariates
-            year_f * region,                                           #Interaction terms
-            family = tweedie(),
+mod1a <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
+            year_f * region + 
+            offset(log(area_hectares)),
             data = seamap_west)
 
-# summary(mod1a)
-# 
-# emmeans::emmip(mod1a, region ~ year_f) 
+summary(mod1a)
+
+emmeans::emmip(mod1a, region ~ year_f)
 ```
@@
 broom::glance(mod1a) %>% kable()
+
+#Percent deviance explained
+(mod1a$null.deviance - mod1a$deviance) / mod1a$null.deviance
 ```
@@
 ```{r}
-#Predicted abundance dataframe
-mod1a.dat <- emmeans(mod1a, 
-                        specs = "year_f" , 
+
+#Estimated Marginal Means with an offset
+#parameter in the call of offset = 0:
+mod1a.dat <- as.data.frame(emmeans(mod1a, 
+                                  specs = "year_f", 
                                   by    = "region",
-                        type  = "response") %>% 
-  as.data.frame()
-
-#Try this
-emm <- update(emmeans(m1, "am"), tran = "log")
-summary(emm, type = "response")
-
-#Standardize to mean
-mean_pred <- mean(mod1a.dat$response)
-mod1a.dat <- mod1a.dat %>% mutate(Std_Index = response/mean_pred,
-                                CV = SE/response,
-                                LCI = asymp.LCL/mean_pred,
-                                UCI = asymp.UCL/mean_pred,
-                                Year_n = as.numeric(as.character(year_f)))
+                                  type  = "response", 
+                                  offset = 0))
+mod1a.dat$CV <- nbemeans$SE/nbemeans$response
 
 #make scale_x_discrete breaks b/c ggplot is dumb
-ystart <- min(as.numeric(seamap$survey_year))
-yend   <- max(as.numeric(seamap$survey_year))
+ystart <- min(as.numeric(seamap_west$survey_year))
+yend   <- max(as.numeric(seamap_west$survey_year))
 ynames <- lubridate::year(seq.Date(as.Date(paste(ystart), "%Y"), 
@@
 p <- mod1a.dat %>% 
-  ggplot(aes(year_f, response)) +
-      geom_ribbon(aes(Year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
-      geom_line(aes(Year_n, response, group = 1)) +
-      geom_point(aes(Year_n, response)) +
-      geom_hline(aes(yintercept = 0), color = "darkred", linetype = 2) +
+  mutate(year_n = as.numeric(as.character(year_f))) %>% 
+  ggplot(aes(year_n, response)) +
+      geom_ribbon(aes(year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
+      geom_line(aes(year_n, response, group = 1)) +
+      geom_point(aes(year_n, response)) +
+      geom_hline(aes(yintercept = mean(seamap_west$cpue_towspd)), color = "darkred", linetype = 2) +
       scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
-      xlab("") + ylab("Crabs per Hectare") +
+      labs(
+        x = NULL, 
+        y = "Crabs per Hectare",
+        caption = "Red dashed line is the grand mean of crabs/hectare, representing the null model.") +
       theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
@@
 
-## Negative Binomial Models {.tabset .tabset-fade .tabset-pills}
+### Observed vs. Predicted
+
+Model prediction (black) & observed mean values (blue), both standardized by overall mean
+
+```{r}
+#Observed data
+mean_obs <- mean(seamap$Sapidus_Catch)
+obs_timeline <- seamap %>% 
+  group_by(Survey_Year) %>% 
+  summarise(Nobs = n(),
+            PercentPos = mean(Crab_presence),
+            Mean_Catch = mean(Sapidus_Catch)) %>% 
+  mutate(Index_Obs = Mean_Catch/mean_obs)
+
+#Plot again with observed data set on top in blue 
+p + geom_line(data = obs_timeline, 
+              aes(Survey_Year, Index_Obs, group = 1), 
+              col = "royalblue", linetype = 2) +
+    geom_point(data = obs_timeline, 
+               aes(Survey_Year, Index_Obs), col = "royalblue") +
+  labs(title = "Model Estimates and Yearly observed means")
+```

### 2020-01-08 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
model b added for post-design change

@@
 title: "Offshore Crabs/Hectare Modeling"
+editor_options: 
+  chunk_output_type: console
 ---
@@
                   size = .25) +
-  # geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
-  # geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
-  # annotate(geom = "text", x = 16.5, y = 0.75, label = "East of Mobile Bay") +
-  # annotate(geom = "text", x = 8, y = 0.75, label = "LA & MS") +
-  # annotate(geom = "text", x = 2.5, y = 0.75, label = "Texas") +
   scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
@@
 
-## Combining Figures {.tabset .tabset-fade .tabset-pills}
+# Crab/hectare Models {.tabset .tabset-pills}
 
-### 1x2
-
-```{r, message = FALSE, warning = FALSE, comment = NA}
-year_plots <- grid.arrange(grobs = list(year_plot_1 + xlab(""), year_plot_2), nrow = 2, ncol = 1)
-year_plots
-season_plots <- grid.arrange(grobs = list(season_plot_1 + xlab(""), season_plot_2), nrows = 2, ncol = 1)
-season_plots
-szone_plots <- grid.arrange(grobs = list(szones_plot_1 + xlab(""), szones_plot_2), nrows = 2, ncol = 1)
-szone_plots
-
-```
-
-### 3x2 A.
-
-```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}
-super_plot_tall <- grid.arrange(
-  grobs = list(year_plot_1, 
-               year_plot_2 + ylab(""),
-               season_plot_1, 
-               season_plot_2 + ylab(""),
-               szones_plot_1, 
-               szones_plot_2 + ylab("")), 
-  nrow = 3)
-#super_plot_tall
-```
-
-### 3x2 B.
-
-```{r, message = FALSE, warning = FALSE, comment = NA, fig.height=8}
-
-super_plot_wide <- grid.arrange(
-  grobs = list(year_plot_1 + xlab(""), 
-               season_plot_1 + xlab("") + ylab(""), 
-               szones_plot_1 + xlab("") + ylab(""),
-               year_plot_2,            
-               season_plot_2 + ylab(""), 
-               szones_plot_2 + ylab("")),
-  nrow = 2
-)
-
-#super_plot_wide
-```
-
-# Crab/hectare Models
-
-## NEgbin w/ Offset {.tabset .tabset-pills}
-
-### Model 1a. 2000-2018 w/ interaction
+## Model A. 2000-2018 w/ interaction
 
 This model uses crabs per hectare as the response over the period of 18 years (2000-2018). Data is limited to statzones that were consistently sampled over the time period (i.e. West of Mobile Bay).
+
+Model is a generalized linear model with a negative binomial error distribution.
+Blue crab catch is predicted as the sum of linear predictors for the year and season when the station was sampled in addition to the region in which it took place, with an interaction between survey year and region.
+An offset of area towed in hectares was used to predict catch as a rate and account for differences in sampling effort at different stations.
 
@@
 
-summary(mod1a)
-
-emmeans::emmip(mod1a, region ~ year_f)
+#summary(mod1a)
 ```
 
-#### Model Summary
+### Interaction Plot
+
+Looking at an interaction plot indicates that the impact of each region is not consistent across years and that there is an important interaction in the data.
+
+```{r}
+emmeans::emmip(mod1a, region ~ year_f) +
+  labs(title = "Interaction Plot: year * region",
+       caption = "criss-crossing of estimates is subjective indication of interaction",
+       x = NULL) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
+```
+
+### Model Summary
+
+Understanding p-values in glm model summary. Using the default settings in R sets the contrast levels for factors such that all factors are contrasted against the first/lowest factor level.
+
+For example in our model year is modeled as a factor, which adjusts the intercept for the model for each.
+The first year is 2000, so all other years are contrasted against that year's mean estimate.
+One quick way to confirm what factor level is the contrast is y checking which levels are absent from the summary table `summary(my_model)`
+
+Contrasts:   
+year = 2000   
+region = texas   
+season = summer
+
+P-values on factor levels in these tables indicate significant deviation from the contrasts. Post-hoc tests are necessary to compare individual levels against one another.
 
@@
 
-#### Fit Diagnostics
+### Fit Diagnostics - Deviance
 
@@
 #Percent deviance explained
-(mod1a$null.deviance - mod1a$deviance) / mod1a$null.deviance
+perc_dev <- (mod1a$null.deviance - mod1a$deviance) / mod1a$null.deviance
 ```
 
-##### CPUE Timeline
+Goodness of fit for generalized linear models is described using deviance. A glm will report 2 deviance measures:
+
+`null.deviance` is the residual variation remaining from the null model. The null model here is the grand mean of blue crab catch per hectare of all observations
+
+`deviance` is the residual variation remaining from the fitted model. Numbers closer to the null.deviance indicate that the model did not perform much better than the null model.
+
+`% deviance explained` is calculated as $\frac{null.deviance - deviance}{null.deviance} * 100$ and expresses the improvement of the fitted model over the null in % deviance explained.
+
+Percent Deviance for model 1a. = `r perc_dev`
+
+#### CPUE Timeline
+
+Because we used area towed in the model as an offset predictions from our model can be interprated as crabs per hectare.
 
@@
                                   offset = 0))
-mod1a.dat$CV <- nbemeans$SE/nbemeans$response
+mod1a.dat$CV <- mod1a.dat$SE/mod1a.dat$response
 
@@
         x = NULL, 
-        y = "Crabs per Hectare",
-        caption = "Red dashed line is the grand mean of crabs/hectare, representing the null model.") +
+        y = "Crabs per Hectare") +
       theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
@@
 
-emmeans(mod1a, specs = "year_f", by = c("region", "season", "survey_design"))
 ```
 
-### Observed vs. Predicted
+### Observed vs. Predicted, all model factors
 
@@
 ```{r}
+
+#Estimated Marginal Means with an offset
+#parameter in the call of offset = 0:
+mod1a.dat <- as.data.frame(emmeans(mod1a, 
+                                  specs = "year_f", 
+                                  by    = c("region", "season"),
+                                  type  = "response", 
+                                  offset = 0))
+mod1a.dat$CV <- mod1a.dat$SE/mod1a.dat$response
+
 #Observed data
-mean_obs <- mean(seamap$Sapidus_Catch)
-obs_timeline <- seamap %>% 
-  group_by(Survey_Year) %>% 
+mean_obs <- mean(seamap_west$cpue_towspd)
+obs_timeline <- seamap_west %>% 
+  group_by(survey_year, region, season) %>% 
   summarise(Nobs = n(),
-            PercentPos = mean(Crab_presence),
-            Mean_Catch = mean(Sapidus_Catch)) %>% 
-  mutate(Index_Obs = Mean_Catch/mean_obs)
+            PercentPos = mean(crab_presence),
+            Mean_CPUE = mean(cpue_towspd)) %>% 
+  mutate(Index_Obs = Mean_CPUE/mean_obs)
 
-#Plot again with observed data set on top in blue 
-p + geom_line(data = obs_timeline, 
-              aes(Survey_Year, Index_Obs, group = 1), 
+#ggplot of standardized index of abundance
+p <- mod1a.dat %>% 
+  mutate(year_n = as.numeric(as.character(year_f))) %>% 
+  ggplot(aes(year_n, response)) +
+      #Fitted Data
+      geom_ribbon(aes(year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
+      geom_line(aes(year_n, response, group = 1)) +
+      geom_point(aes(year_n, response)) +
+      # Observed Data
+      geom_line(data = obs_timeline, 
+              aes(survey_year, Mean_CPUE, group = region), 
               col = "royalblue", linetype = 2) +
       geom_point(data = obs_timeline, 
-               aes(Survey_Year, Index_Obs), col = "royalblue") +
-  labs(title = "Model Estimates and Yearly observed means")
+                 aes(survey_year, Mean_CPUE, group = region), col = "royalblue") +
+      #Theme changes
+      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
+      labs(
+        x = NULL, 
+        y = "Crabs per Hectare",
+        title = "Model Estimates and Yearly observed means") +
+      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
+      facet_grid(season~region)
+p
+
 ```
+
+## Model B. 2009-2018
+
+This model uses crabs per hectare as the response over the period of 9 years (2009-2018).
+Data selection and sampling effort was consistent over this period.
+Additionally the survey expanded to the Eastern Gulf of Mexico so stat zones in that region are included as well.
+
+Model is a generalized linear model with a negative binomial error distribution.
+Blue crab catch is predicted as the sum of linear predictors for the year and season when the station was sampled in addition to the region in which it took place, with an interaction between survey year and region.
+An offset of area towed in hectares was used to predict catch as a rate and account for differences in sampling effort at different stations.
+
+```{r}
+seamap_east <- seamap %>% 
+  filter(statzone != 12,
+         statzone != 1,
+         survey_year %in% 2009:2018) %>% 
+  mutate(statzone = factor(statzone))
+
+modb <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
+            year_f * region + 
+            offset(log(area_hectares)),
+            data = seamap_east)
+
+#summary(modb)
+```
+
+### Interaction Plot
+
+Looking at an interaction plot indicates that the impact of each region is not consistent across years and that there is an important interaction in the data.
+The sharp peaks for Florida's linear predictor reflect years when there was no catch.
+
+```{r}
+emmeans::emmip(modb, region ~ year_f) +
+  labs(title = "Interaction Plot: year * region",
+       caption = "criss-crossing of estimates is subjective indication of interaction",
+       x = NULL) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
+```
+
+### Model Summary
+
+```{r}
+tidy(modb) %>% 
+  mutate(`signif.` = ifelse(p.value <= .05, "*", "")) %>% 
+  kable()
+```
+
+### Fit Diagnostics - Deviance
+
+```{r}
+broom::glance(modb) %>% kable()
+
+#Percent deviance explained
+perc_dev <- (modb$null.deviance - modb$deviance) / modb$null.deviance
+```
+
+Goodness of fit for generalized linear models is described using deviance. A glm will report 2 deviance measures:
+
+`null.deviance` is the residual variation remaining from the null model. The null model here is the grand mean of blue crab catch per hectare of all observations
+
+`deviance` is the residual variation remaining from the fitted model. Numbers closer to the null.deviance indicate that the model did not perform much better than the null model.
+
+`% deviance explained` is calculated as $\frac{null.deviance - deviance}{null.deviance} * 100$ and expresses the improvement of the fitted model over the null in % deviance explained.
+
+Percent Deviance for model 1a. = `r perc_dev`
+
+#### CPUE Timeline
+
+Because we used area towed in the model as an offset predictions from our model can be interprated as crabs per hectare.
+
+```{r}
+
+#Estimated Marginal Means with an offset
+#parameter in the call of offset = 0:
+modb.dat <- as.data.frame(emmeans(modb, 
+                                  specs = "year_f", 
+                                  by    = "region",
+                                  type  = "response", 
+                                  offset = 0))
+modb.dat$CV <- modb.dat$SE/modb.dat$response
+
+#make scale_x_discrete breaks b/c ggplot is dumb
+ystart <- min(as.numeric(seamap_east$survey_year))
+yend   <- max(as.numeric(seamap_east$survey_year))
+ynames <- lubridate::year(seq.Date(as.Date(paste(ystart), "%Y"), 
+                   as.Date(paste(yend), "%Y"), 
+                   by = "year"))
+
+#ggplot of standardized index of abundance
+p <- modb.dat %>% 
+  mutate(year_n = as.numeric(as.character(year_f))) %>% 
+  ggplot(aes(year_n, response)) +
+      geom_ribbon(aes(year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
+      geom_line(aes(year_n, response, group = 1)) +
+      geom_point(aes(year_n, response)) +
+      geom_hline(aes(yintercept = mean(seamap_east$cpue_towspd)), color = "darkred", linetype = 2) +
+      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
+      labs(
+        x = NULL, 
+        y = "Crabs per Hectare") +
+      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
+      facet_wrap(~region)
+p
+
+```
+
+### Observed vs. Predicted, all model factors
+
+Model prediction (black) & observed mean values (blue), both standardized by overall mean
+
+```{r}
+
+#Estimated Marginal Means with an offset
+#parameter in the call of offset = 0:
+modb.dat <- as.data.frame(emmeans(modb, 
+                                  specs = "year_f", 
+                                  by    = c("region", "season"),
+                                  type  = "response", 
+                                  offset = 0))
+modb.dat$CV <- modb.dat$SE/modb.dat$response
+
+#Drop Infinite credibility intervals
+modb.dat <- modb.dat %>% 
+  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL))
+
+#Observed data
+mean_obs <- mean(seamap_east$cpue_towspd)
+obs_timeline <- seamap_east %>% 
+  group_by(survey_year, region, season) %>% 
+  summarise(Nobs = n(),
+            PercentPos = mean(crab_presence),
+            Mean_CPUE = mean(cpue_towspd)) %>% 
+  mutate(Index_Obs = Mean_CPUE/mean_obs)
+
+#ggplot of standardized index of abundance
+p <- modb.dat %>% 
+  mutate(year_n = as.numeric(as.character(year_f))) %>% 
+  ggplot(aes(year_n, response)) +
+      #Fitted Data
+      geom_ribbon(aes(year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
+      geom_line(aes(year_n, response, group = 1)) +
+      geom_point(aes(year_n, response)) +
+      # Observed Data
+      geom_line(data = obs_timeline, 
+              aes(survey_year, Mean_CPUE, group = region), 
+              col = "royalblue", linetype = 2) +
+      geom_point(data = obs_timeline, 
+                 aes(survey_year, Mean_CPUE, group = region), col = "royalblue") +
+      #Theme changes
+      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
+      labs(
+        x = NULL, 
+        y = "Crabs per Hectare",
+        title = "Model Estimates and Yearly observed means") +
+      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
+      facet_grid(season~region)
+p
+
+```

### 2020-01-08 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
offshore analysis report

@@
----
-title: "Offshore Crabs/Hectare Modeling"
-editor_options: 
-  chunk_output_type: console
----
+---0
 title: "Offshore Indices of Abundance for <br/> Blue Crabs"
@@
 
-**Overall Mean Catch Crabs/Hectare: `r overall_mean`**
-**Stations with no catch: `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`**
+**Overall Mean Catch Crabs/Hectare:** `r overall_mean`
+
+**Stations with no catch:** `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`
 
@@
 
-Percent Deviance for model 1a. = `r perc_dev`
+Percent Deviance for model A. = `r perc_dev`
 
@@
 
-Percent Deviance for model 1a. = `r perc_dev`
+Percent Deviance for model B. = `r perc_dev`
 

### 2020-01-08 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
reorganized report

@@
----0
+---
 title: "Offshore Indices of Abundance for <br/> Blue Crabs"
@@
 
-crabs %>% 
-  mutate(STAT_ZONE = fct_rev(STAT_ZONE)) %>% 
-  ggplot(aes(STAT_ZONE, Sapidus_Catch)) + 
-  geom_boxplot(aes(group = STAT_ZONE)) + 
-  labs(title    = "Blue Crab Catch by Stat Zone", 
-       subtitle = "Stat zones ordered West to East - 2000 to 2018", 
-       x        = "Statistical Zone",
-       y        = "C. sapidus Single Station Catch") +
-  facet_wrap(~Survey_design)
-
 overall_mean <- mean(seamap$CPUE_towspd, na.rm = T)
@@
  * Overall Frequency of Occurrence was `r mean(seamap$Crab_presence, na.rm = TRUE) * 100`
+
+```{r}
+crabs %>% 
+  mutate(STAT_ZONE = fct_rev(STAT_ZONE)) %>% 
+  ggplot(aes(STAT_ZONE, Sapidus_Catch)) + 
+  geom_boxplot(aes(group = STAT_ZONE)) + 
+  labs(title    = "Blue Crab Catch by Stat Zone", 
+       subtitle = "Stat zones ordered West to East - 2000 to 2018", 
+       x        = "Statistical Zone",
+       y        = "C. sapidus Single Station Catch") +
+  facet_wrap(~Survey_design)
+```
 

### 2020-01-10 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
fixed toc
added likelihood ratio test

@@
 ---
-title: "Offshore Indices of Abundance for <br/> Blue Crabs"
+title: "Offshore Blue Crab Densities for <br/> The Gulf of Mexico"
 author: "Adam A Kemberling"
@@
 
-## Model A. 2000-2018 w/ interaction
+## Model A. 2000-2018 {.tabset}
 
@@
 
-### Fit Diagnostics - Deviance
+### Deviance
 
@@
 
-Percent Deviance for model A. = `r perc_dev`
+**Percent Deviance for model A.** = `r perc_dev`
 
-#### CPUE Timeline
+### Likelihood Ratio Test
+
+Significance of the entire factor can be obtained by using a Chi-squared likelihood ratio test.
+
+```{r}
+
+#Drop1 method
+#drop1(mod1a, test = "F")     # F-test
+#drop1(mod1a, test = "Chisq") # Chisq LRT - no scope
+
+#Name what you want to drop
+lrt_y  <- drop1(mod1a, scope = ~ year_f, test = "Chisq")
+lrt_r  <- drop1(mod1a, scope = ~ region, test = "Chisq")
+lrt_s  <- drop1(mod1a, scope = ~ season, test = "Chisq")
+lrt_yr <- drop1(mod1a, scope = ~ year_f*region, test = "Chisq")
+
+bind_rows(
+  list(
+    lrt_y  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor"),
+    lrt_r  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
+    lrt_s  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
+    lrt_yr  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region")
+)) %>% kable()
+
+# #Anova method - LRT
+# 
+# # No interaction - testing
+# mod1_test <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season + 
+#             offset(log(area_hectares)),
+#             data = seamap_west)
+# 
+# anova(mod1a, mod1_test, test = "Chisq")
+```
+
+### CPUE Timeline
 
@@
 
-### Observed vs. Predicted, all model factors
+### Observed vs. Predicted
 
-Model prediction (black) & observed mean values (blue), both standardized by overall mean
+Model prediction (black) & observed mean values (blue)
 
@@
 
-## Model B. 2009-2018
+## Model B. 2009-2018 {.tabset}
 
@@
 
-Percent Deviance for model B. = `r perc_dev`
+**Percent Deviance for model B.** = `r perc_dev`
 
-#### CPUE Timeline
+### Likelihood Ratio Test
+
+```{r}
+
+#Drop1 method
+#drop1(mod1a, test = "F")
+#drop1(modb, test = "Chisq") # no scope
+
+#Name what you want to drop
+lrt_y  <- drop1(modb, scope = ~ year_f, test = "Chisq")
+lrt_r  <- drop1(modb, scope = ~ region, test = "Chisq")
+lrt_s  <- drop1(modb, scope = ~ season, test = "Chisq")
+lrt_yr <- drop1(modb, scope = ~ year_f*region, test = "Chisq")
+
+bind_rows(
+  list(
+    lrt_y  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor"),
+    lrt_r  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
+    lrt_s  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
+    lrt_yr  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region")
+)) %>% kable()
+
+```
+
+### CPUE Timeline
 

### 2020-01-23 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
2020 edits, manuscrpt model

@@
 
-**Overall Mean Catch Crabs/Hectare:** `r overall_mean`
-
-**Stations with no catch:** `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`
+**Overall Mean Catch Crabs/Hectare:** `r round(overall_mean, 3)`
+
+**Stations with no catch:** `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
 
@@
 
-# Crab/hectare Models {.tabset .tabset-pills}
+# East-West Models {.tabset .tabset-pills}
 
@@
 ```
+
+# Manuscript Model {.tabset .tabset-pills }
+
+## Model Dataset
+
+```{r}
+start_year <- min(as.numeric(as.character(seamap_west$survey_year)))
+end_year <- max(as.numeric(as.character(seamap_west$survey_year)))
+total_catch <- sum(seamap_west$sapidus_catch, na.rm = T)
+overall_foa <- mean(seamap_west$crab_presence, na.rm = TRUE) * 100
+overall_mean <- mean(seamap_west$cpue_towspd, na.rm = T)
+percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
+station_count <- seamap_west %>% count()
+```
+
+* Total Number of Stations = `r nrow(seamap_west)`
+
+ * Starting in `r start_year` and continuing through `r end_year`
+
+ * Total Sapidus Caught was `r total_catch`
+
+ * Overall Frequency of Occurrence was `r overall_foa`
+
+ * Overall Mean Catch Crabs/Hectare:** `r round(overall_mean, 3)`
+
+ * Stations with no catch:** `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
+
+## Yearly Catch Plot
+
+## Region - Season Plot
+
+## Seasonal Catch Plot
+
+## Candidate Models
+
+```{r}
+
+#Candidate 1 - no interactions
+candidate_1 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
+            #year_f * region + 
+            offset(log(area_hectares)),
+            data = seamap_west)
+
+#Candidate 2 - year * region
+candidate_2 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
+            year_f * region + 
+            offset(log(area_hectares)),
+            data = seamap_west)
+
+#Candidate 3 - year * season
+candidate_3 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
+            year_f * season + 
+            offset(log(area_hectares)),
+            data = seamap_west)
+
+#Candidate 4 - region * season
+candidate_4 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
+            region * season + 
+            offset(log(area_hectares)),
+            data = seamap_west)
+
+#Candidate 5 - year * region + region * season
+candidate_5 <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
+            year_f * region + region * season +
+            offset(log(area_hectares)),
+            data = seamap_west)
+
+model_list <- list(
+  "no interactions" = candidate_1,
+  "year * region" = candidate_2,
+  "year * season" = candidate_3,
+  "region * season" = candidate_4,
+  "all interactions" = candidate_5
+)
+
+model_aic <- map(model_list,AIC)
+model_aic <- bind_rows(
+  imap(model_aic, function(x,y) {
+    aic_df <- data.frame("Formulation" = y, AIC = x) }
+    )
+  )
+model_aic %>% mutate(`Delta AIC` = AIC - min(AIC)) %>% knitr::kable()
+
+best_mod <- candidate_2
+rm(candidate_1, candidate_2, candidate_3, candidate_4, candidate_5)
+```
+
+## Catch per Hectare Plot

### 2020-01-23 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
updated manuscript figures and models

@@
   scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
-  labs(x = "Survey Year",
+  labs(x = "Region",
        y = "Mean Catch (C. sapidus / Hectare)") + theme(
@@
   scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = "Survey Year",
+  labs(x = "Region",
        y = "Percent Occurrence") + theme(
@@
 
+*NOTE: Zeros removed for plotting*
+
+```{r}
+seamap_west %>% 
+  mutate(year = as.numeric(as.character(year_f))) %>% 
+  filter(cpue_towspd > 0) %>% 
+  ggplot(aes(year, cpue_towspd)) +
+  #geom_boxplot(aes(group = year)) +
+  geom_boxplot(aes(group = year), outlier.shape = NA) +
+  ylim(0, 2) +
+  labs(x = NULL, y = "Crabs / Hectare")
+```
+
 ## Region - Season Plot
+
+*NOTE: Zeros removed for plotting*
+
+```{r}
+region_plot_west <- seamap_west %>% 
+  filter(cpue_towspd > 0) %>% 
+  ggplot(aes(region, cpue_towspd)) +
+  geom_boxplot(aes(fill = season), outlier.shape = NA) +
+   scale_fill_grey(start = 0.3, end = 0.5) +
+  ylim(0, 2) +
+  labs(x = NULL, y = "Crabs / Hectare") + 
+  theme(
+    legend.title = element_blank(),
+    legend.position = c(1, .98),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA)
+    )
+
+season_plot_west <- seamap_west %>% 
+    group_by(region, season) %>% 
+    summarise(
+      stations = n(),
+      `missing obs`     = sum(is.na(cpue_towspd)),
+      `% Occurrence` = mean(crab_presence, na.rm = T),
+      `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(stations - `missing obs`)) %>% 
+    mutate(
+      occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+      occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+      occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+    ) %>% 
+  ggplot(aes(region, `% Occurrence`)) +
+    geom_pointrange(aes(ymin = occurrence_ymin, 
+                        ymax = occurrence_ymax, 
+                        shape = season, 
+                        color = season)) +
+    scale_color_grey(start = 0.3, end = 0.5) +
+    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
+    labs(x = NULL, y = "Percent Occurrence") + 
+  theme(
+    legend.title = element_blank(),
+    legend.position = c(1, .98),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA)
+    )
+
+region_plot_west + season_plot_west
+
+```
 

### 2020-01-27 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
manuscript plot updates

@@
                              panel.grid.minor = element_blank(), 
-                             panel.border = element_rect(fill = NA)))
+                             panel.border = element_rect(fill = NA),
+                             axis.text = element_text(size = 12),
+                             axis.title = element_text(size = 14)))
 
@@
 ```{r}
-seamap <- seamap %>% rename_all(tolower)
+seamap <- seamap %>% rename_all(tolower) %>% filter(statzone != 12)
 seamap_west <- seamap %>% 
-  filter(statzone != 12,
-         statzone %in% 11:21) %>% 
+  filter(statzone %in% 11:21) %>% 
   mutate(statzone = factor(statzone))
@@
 
+The following numbers are from the Western Gulf Dataset used in the generalized linear model*
+
 ```{r}
@@
 
+*NOTE: Contains Data Across All Years and Regions (Including Florida)*
+
+```{r}
+year_sums <- seamap %>% 
+  group_by(survey_year) %>% 
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(cpue_towspd)),
+            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
+            `SD`              = sd(cpue_towspd, na.rm = T),
+            `Var`             = var(cpue_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+            `% Occurrence`    = mean(crab_presence, na.rm = T),
+            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+  ungroup() %>% 
+    mutate(Survey_Year        = factor(survey_year),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+         )
+
+year_sums %>% select(`Survey Year` = survey_year, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
+
+year_plot <- year_sums %>% 
+  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
+  ggplot() +
+    geom_col(aes(survey_year, `Mean Catch`)) +
+    geom_errorbar(aes(x = survey_year, 
+                      ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  size = .25) +
+  labs(x = NULL,
+       y = "Mean Catch (C. sapidus / Hectare)")
+
+year_plot
+
+year_foa <- year_sums %>% 
+  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
+  ggplot() +
+    geom_col(aes(survey_year, `% Occurrence`)) +
+    geom_errorbar(aes(x = survey_year, 
+                      ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  size = .25) +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = NULL, y = "Percent Occurrence")
+
+year_foa
+
+year_plot + year_foa
+```
+
+## Region - Season Plot
+
 *NOTE: Zeros removed for plotting*
@@
 ```{r}
-seamap_west %>% 
-  mutate(year = as.numeric(as.character(year_f))) %>% 
-  filter(cpue_towspd > 0) %>% 
-  ggplot(aes(year, cpue_towspd)) +
-  #geom_boxplot(aes(group = year)) +
-  geom_boxplot(aes(group = year), outlier.shape = NA) +
-  ylim(0, 2) +
-  labs(x = NULL, y = "Crabs / Hectare")
-```
-
-## Region - Season Plot
-
-*NOTE: Zeros removed for plotting*
-
-```{r}
-region_plot_west <- seamap_west %>% 
-  filter(cpue_towspd > 0) %>% 
-  ggplot(aes(region, cpue_towspd)) +
-  geom_boxplot(aes(fill = season), outlier.shape = NA) +
-   scale_fill_grey(start = 0.3, end = 0.5) +
-  ylim(0, 2) +
-  labs(x = NULL, y = "Crabs / Hectare") + 
-  theme(
-    legend.title = element_blank(),
-    legend.position = c(1, .98),
+rs_summary <- seamap %>% 
+  filter(is.na(region)      == FALSE) %>% 
+  group_by(region, season) %>% 
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(cpue_towspd)),
+            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
+            `SD`              = sd(cpue_towspd, na.rm = T),
+            `Var`             = var(cpue_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+            `% Occurrence`    = mean(crab_presence, na.rm = T),
+            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+    ungroup() %>% 
+    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
+           region             = factor(region, 
+                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
+           #region             = fct_rev(region),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+    )
+
+#Summary Table
+rs_summary %>% 
+  select(Region = region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
+  knitr::kable()
+
+# Plot
+rs_plot <- rs_summary %>% 
+  ggplot(aes(region, `Mean Catch`, fill = season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  position = "dodge", 
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  labs(x = NULL,
+       y = "Mean Catch (C. sapidus / Hectare)") + theme(
+    legend.position = c(1, .95),
     legend.justification = c("right", "top"),
@@
     legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA)
-    )
-
-season_plot_west <- seamap_west %>% 
-    group_by(region, season) %>% 
-    summarise(
-      stations = n(),
-      `missing obs`     = sum(is.na(cpue_towspd)),
+    legend.background = element_rect(fill = NA))
+
+rs_plot
+
+rs_plot_2 <- rs_summary %>% 
+  ggplot(aes(region, `% Occurrence`, fill = Season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  position = "dodge",
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = NULL,
+       y = "Percent Occurrence") + theme(
+    legend.position = c(1, .95),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA))
+
+rs_plot_2
+
+rs_plot + rs_plot_2
+
+```
+
+## Seasonal Catch Plot
+
+```{r}
+season_summary <- seamap %>% 
+  group_by(survey_year, season) %>% 
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(cpue_towspd)),
+            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
+            `SD`              = sd(cpue_towspd, na.rm = T),
+            `Var`             = var(cpue_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
             `% Occurrence`    = mean(crab_presence, na.rm = T),
-      `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(stations - `missing obs`)) %>% 
-    mutate(
+            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+    ungroup() %>% 
+    mutate(survey_year        = factor(survey_year),
+           # StatZone         = factor(StatZone),
+           # StatZone         = fct_rev(StatZone),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
            occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
@@
            occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-    ) %>% 
-  ggplot(aes(region, `% Occurrence`)) +
-    geom_pointrange(aes(ymin = occurrence_ymin, 
-                        ymax = occurrence_ymax, 
-                        shape = season, 
-                        color = season)) +
-    scale_color_grey(start = 0.3, end = 0.5) +
-    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
-    labs(x = NULL, y = "Percent Occurrence") + 
-  theme(
-    legend.title = element_blank(),
-    legend.position = c(1, .98),
+         )
+
+season_summary %>% select(`Survey Year` = survey_year, Season = season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
+
+season_plot <- season_summary %>% 
+  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
+  ggplot(aes(survey_year, `Mean Catch`, fill = season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  position = "dodge",
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  labs(x = NULL,
+       y = "Mean Catch (C. sapidus / Hectare)") + theme(
+    legend.position = c(1, .95),
     legend.justification = c("right", "top"),
@@
     legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA)
-    )
-
-region_plot_west + season_plot_west
-
-```
-
-## Seasonal Catch Plot
+    legend.background = element_rect(fill = NA))
+
+season_plot
+
+season_plot_2 <- season_summary %>% 
+  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
+  ggplot(aes(survey_year, `% Occurrence`, fill = season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  position = "dodge",
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = "Survey Year",
+       y = "Percent Occurrence") + theme(
+    legend.position = c(1, .95),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA))
+
+season_plot_2
+
+season_plot + season_plot_2
+```
 

### 2020-01-28 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
model updates

@@
 
-The following numbers are from the Western Gulf Dataset used in the generalized linear model*
-
-```{r}
+**The following numbers are from all usable data from 2000-2018**
+
+```{r seamap all stats}
+start_year <- min(as.numeric(as.character(seamap$survey_year)))
+end_year <- max(as.numeric(as.character(seamap$survey_year)))
+total_catch <- sum(seamap$sapidus_catch, na.rm = T)
+overall_foa <- mean(seamap$crab_presence, na.rm = TRUE) * 100
+overall_mean <- mean(seamap$cpue_towspd, na.rm = T)
+percent_zeros <- seamap %>% filter(sapidus_catch == 0) %>% count()
+station_count <- seamap %>% count()
+
+#seamap %>% group_by(survey_year) %>% summarise(foa = mean(crab_presence)) %>% arrange(foa)
+
+```
+
+ * Total Number of Stations = `r nrow(seamap)`
+
+ * Starting in `r start_year` and continuing through `r end_year`
+
+ * Total Sapidus Caught was `r total_catch`
+
+ * Overall Frequency of Occurrence was `r overall_foa`
+
+ * Overall Mean Catch Crabs/Hectare: `r overall_mean`
+
+ * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
+
+**The following numbers are from the Western Gulf Dataset used in the generalized linear model**
+
+```{r seamap west stats}
 start_year <- min(as.numeric(as.character(seamap_west$survey_year)))
@@
 overall_foa <- mean(seamap_west$crab_presence, na.rm = TRUE) * 100
-overall_mean <- mean(seamap_west$cpue_towspd, na.rm = T)
+overall_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
 percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
 station_count <- seamap_west %>% count()
+
 ```
@@
 
- * Overall Mean Catch Crabs/Hectare:** `r round(overall_mean, 3)`
-
- * Stations with no catch:** `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
+ * Overall Mean Catch Crabs/Hectare: `r overall_mean`
+
+ * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
 
@@
 
-*NOTE: Zeros removed for plotting*
+*NOTE: Contains Data Across All Years and Regions (Including Florida)*
 
@@
   labs(x = NULL,
-       y = "Mean Catch (C. sapidus / Hectare)") + theme(
+       y = "Mean Catch (C. sapidus / Hectare)") + 
+  theme(
     legend.position = c(1, .95),
@@
 
+**Model Selection using AIC**
+
 ```{r}
@@
 
+**Predictor Significance using Chi-Square LRT and Deviance**
+
+```{r}
+
+#Drop1 method
+#drop1(mod1a, test = "F")     # F-test
+#drop1(mod1a, test = "Chisq") # Chisq LRT - no scope
+
+#Name what you want to drop
+lrt_y  <- drop1(mod1a, scope = ~ year_f, test = "Chisq")
+lrt_r  <- drop1(mod1a, scope = ~ region, test = "Chisq")
+lrt_s  <- drop1(mod1a, scope = ~ season, test = "Chisq")
+lrt_yr <- drop1(mod1a, scope = ~ year_f*region, test = "Chisq")
+
+bind_rows(
+  list(
+    lrt_y  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor"),
+    lrt_r  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
+    lrt_s  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
+    lrt_yr  %>% as.data.frame() %>% 
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region")
+)) %>% kable()
+
+#broom::glance(best_mod) %>% kable()
+#Percent deviance explained
+perc_dev <- (best_mod$null.deviance - best_mod$deviance) / best_mod$null.deviance
+perc_dev <- round(perc_dev * 100,2)
+```
+
+*Percent Deviance Explained by Best Candidate Model:* `r perc_dev`
+
 ## Catch per Hectare Plot
+
+```{r}
+
+#Estimated Marginal Means with an offset
+#parameter in the call of offset = 0:
+best_mod_dat <- as.data.frame(emmeans(best_mod, 
+                                  specs = "year_f", 
+                                  by    = c("region", "season"),
+                                  type  = "response", 
+                                  offset = 0))
+best_mod_dat$CV <- best_mod_dat$SE/best_mod_dat$response
+
+#Drop Infinite credibility intervals
+best_mod_dat <- best_mod_dat %>% 
+  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL))
+
+# #Observed data
+# mean_obs <- mean(seamap_west$cpue_towspd)
+# obs_timeline <- seamap_west %>% 
+#   group_by(survey_year, region, season) %>% 
+#   summarise(Nobs = n(),
+#             PercentPos = mean(crab_presence),
+#             Mean_CPUE = mean(cpue_towspd)) %>% 
+#   mutate(Index_Obs = Mean_CPUE/mean_obs)
+
+#ggplot of standardized index of abundance
+p <- best_mod_dat %>% 
+  mutate(year_n = as.numeric(as.character(year_f))) %>% 
+  ggplot(aes(year_n, response)) +
+      #Fitted Data
+      geom_line(aes(year_n, response, color = season)) +
+      geom_point(aes(year_n, response, color = season, shape = season)) +
+      # Observed Data
+      # geom_line(data = obs_timeline, 
+      #         aes(survey_year, Mean_CPUE, group = region), 
+      #         col = "royalblue", linetype = 2) +
+      # geom_point(data = obs_timeline, 
+      #            aes(survey_year, Mean_CPUE, group = region), col = "royalblue") +
+      scale_color_grey(start = 0.2, end = 0.6) + 
+      labs(
+        x = NULL, 
+        y = "Crabs per Hectare",
+        title = "Model Estimates and Yearly observed means") +
+      facet_grid(region ~ .) +
+  theme(
+    legend.position = c(1, .98),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA),
+    legend.title = element_blank())
+p
+
+```

### 2020-01-29 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
end of offshore model

@@
 
-## Candidate Models
-
-**Model Selection using AIC**
+## Candidate Models {.tabset}
+
+### Model Selection using AIC
 
@@
 
-**Predictor Significance using Chi-Square LRT and Deviance**
+### Predictor Significance
 
@@
     lrt_s  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
+      rownames_to_column(var = "Predictor") %>% filter(Predictor == "season"),
     lrt_yr  %>% as.data.frame() %>% 
@@
 *Percent Deviance Explained by Best Candidate Model:* `r perc_dev`
+
+### Model Summary
+
+Statistic reported below is the Wald Chi-Square z-score.
+
+```{r}
+#summary(best_mod) #to see what test statistic is used
+broom::tidy(best_mod) %>% kable()
+```
+
+### Interaction Plot
+
+```{r}
+emmip(best_mod, region ~ year_f, type = "response", offset = 0) + labs(x = NULL, caption = "Interaction Plot for year * region factors")
+```
 
@@
 
-# #Observed data
-# mean_obs <- mean(seamap_west$cpue_towspd)
-# obs_timeline <- seamap_west %>% 
-#   group_by(survey_year, region, season) %>% 
-#   summarise(Nobs = n(),
-#             PercentPos = mean(crab_presence),
-#             Mean_CPUE = mean(cpue_towspd)) %>% 
-#   mutate(Index_Obs = Mean_CPUE/mean_obs)
-
-#ggplot of standardized index of abundance
+# Catch Plot
 p <- best_mod_dat %>% 
@@
   ggplot(aes(year_n, response)) +
-      #Fitted Data
       geom_line(aes(year_n, response, color = season)) +
       geom_point(aes(year_n, response, color = season, shape = season)) +
-      # Observed Data
-      # geom_line(data = obs_timeline, 
-      #         aes(survey_year, Mean_CPUE, group = region), 
-      #         col = "royalblue", linetype = 2) +
-      # geom_point(data = obs_timeline, 
-      #            aes(survey_year, Mean_CPUE, group = region), col = "royalblue") +
       scale_color_grey(start = 0.2, end = 0.6) + 

### 2020-01-29 2019_edits/R/fecundity_analyses/egg_models_2.Rmd
paths changed for reproductive analyses

--- 2019-12-31 2019_edits/R/fecundity_code/egg_models_2.Rmd
@@
 
-#Egg Data
-eggdat <- read_csv(here("data/repo/seamap_summerandfall2017_crabs.csv"), guess_max = 10000, col_types = cols())
+#Egg Data - one record per egg
+eggdat <- read_csv("~/Dropbox/SEAMAP_2019/data/repro/seamap_summerandfall2017_crabs.csv", 
+                   guess_max = 10000, col_types = cols())
+
 eggdat <- eggdat %>% 
@@
 
-#Stations
-stat_dat <- read_csv(here("data/repo/2017_allcrabs_onerow_withstationdata.csv"), guess_max = 10000, col_types = cols())
+#Stations - one row per crab record
+stat_dat <- read_csv("~/Dropbox/SEAMAP_2019/data/repro/2017_allcrabs_onerow_withstationdata.csv", 
+                     guess_max = 10000, col_types = cols())
 eggdat <- stat_dat %>%  
@@
 # Add the statzone using statzone polygon - use this to make regions consistent between models
-szones <- read_sf(here("data/gis_files","NMFS_Fishing_Grids_GOM_2013.shp"), crs = 4326)
+szones <- read_sf("~/Dropbox/SEAMAP_2019/data/gis_files/NMFS_Fishing_Grids_GOM_2013.shp", crs = 4326)
 

### 2020-02-04 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
effort and catch maps added

@@
             `% Occurrence`    = mean(crab_presence, na.rm = T),
-            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)
+            ) %>% 
   ungroup() %>% 
@@
     geom_col(aes(survey_year, `% Occurrence`)) +
-    geom_errorbar(aes(x = survey_year, 
-                      ymin = occurrence_ymin,
-                      ymax = occurrence_ymax),
-                  size = .25) +
+    # geom_errorbar(aes(x = survey_year, 
+    #                   ymin = occurrence_ymin,
+    #                   ymax = occurrence_ymax),
+    #               size = .25) +
   scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
@@
 
-```{r}
+*NOTE 2: Mean Catch (per hectare) and frequency of occurrence calculated for each year, in each region, for each season. The mean and standard error of those annual measurements are then taken*
+
+```{r old}
+# rs_summary <- seamap %>% 
+#   filter(is.na(region)      == FALSE) %>% 
+#   group_by(region, season) %>% 
+#   summarise(Stations          = n(),
+#             `Missing Obs`     = sum(is.na(cpue_towspd)),
+#             `Mean Catch`      = mean(cpue_towspd, na.rm = T),
+#             `SD`              = sd(cpue_towspd, na.rm = T),
+#             `Var`             = var(cpue_towspd),
+#             `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+#             `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+#             `% Occurrence`    = mean(crab_presence, na.rm = T),
+#             `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+#     ungroup() %>% 
+#     mutate(Season             = factor(season, levels = c("Summer", "Fall")),
+#            region             = factor(region, 
+#                                        levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
+#            #region             = fct_rev(region),
+#            catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+#            catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+#            catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+#            occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+#            occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+#            occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+#     )
+
+# #Summary Table
+# rs_summary %>% 
+#   select(Region = region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
+#   knitr::kable()
+
+#Calaculate Annual average cpue and percent occurrence
 rs_summary <- seamap %>% 
-  filter(is.na(region)      == FALSE) %>% 
+  group_by(survey_year, region, season) %>% 
+  summarise(cpue = mean(cpue_towspd, na.rm = T),
+            percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
   group_by(region, season) %>% 
-  summarise(Stations          = n(),
-            `Missing Obs`     = sum(is.na(cpue_towspd)),
-            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
-            `SD`              = sd(cpue_towspd, na.rm = T),
-            `Var`             = var(cpue_towspd),
-            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-            `% Occurrence`    = mean(crab_presence, na.rm = T),
-            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+  summarise(nyears = n(),
+            avg_annual_cpue = mean(cpue, na.rm = T),
+            annual_cpue_se = sd(cpue, na.rm = T) / sqrt(nyears),
+            avg_percent_occurrence = mean(percent_occurrence, na.rm = T),
+            po_se = sd(percent_occurrence, na.rm = T) / sqrt(nyears)) %>% 
     ungroup() %>%
     mutate(Season             = factor(season, levels = c("Summer", "Fall")),
-           region             = factor(region, 
-                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
-           #region             = fct_rev(region),
-           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           region             = factor(region, levels = c("Texas", "Louisiana", 
+                                                          "MS Bight", "Florida")),
+           catch_ymin         = avg_annual_cpue - (2 * annual_cpue_se),
+           catch_ymax         = avg_annual_cpue + (2 * annual_cpue_se),
            catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-    )
-
-#Summary Table
-rs_summary %>% 
-  select(Region = region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
-  knitr::kable()
+           occurrence_ymin    = avg_percent_occurrence - (2 * po_se),
+           occurrence_ymax    = avg_percent_occurrence + (2 * po_se),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin),
+           occurrence_ymax    = ifelse(occurrence_ymax > 1, 1, occurrence_ymax)
+    )
 
@@
 rs_plot <- rs_summary %>% 
-  ggplot(aes(region, `Mean Catch`, fill = season)) +
+  ggplot(aes(region, avg_annual_cpue, fill = season)) +
     geom_col(position = "dodge") +
@@
 rs_plot_2 <- rs_summary %>% 
-  ggplot(aes(region, `% Occurrence`, fill = Season)) +
+  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
     geom_col(position = "dodge") +
@@
 
-```{r}
+*NOTE 2: Mean Catch (per hectare) and frequency of occurrence calculated for each year, for each season. The mean and standard error of those annual measurements are then taken*
+
+```{r}
+# season_summary <- seamap %>% 
+#   group_by(survey_year, season) %>% 
+#   summarise(Stations          = n(),
+#             `Missing Obs`     = sum(is.na(cpue_towspd)),
+#             `Mean Catch`      = mean(cpue_towspd, na.rm = T),
+#             `SD`              = sd(cpue_towspd, na.rm = T),
+#             `Var`             = var(cpue_towspd),
+#             `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+#             `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
+#             `% Occurrence`    = mean(crab_presence, na.rm = T),
+#             `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+#     ungroup() %>% 
+#     mutate(survey_year        = factor(survey_year),
+#            # StatZone         = factor(StatZone),
+#            # StatZone         = fct_rev(StatZone),
+#            catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+#            catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+#            catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
+#            occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
+#            occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
+#            occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
+#          )
+# 
+# season_summary %>% select(`Survey Year` = survey_year, Season = season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
+
+#Calaculate Annual average cpue and percent occurrence
 season_summary <- seamap %>% 
   group_by(survey_year, season) %>% 
-  summarise(Stations          = n(),
-            `Missing Obs`     = sum(is.na(cpue_towspd)),
-            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
-            `SD`              = sd(cpue_towspd, na.rm = T),
-            `Var`             = var(cpue_towspd),
-            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-            `% Occurrence`    = mean(crab_presence, na.rm = T),
-            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
+  summarise(cpue = mean(cpue_towspd, na.rm = T),
+            percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
+  group_by(season) %>% 
+  summarise(nyears = n(),
+            avg_annual_cpue = mean(cpue, na.rm = T),
+            annual_cpue_se = sd(cpue, na.rm = T) / sqrt(nyears),
+            avg_percent_occurrence = mean(percent_occurrence, na.rm = T),
+            po_se = sd(percent_occurrence, na.rm = T) / sqrt(nyears)) %>% 
     ungroup() %>%
-    mutate(survey_year        = factor(survey_year),
-           # StatZone         = factor(StatZone),
-           # StatZone         = fct_rev(StatZone),
-           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
+           catch_ymin         = avg_annual_cpue - (2 * annual_cpue_se),
+           catch_ymax         = avg_annual_cpue + (2 * annual_cpue_se),
            catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-         )
-
-season_summary %>% select(`Survey Year` = survey_year, Season = season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
+           occurrence_ymin    = avg_percent_occurrence - (2 * po_se),
+           occurrence_ymax    = avg_percent_occurrence + (2 * po_se),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin),
+           occurrence_ymax    = ifelse(occurrence_ymax > 1, 1, occurrence_ymax)
+    )
 
 season_plot <- season_summary %>% 
-  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
-  ggplot(aes(survey_year, `Mean Catch`, fill = season)) +
-    geom_col(position = "dodge") +
+  ggplot(aes(season, avg_annual_cpue, fill = season)) +
+    geom_col() +
     geom_errorbar(aes(ymin = catch_ymin,
                       ymax = catch_ymax),
-                  position = "dodge",
                   size = .25) +
@@
 season_plot_2 <- season_summary %>% 
-  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
-  ggplot(aes(survey_year, `% Occurrence`, fill = season)) +
+  ggplot(aes(season, avg_percent_occurrence, fill = season)) +
     geom_col(position = "dodge") +
@@
                       ymax = occurrence_ymax),
-                  position = "dodge",
                   size = .25) +
@@
   scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = "Survey Year",
+  labs(x = NULL,
        y = "Percent Occurrence") + theme(
@@
 ```
+
+## Spatial Grids  {.tabset}
+
+```{r}
+
+library(stars)
+library(sf)
+library(rnaturalearth)
+
+#State and Country Bounds
+usmap <- ne_states(country = "united states of america") %>% 
+  st_as_sf() %>% 
+  filter(region == "South")
+
+mex <- ne_states(country = "mexico") %>% 
+  st_as_sf()
+
+#Custom grid for rasterize
+test_bbox <- st_bbox(c(xmin = -97.5, xmax = -81,
+                       ymin = 24.3, ymax = 30.5),
+                     crs = st_crs(4326))
+
+num_x <- seq(from = -97.4, to = -81.3, by = 0.2)
+num_y <- seq(from = 24.4, to = 30.4, by = 0.2)
+
+####  Aggregation  ####
+#Aggregating the seamap model into bins
+seamap_sf_agg <- seamap %>% 
+  mutate(lon_bin = round(start_long, 1),
+         lat_bin = round(start_lat, 1)) %>% 
+  group_by(lon_bin, lat_bin) %>% 
+  summarise(n_stations = n(),
+            total_catch = sum(sapidus_catch, na.rm = T),
+            avg_cpue = mean(cpue_towspd)) %>% 
+  st_as_sf(coords = c("lon_bin", "lat_bin"), crs = 4326, remove = FALSE)
+
+####  Total Catch  ####
+
+#Convert to Raster and plot 
+catch_ras <- st_rasterize(
+  seamap_sf_agg["total_catch"],
+  template = st_as_stars(
+      test_bbox,
+      #st_bbox(seamap_sf), 
+      values = NA_real_,
+      nx = length(num_x),
+      ny = length(num_y))
+  )
+
+#plot(catch_ras, axes = T, main = "Total Sapidus Catch - All Years 2000+")
+
+####  Mean CPUE  ####
+
+cpue_ras <- st_rasterize(
+  seamap_sf_agg["avg_cpue"],
+  template = st_as_stars(
+      test_bbox,
+      #st_bbox(seamap_sf), 
+      values = NA_real_,
+      nx = length(num_x),
+      ny = length(num_y))
+  )
+
+#plot(cpue_ras, axes = T, main = " Mean Catch/Hectare - All Years 2000+")
+
+####  Sampling Effort  ####
+effort_ras <- st_rasterize(
+  seamap_sf_agg["n_stations"],
+  template = st_as_stars(
+      test_bbox,
+      #st_bbox(seamap_sf), 
+      values = NA_real_,
+      nx = length(num_x),
+      ny = length(num_y))
+  )
+
+```
+
+### Sampling Effort
+
+```{r}
+####  Sampling Effort  ####
+ggplot() +
+  geom_stars(data = effort_ras) +
+  geom_sf(data = usmap) +
+  geom_sf(data = mex) +
+  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
+  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
+  labs(x = NULL, y = NULL) +
+  guides(fill = guide_colorbar(title = "Total Sampling Effort (Stations)",
+                               title.hjust = 0.5, 
+                               title.position = "top",
+                               barwidth = 10)) +
+  theme(legend.position = "bottom")
+```
+
+### Catch per Hectare
+
+```{r}
+
+####  CPUE  ####
+ggplot() +
+  geom_stars(data = cpue_ras) +
+  geom_sf(data = usmap) +
+  geom_sf(data = mex) +
+  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
+  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
+  labs(x = NULL, y = NULL) +
+  guides(fill = guide_colorbar(title = "Average Catch/Hectare",
+                               title.hjust = 0.5, 
+                               title.position = "top",
+                               barwidth = 10)) +
+  theme(legend.position = "bottom")
+
+```
+
+### Total Catch
+
+```{r}
+####  Total Catch  ####
+ggplot() +
+  geom_stars(data = catch_ras) +
+  geom_sf(data = usmap) +
+  geom_sf(data = mex) +
+  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
+  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
+  labs(x = NULL, y = NULL) +
+  guides(fill = guide_colorbar(title = "Total C. sapidus Caught",
+                               title.hjust = 0.5, 
+                               title.position = "top",
+                               barwidth = 10)) +
+  theme(legend.position = "bottom")
+
+```

### 2020-02-10 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
pulled manuscript edits out into their own markdown

--- 2020-02-04 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
@@
 ---
-title: "Offshore Blue Crab Densities for <br/> The Gulf of Mexico"
-author: "Adam A Kemberling"
-date: "1/4/2020"
+title: "Offshore Modeling - Manuscript Model"
+author: "Adam A. Kemberling"
+date: "`r Sys.Date()`"
 output: 
@@
                              panel.border = element_rect(fill = NA),
-                             axis.text = element_text(size = 12),
-                             axis.title = element_text(size = 14)))
+                             axis.text = element_text(size = 12, color = "black"),
+                             axis.title = element_text(size = 14, color = "black")))
 
@@
 
-```{r data}
-seamap <- read_csv("~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019.csv",
-                   guess_max = 1e6, 
-                   col_types = cols())
-
-#Set up Season Column, using survey titles
-seamap[str_detect(seamap$TITLE, "Fall"),"Season"]   <- "Fall"
-seamap[str_detect(seamap$TITLE, "Winter"),"Season"] <- "Winter"
-seamap[str_detect(seamap$TITLE, "Summer"),"Season"] <- "Summer"
-seamap[str_detect(seamap$TITLE, "Spring"),"Season"] <- "Spring"
-
-# Make any setup changes
-seamap <- seamap %>% 
-  mutate(STAT_ZONE     = factor(STAT_ZONE),
-         Crab_presence = ifelse(Sapidus_Catch > 0, 1, 0),
-         Survey_Year   = as.numeric(Survey_Year),
-         Season        = factor(Season, levels = c("Summer","Fall","Winter")),
-         Survey_Month  = lubridate::month(Date),
-         Survey_Month  = factor(Survey_Month),
-         Survey_design = ifelse(Survey_Year < 2009, "Old Design", "Current Design"),
-         Survey_design = ifelse(Survey_Year == 2008 & Season == "Fall", "Current Design", Survey_design),
-         Survey_design = factor(Survey_design, levels = c("Old Design", "Current Design")),
-         ####  More changes from DE
-         Year_f             =  factor(Survey_Year),
-         Month_f            =  factor(Survey_Month),
-         Depth              =  (Start_Depth + End_Depth)/2,
-         Temp_std           =  (Temp_B- mean(Temp_B))/ mean(Temp_B),
-         Salinity_std       =  (Salinity_B- mean(Salinity_B))/ mean(Salinity_B),
-         Depth_std          =  (Depth- mean(Depth))/ mean(Depth))
-
-# Do all filtering
-seamap <- seamap %>% 
-  filter(Season            !=  "Winter",
-         Survey_Year     %in%  c(2000:2018),
-         Spd_kmh           !=  0,                    #these are infinite cpue
-         Depth             <=  110)
-
-# Catch only set
-crabs <- seamap %>% filter(Sapidus_Catch > 0)
-
-overall_mean <- mean(seamap$CPUE_towspd, na.rm = T)
-percent_zeros <- seamap %>% filter(Sapidus_Catch == 0) %>% count()
-station_count <- seamap %>% count()
-```
-
-# Data Set Summary
-
- * Total Number of Stations = `r nrow(seamap)`
-
- * Starting in `r min(as.numeric(as.character(seamap$Survey_Year)))` and continuing through `r max(as.numeric(as.character(seamap$Survey_Year)))`
-
- * Total Sapidus Caught was `r sum(seamap$Sapidus_Catch, na.rm = T)`
-
- * Overall Frequency of Occurrence was `r mean(seamap$Crab_presence, na.rm = TRUE) * 100`
-
-```{r}
-crabs %>% 
-  mutate(STAT_ZONE = fct_rev(STAT_ZONE)) %>% 
-  ggplot(aes(STAT_ZONE, Sapidus_Catch)) + 
-  geom_boxplot(aes(group = STAT_ZONE)) + 
-  labs(title    = "Blue Crab Catch by Stat Zone", 
-       subtitle = "Stat zones ordered West to East - 2000 to 2018", 
-       x        = "Statistical Zone",
-       y        = "C. sapidus Single Station Catch") +
-  facet_wrap(~Survey_design)
-```
-
-# Factor Summaries
-
-## Yearly Summaries {.tabset .tabset-fade .tabset-pills}
-
-**Overall Mean Catch Crabs/Hectare:** `r round(overall_mean, 3)`
-
-**Stations with no catch:** `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
-
-```{r}
-year_sums <- seamap %>% 
-  group_by(Survey_Year) %>% 
-  summarise(Stations          = n(),
-            `Missing Obs`     = sum(is.na(CPUE_towspd)),
-            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
-            `SD`              = sd(CPUE_towspd, na.rm = T),
-            `Var`             = var(CPUE_towspd),
-            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-            `% Occurrence`    = mean(Crab_presence, na.rm = T),
-            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
-  ungroup() %>% 
-    mutate(Survey_Year        = factor(Survey_Year),
-           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
-           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-         )
-
-year_sums %>% select(Survey_Year, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
-#knitr::kable(year_sums)
-```
-
-***
-
-### Yearly Catch Plot
-
-```{r}
-
-year_plot_1 <- year_sums %>% 
-  ggplot() +
-    geom_col(aes(Survey_Year, `Mean Catch`)) +
-    geom_errorbar(aes(x = Survey_Year, 
-                      ymin = catch_ymin,
-                      ymax = catch_ymax),
-                  size = .25) +
-  labs(x = "Survey Year",
-       y = "Mean Catch (C. sapidus / Hectare)") +
-  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
-
-year_plot_1
-#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)
-
-```
-
-***
-
-### Yearly Frequency of Occurrence
-
-```{r}
-
-year_plot_2 <- year_sums %>% 
-  ggplot() +
-    geom_col(aes(Survey_Year, `% Occurrence`)) +
-    geom_errorbar(aes(x = Survey_Year, 
-                      ymin = occurrence_ymin,
-                      ymax = occurrence_ymax),
-                  size = .25) +
-  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = "Survey Year",
-       y = "Percent Occurrence") +
-  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
-
-year_plot_2
-#ggsave(plot = year_plot_2, here("2019_edits/figures", "yearly_occurrence.png"), dpi = 600)
-
-```
-
-***
-
-### Yearly Side-by
-
-```{r}
-year_plot_1 + year_plot_2
-```
-
-***
-
-## Stat Zone Summaries {.tabset .tabset-fade .tabset-pills}
-
-```{r}
-#Assign Stat Zone from NMFS grid
-szones <- read_sf("~/Dropbox/SEAMAP_2019/data/gis_files/NMFS_Fishing_Grids_GOM_2013.shp", 
-                  crs = 4326)
-
-# Add a better StatZone ID by spatial overlap
-seamap <- seamap %>% 
-  st_as_sf(coords = c("Start_Long", "Start_Lat"), crs = 4326, remove = FALSE) %>% 
-  st_join(szones["StatZone"]) %>% 
-  st_set_geometry(NULL) %>% 
-  as.data.frame() %>% 
-  dplyr::select(-STAT_ZONE) %>%  #Remove default/incorrect one
-  mutate(StatZone = factor(StatZone))
-
-szone_summary <- seamap %>% 
-  filter(is.na(StatZone)      == FALSE) %>% 
-  group_by(StatZone) %>% 
-  summarise(Stations          = n(),
-            `Missing Obs`     = sum(is.na(CPUE_towspd)),
-            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
-            `SD`              = sd(CPUE_towspd, na.rm = T),
-            `Var`             = var(CPUE_towspd),
-            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-            `% Occurrence`    = mean(Crab_presence, na.rm = T),
-            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
-    ungroup() %>% 
-    mutate(StatZone           = factor(StatZone),
-           StatZone           = fct_rev(StatZone),
-           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
-           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-         )
-
-szone_summary %>% 
-  select(StatZone, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
-  knitr::kable()
-
-```
-
-***
-
-### Stat Zone Catch Plot
-
-```{r}
-
-szones_plot_1 <- szone_summary %>% 
-  ggplot() +
-    geom_col(aes(StatZone, `Mean Catch`)) +
-    geom_errorbar(aes(x = StatZone, 
-                      ymin = catch_ymin,
-                      ymax = catch_ymax),
-                  size = .25) +
-  geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
-  geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
-  #annotate(geom = "text", x = 7, y = 2.0, label = "LA + MS") +
-  #annotate(geom = "text", x = 16, y = 2.0, label = "East of Mobile Bay") +
-  annotate(geom = "text", x = 16.5, y = -0.1, label = "East of Mobile Bay") +
-  annotate(geom = "text", x = 8, y = -0.1, label = "LA & MS") +
-  annotate(geom = "text", x = 2.5, y = -0.1, label = "Texas") +
-    labs(x= "Statistical Zone",
-         y = "Mean Catch (C. sapidus / Hectare)")
-
-szones_plot_1 
-#ggsave(plot = szones_plot_1, here("2019_edits/figures", "statzones_catch.png"), dpi = 600)
-
-```
-
-***
-
-### Stat Zone Frequency of Occurrence
-
-```{r}
-
-szones_plot_2 <- szone_summary %>% 
-  ggplot() +
-    geom_col(aes(StatZone, `% Occurrence`)) +
-    geom_errorbar(aes(x = StatZone, 
-                      ymin = occurrence_ymin,
-                      ymax = occurrence_ymax),
-                  size = .25) +
-  geom_vline(xintercept = 11.5, color = "gray", lty = 2) +
-  geom_vline(xintercept = 4.5, color = "gray", lty = 2) +
-  annotate(geom = "text", x = 16.5, y = 0.75, label = "East of Mobile Bay") +
-  annotate(geom = "text", x = 8, y = 0.75, label = "LA & MS") +
-  annotate(geom = "text", x = 2.5, y = 0.75, label = "Texas") +
-  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = "Statistical Zone",
-       y = "Percent Occurrence")
-
-szones_plot_2
-#ggsave(plot = szones_plot_2, here("2019_edits/figures", "statzones_occurrence.png"), dpi = 600)
-```
-
-***
-
-###  Stat Zone Side-by
-
-```{r}
-szones_plot_1 + szones_plot_2
-```
-
-***
-
-## Region Summary {.tabset .tabset-fade .tabset-pills}
-
-```{r}
-seamap <- seamap %>% 
-  mutate(
-    # region = ifelse(Start_Lat < 28.387595 & Start_Long < -96, "South Texas", "TX/LA"),
-    #      region = ifelse(Start_Long > -89.2, "MS Bight", region),
-    #      region = ifelse(Start_Long > -87.5, "FL", region),
-    #      region = factor(region)
-    region = ifelse(StatZone %in% seq("21", "18"), "Texas", "Louisiana"),
-    region = ifelse(StatZone %in% seq("12", "10"), "MS Bight", region),
-    region = ifelse(StatZone %in% seq("1", "9"), "Florida", region),
+# Manuscript Model
+
+```{r load export}
+seamap <- read_csv(str_c("~/Dropbox/SEAMAP_2019/data/offshore/", 
+                        "seamap_manuscriptmods_full.csv"), 
+                   col_types = cols()) %>% 
+  mutate(year_f = factor(year_f),
+         Season = factor(season, levels = c("Summer", "Fall")),
          region = factor(region, levels = c("Texas", "Louisiana", "MS Bight", "Florida"))
@@
 
-#Output seamap analysis file
-write_csv(seamap, 
-          "~/Dropbox/SEAMAP_2019/data/offshore/seamap_cpue_2019_analysis.csv", 
-          col_names = TRUE)
-
-region_summary <- seamap %>% 
-  filter(is.na(region)      == FALSE) %>% 
-  group_by(region) %>% 
-  summarise(Stations          = n(),
-            `Missing Obs`     = sum(is.na(CPUE_towspd)),
-            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
-            `SD`              = sd(CPUE_towspd, na.rm = T),
-            `Var`             = var(CPUE_towspd),
-            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-            `% Occurrence`    = mean(Crab_presence, na.rm = T),
-            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
-    ungroup() %>% 
-    mutate(region             = factor(region, 
-                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
-           #region             = fct_rev(region),
-           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
-           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-    )
-
-region_summary %>% 
-  select(region, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
-  knitr::kable()
-
-```
-
-***
-
-### Regional Catch Plot
-
-```{r}
-
-region_plot_1 <- region_summary %>% 
-  ggplot() +
-    geom_col(aes(region, `Mean Catch`)) +
-    geom_errorbar(aes(x = region, 
-                      ymin = catch_ymin,
-                      ymax = catch_ymax),
-                  size = .25) +
-    labs(x= "Sampling Region",
-         y = "Mean Catch (C. sapidus / Hectare)")
-
-region_plot_1 
-#ggsave(plot = region_plot_1, here("2019_edits/figures", "regions_catch.png"), dpi = 600)
-```
-
-***
-
-### Regional Frequency of Occurrence
-
-```{r}
-
-region_plot_2 <- region_summary %>% 
-  ggplot() +
-    geom_col(aes(region, `% Occurrence`)) +
-    geom_errorbar(aes(x = region, 
-                      ymin = occurrence_ymin,
-                      ymax = occurrence_ymax),
-                  size = .25) +
-  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = "Sampling Region",
-       y = "Percent Occurrence")
-
-region_plot_2
-#ggsave(plot = region_plot_2, here("2019_edits/figures", "regions_occurrence.png"), dpi = 600)
-
-```
-
-***
-
-### Regional Side-by
-
-```{r}
-region_plot_1 + region_plot_2
-```
-
-***
-
-## Region - Season {.tabset .tabset-fade .tabset-pills}
-
-```{r}
-rs_summary <- seamap %>% 
-  filter(is.na(region)      == FALSE) %>% 
-  group_by(region, Season) %>% 
-  summarise(Stations          = n(),
-            `Missing Obs`     = sum(is.na(CPUE_towspd)),
-            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
-            `SD`              = sd(CPUE_towspd, na.rm = T),
-            `Var`             = var(CPUE_towspd),
-            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-            `% Occurrence`    = mean(Crab_presence, na.rm = T),
-            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
-    ungroup() %>% 
-    mutate(Season             = factor(Season, levels = c("Summer", "Fall")),
-           region             = factor(region, 
-                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
-           #region             = fct_rev(region),
-           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
-           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-    )
-
-rs_summary %>% 
-  select(region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
-  knitr::kable()
-```
-
-***
-
-### Region - Season Catch
-
-```{r}
-rs_plot_1 <- rs_summary %>% 
-  ggplot(aes(region, `Mean Catch`, fill = Season)) +
-    geom_col(position = "dodge") +
-    geom_errorbar(aes(ymin = catch_ymin,
-                      ymax = catch_ymax),
-                  position = "dodge", 
-                  size = .25) +
-  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
-  labs(x = "Region",
-       y = "Mean Catch (C. sapidus / Hectare)") + theme(
-    legend.position = c(1, .95),
-    legend.justification = c("right", "top"),
-    legend.box.just = "right",
-    legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA),
-    axis.text.x = element_text(angle = 45, vjust = 0.5)
-    )
-
-rs_plot_1 
-```
-
-***
-
-### Region - Season FOO
-
-```{r}
-
-rs_plot_2 <- rs_summary %>% 
-  ggplot(aes(region, `% Occurrence`, fill = Season)) +
-    geom_col(position = "dodge") +
-    geom_errorbar(aes(ymin = occurrence_ymin,
-                      ymax = occurrence_ymax),
-                  position = "dodge",
-                  size = .25) +
-  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
-  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = "Region",
-       y = "Percent Occurrence") + theme(
-    legend.position = c(1, .95),
-    legend.justification = c("right", "top"),
-    legend.box.just = "right",
-    legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA),
-    axis.text.x = element_text(angle = 45, vjust = 0.5)
-    )
-
-rs_plot_2
-
-```
-
-***
-
-### Region - Season Side-by
-
-```{r}
-
-rs_plot_1 + theme(legend.position = "none") + rs_plot_2
-
-```
-
-***
-
-## Seasonal Summary {.tabset .tabset-fade .tabset-pills}
-
-```{r}
-
-season_summary <- seamap %>% 
-  group_by(Survey_Year, Season) %>% 
-  summarise(Stations          = n(),
-            `Missing Obs`     = sum(is.na(CPUE_towspd)),
-            `Mean Catch`      = mean(CPUE_towspd, na.rm = T),
-            `SD`              = sd(CPUE_towspd, na.rm = T),
-            `Var`             = var(CPUE_towspd),
-            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-            `Catch SE`        = sd(CPUE_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-            `% Occurrence`    = mean(Crab_presence, na.rm = T),
-            `% Occurrence SE` = sd(Crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
-    ungroup() %>% 
-    mutate(Survey_Year        = factor(Survey_Year),
-           # StatZone         = factor(StatZone),
-           # StatZone         = fct_rev(StatZone),
-           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
-           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-         )
-
-season_summary %>% select(Survey_Year, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
-#knitr::kable(season_summary)
-```
-
-***
-
-### Seasonal Catch Plot
-
-```{r}
-
-season_plot_1 <- season_summary %>% 
-  ggplot(aes(Survey_Year, `Mean Catch`, fill = Season)) +
-    geom_col(position = "dodge") +
-    geom_errorbar(aes(ymin = catch_ymin,
-                      ymax = catch_ymax),
-                  position = "dodge",
-                  size = .25) +
-  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
-  labs(x = "Survey Year",
-       y = "Mean Catch (C. sapidus / Hectare)") + theme(
-    legend.position = c(1, .95),
-    legend.justification = c("right", "top"),
-    legend.box.just = "right",
-    legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA),
-    axis.text.x = element_text(angle = 45, vjust = 0.5)
-    )
-
-season_plot_1 
-#ggsave(plot =  year_plot_1, here("2019_edits/figures", "yearly_catch.png"), dpi = 600)
-
-```
-
-***
-
-### Seasonal Frequency of Occurrence
-
-```{r}
-
-season_plot_2 <- season_summary %>% 
-  ggplot(aes(Survey_Year, `% Occurrence`, fill = Season)) +
-    geom_col(position = "dodge") +
-    geom_errorbar(aes(ymin = occurrence_ymin,
-                      ymax = occurrence_ymax),
-                  position = "dodge",
-                  size = .25) +
-  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
-  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = "Survey Year",
-       y = "Percent Occurrence") + theme(
-    legend.position = c(1, .95),
-    legend.justification = c("right", "top"),
-    legend.box.just = "right",
-    legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA),
-    axis.text.x = element_text(angle = 45, vjust = 0.5)
-    )
-
-season_plot_2
-
-```
-
-***
-
-### Seasonal Side-by
-
-```{r}
-season_plot_1 + theme(legend.position = "none") + season_plot_2
-```
-
-***
-
-# East-West Models {.tabset .tabset-pills}
-
-## Model A. 2000-2018 {.tabset}
-
-This model uses crabs per hectare as the response over the period of 18 years (2000-2018). Data is limited to statzones that were consistently sampled over the time period (i.e. West of Mobile Bay).
-
-Model is a generalized linear model with a negative binomial error distribution.
-Blue crab catch is predicted as the sum of linear predictors for the year and season when the station was sampled in addition to the region in which it took place, with an interaction between survey year and region.
-An offset of area towed in hectares was used to predict catch as a rate and account for differences in sampling effort at different stations.
-
-```{r}
-seamap <- seamap %>% rename_all(tolower) %>% filter(statzone != 12)
-seamap_west <- seamap %>% 
-  filter(statzone %in% 11:21) %>% 
-  mutate(statzone = factor(statzone))
-
-mod1a <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
-            year_f * region + 
-            offset(log(area_hectares)),
-            data = seamap_west)
-
-#summary(mod1a)
-```
-
-### Interaction Plot
-
-Looking at an interaction plot indicates that the impact of each region is not consistent across years and that there is an important interaction in the data.
-
-```{r}
-emmeans::emmip(mod1a, region ~ year_f) +
-  labs(title = "Interaction Plot: year * region",
-       caption = "criss-crossing of estimates is subjective indication of interaction",
-       x = NULL) +
-  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
-```
-
-### Model Summary
-
-Understanding p-values in glm model summary. Using the default settings in R sets the contrast levels for factors such that all factors are contrasted against the first/lowest factor level.
-
-For example in our model year is modeled as a factor, which adjusts the intercept for the model for each.
-The first year is 2000, so all other years are contrasted against that year's mean estimate.
-One quick way to confirm what factor level is the contrast is y checking which levels are absent from the summary table `summary(my_model)`
-
-Contrasts:   
-year = 2000   
-region = texas   
-season = summer
-
-P-values on factor levels in these tables indicate significant deviation from the contrasts. Post-hoc tests are necessary to compare individual levels against one another.
-
-```{r}
-tidy(mod1a) %>% 
-  mutate(`signif.` = ifelse(p.value <= .05, "*", "")) %>% 
-  kable()
-```
-
-### Deviance
-
-```{r}
-broom::glance(mod1a) %>% kable()
-
-#Percent deviance explained
-perc_dev <- (mod1a$null.deviance - mod1a$deviance) / mod1a$null.deviance
-```
-
-Goodness of fit for generalized linear models is described using deviance. A glm will report 2 deviance measures:
-
-`null.deviance` is the residual variation remaining from the null model. The null model here is the grand mean of blue crab catch per hectare of all observations
-
-`deviance` is the residual variation remaining from the fitted model. Numbers closer to the null.deviance indicate that the model did not perform much better than the null model.
-
-`% deviance explained` is calculated as $\frac{null.deviance - deviance}{null.deviance} * 100$ and expresses the improvement of the fitted model over the null in % deviance explained.
-
-**Percent Deviance for model A.** = `r perc_dev`
-
-### Likelihood Ratio Test
-
-Significance of the entire factor can be obtained by using a Chi-squared likelihood ratio test.
-
-```{r}
-
-#Drop1 method
-#drop1(mod1a, test = "F")     # F-test
-#drop1(mod1a, test = "Chisq") # Chisq LRT - no scope
-
-#Name what you want to drop
-lrt_y  <- drop1(mod1a, scope = ~ year_f, test = "Chisq")
-lrt_r  <- drop1(mod1a, scope = ~ region, test = "Chisq")
-lrt_s  <- drop1(mod1a, scope = ~ season, test = "Chisq")
-lrt_yr <- drop1(mod1a, scope = ~ year_f*region, test = "Chisq")
-
-bind_rows(
-  list(
-    lrt_y  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor"),
-    lrt_r  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
-    lrt_s  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
-    lrt_yr  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region")
-)) %>% kable()
-
-# #Anova method - LRT
-# 
-# # No interaction - testing
-# mod1_test <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season + 
-#             offset(log(area_hectares)),
-#             data = seamap_west)
-# 
-# anova(mod1a, mod1_test, test = "Chisq")
-```
-
-### CPUE Timeline
-
-Because we used area towed in the model as an offset predictions from our model can be interprated as crabs per hectare.
-
-```{r}
-
-#Estimated Marginal Means with an offset
-#parameter in the call of offset = 0:
-mod1a.dat <- as.data.frame(emmeans(mod1a, 
-                                  specs = "year_f", 
-                                  by    = "region",
-                                  type  = "response", 
-                                  offset = 0))
-mod1a.dat$CV <- mod1a.dat$SE/mod1a.dat$response
-
-#make scale_x_discrete breaks b/c ggplot is dumb
-ystart <- min(as.numeric(seamap_west$survey_year))
-yend   <- max(as.numeric(seamap_west$survey_year))
-ynames <- lubridate::year(seq.Date(as.Date(paste(ystart), "%Y"), 
-                   as.Date(paste(yend), "%Y"), 
-                   by = "year"))
-
-#ggplot of standardized index of abundance
-p <- mod1a.dat %>% 
-  mutate(year_n = as.numeric(as.character(year_f))) %>% 
-  ggplot(aes(year_n, response)) +
-      geom_ribbon(aes(year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
-      geom_line(aes(year_n, response, group = 1)) +
-      geom_point(aes(year_n, response)) +
-      geom_hline(aes(yintercept = mean(seamap_west$cpue_towspd)), color = "darkred", linetype = 2) +
-      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
-      labs(
-        x = NULL, 
-        y = "Crabs per Hectare") +
-      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
-      facet_wrap(~region)
-p
-
-```
-
-### Observed vs. Predicted
-
-Model prediction (black) & observed mean values (blue)
-
-```{r}
-
-#Estimated Marginal Means with an offset
-#parameter in the call of offset = 0:
-mod1a.dat <- as.data.frame(emmeans(mod1a, 
-                                  specs = "year_f", 
-                                  by    = c("region", "season"),
-                                  type  = "response", 
-                                  offset = 0))
-mod1a.dat$CV <- mod1a.dat$SE/mod1a.dat$response
-
-#Observed data
-mean_obs <- mean(seamap_west$cpue_towspd)
-obs_timeline <- seamap_west %>% 
-  group_by(survey_year, region, season) %>% 
-  summarise(Nobs = n(),
-            PercentPos = mean(crab_presence),
-            Mean_CPUE = mean(cpue_towspd)) %>% 
-  mutate(Index_Obs = Mean_CPUE/mean_obs)
-
-#ggplot of standardized index of abundance
-p <- mod1a.dat %>% 
-  mutate(year_n = as.numeric(as.character(year_f))) %>% 
-  ggplot(aes(year_n, response)) +
-      #Fitted Data
-      geom_ribbon(aes(year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
-      geom_line(aes(year_n, response, group = 1)) +
-      geom_point(aes(year_n, response)) +
-      # Observed Data
-      geom_line(data = obs_timeline, 
-              aes(survey_year, Mean_CPUE, group = region), 
-              col = "royalblue", linetype = 2) +
-      geom_point(data = obs_timeline, 
-                 aes(survey_year, Mean_CPUE, group = region), col = "royalblue") +
-      #Theme changes
-      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
-      labs(
-        x = NULL, 
-        y = "Crabs per Hectare",
-        title = "Model Estimates and Yearly observed means") +
-      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
-      facet_grid(season~region)
-p
-
-```
-
-## Model B. 2009-2018 {.tabset}
-
-This model uses crabs per hectare as the response over the period of 9 years (2009-2018).
-Data selection and sampling effort was consistent over this period.
-Additionally the survey expanded to the Eastern Gulf of Mexico so stat zones in that region are included as well.
-
-Model is a generalized linear model with a negative binomial error distribution.
-Blue crab catch is predicted as the sum of linear predictors for the year and season when the station was sampled in addition to the region in which it took place, with an interaction between survey year and region.
-An offset of area towed in hectares was used to predict catch as a rate and account for differences in sampling effort at different stations.
-
-```{r}
-seamap_east <- seamap %>% 
-  filter(statzone != 12,
-         statzone != 1,
-         survey_year %in% 2009:2018) %>% 
-  mutate(statzone = factor(statzone))
-
-modb <- MASS:::glm.nb(sapidus_catch ~ year_f + region + season +   #Additive covariates
-            year_f * region + 
-            offset(log(area_hectares)),
-            data = seamap_east)
-
-#summary(modb)
-```
-
-### Interaction Plot
-
-Looking at an interaction plot indicates that the impact of each region is not consistent across years and that there is an important interaction in the data.
-The sharp peaks for Florida's linear predictor reflect years when there was no catch.
-
-```{r}
-emmeans::emmip(modb, region ~ year_f) +
-  labs(title = "Interaction Plot: year * region",
-       caption = "criss-crossing of estimates is subjective indication of interaction",
-       x = NULL) +
-  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
-```
-
-### Model Summary
-
-```{r}
-tidy(modb) %>% 
-  mutate(`signif.` = ifelse(p.value <= .05, "*", "")) %>% 
-  kable()
-```
-
-### Deviance
-
-```{r}
-broom::glance(modb) %>% kable()
-
-#Percent deviance explained
-perc_dev <- (modb$null.deviance - modb$deviance) / modb$null.deviance
-```
-
-Goodness of fit for generalized linear models is described using deviance. A glm will report 2 deviance measures:
-
-`null.deviance` is the residual variation remaining from the null model. The null model here is the grand mean of blue crab catch per hectare of all observations
-
-`deviance` is the residual variation remaining from the fitted model. Numbers closer to the null.deviance indicate that the model did not perform much better than the null model.
-
-`% deviance explained` is calculated as $\frac{null.deviance - deviance}{null.deviance} * 100$ and expresses the improvement of the fitted model over the null in % deviance explained.
-
-**Percent Deviance for model B.** = `r perc_dev`
-
-### Likelihood Ratio Test
-
-```{r}
-
-#Drop1 method
-#drop1(mod1a, test = "F")
-#drop1(modb, test = "Chisq") # no scope
-
-#Name what you want to drop
-lrt_y  <- drop1(modb, scope = ~ year_f, test = "Chisq")
-lrt_r  <- drop1(modb, scope = ~ region, test = "Chisq")
-lrt_s  <- drop1(modb, scope = ~ season, test = "Chisq")
-lrt_yr <- drop1(modb, scope = ~ year_f*region, test = "Chisq")
-
-bind_rows(
-  list(
-    lrt_y  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor"),
-    lrt_r  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
-    lrt_s  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
-    lrt_yr  %>% as.data.frame() %>% 
-      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region")
-)) %>% kable()
-
-```
-
-### CPUE Timeline
-
-Because we used area towed in the model as an offset predictions from our model can be interprated as crabs per hectare.
-
-```{r}
-
-#Estimated Marginal Means with an offset
-#parameter in the call of offset = 0:
-modb.dat <- as.data.frame(emmeans(modb, 
-                                  specs = "year_f", 
-                                  by    = "region",
-                                  type  = "response", 
-                                  offset = 0))
-modb.dat$CV <- modb.dat$SE/modb.dat$response
-
-#make scale_x_discrete breaks b/c ggplot is dumb
-ystart <- min(as.numeric(seamap_east$survey_year))
-yend   <- max(as.numeric(seamap_east$survey_year))
-ynames <- lubridate::year(seq.Date(as.Date(paste(ystart), "%Y"), 
-                   as.Date(paste(yend), "%Y"), 
-                   by = "year"))
-
-#ggplot of standardized index of abundance
-p <- modb.dat %>% 
-  mutate(year_n = as.numeric(as.character(year_f))) %>% 
-  ggplot(aes(year_n, response)) +
-      geom_ribbon(aes(year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
-      geom_line(aes(year_n, response, group = 1)) +
-      geom_point(aes(year_n, response)) +
-      geom_hline(aes(yintercept = mean(seamap_east$cpue_towspd)), color = "darkred", linetype = 2) +
-      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
-      labs(
-        x = NULL, 
-        y = "Crabs per Hectare") +
-      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
-      facet_wrap(~region)
-p
-
-```
-
-### Observed vs. Predicted
-
-Model prediction (black) & observed mean values (blue)
-
-```{r}
-
-#Estimated Marginal Means with an offset
-#parameter in the call of offset = 0:
-modb.dat <- as.data.frame(emmeans(modb, 
-                                  specs = "year_f", 
-                                  by    = c("region", "season"),
-                                  type  = "response", 
-                                  offset = 0))
-modb.dat$CV <- modb.dat$SE/modb.dat$response
-
-#Drop Infinite credibility intervals
-modb.dat <- modb.dat %>% 
-  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL))
-
-#Observed data
-mean_obs <- mean(seamap_east$cpue_towspd)
-obs_timeline <- seamap_east %>% 
-  group_by(survey_year, region, season) %>% 
-  summarise(Nobs = n(),
-            PercentPos = mean(crab_presence),
-            Mean_CPUE = mean(cpue_towspd)) %>% 
-  mutate(Index_Obs = Mean_CPUE/mean_obs)
-
-#ggplot of standardized index of abundance
-p <- modb.dat %>% 
-  mutate(year_n = as.numeric(as.character(year_f))) %>% 
-  ggplot(aes(year_n, response)) +
-      #Fitted Data
-      geom_ribbon(aes(year_n, ymin = asymp.LCL, ymax = asymp.UCL), fill = "gray80") +
-      geom_line(aes(year_n, response, group = 1)) +
-      geom_point(aes(year_n, response)) +
-      # Observed Data
-      geom_line(data = obs_timeline, 
-              aes(survey_year, Mean_CPUE, group = region), 
-              col = "royalblue", linetype = 2) +
-      geom_point(data = obs_timeline, 
-                 aes(survey_year, Mean_CPUE, group = region), col = "royalblue") +
-      #Theme changes
-      scale_x_discrete(limits = c(as.numeric(ystart:yend)), labels = ynames) +
-      labs(
-        x = NULL, 
-        y = "Crabs per Hectare",
-        title = "Model Estimates and Yearly observed means") +
-      theme(axis.text.x=element_text(angle=45, hjust = 1, vjust=1), legend.position = "bottom") +
-      facet_grid(season~region)
-p
-
-```
-
-# Manuscript Model {.tabset .tabset-pills }
-
-## Model Dataset
-
-**The following numbers are from all usable data from 2000-2018**
+seamap_west <- read_csv(str_c("~/Dropbox/SEAMAP_2019/data/offshore/", 
+                        "seamapwest_manuscriptmods_full.csv"), 
+                        col_types = cols()) %>% 
+  mutate(year_f = factor(year_f),
+         Season = factor(season, levels = c("Summer", "Fall")),
+         region = factor(region, levels = c("Texas", "Louisiana", "MS Bight", "Florida"))
+)
+```
+
+## Model Dataset {.tabset}
+
+### Model Data - West Only
+
+```{r seamap west stats}
+start_year <- min(as.numeric(as.character(seamap_west$survey_year)))
+end_year <- max(as.numeric(as.character(seamap_west$survey_year)))
+total_catch <- sum(seamap_west$sapidus_catch, na.rm = T)
+overall_foa <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3) * 100
+overall_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
+percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
+station_count <- seamap_west %>% count()
+
+```
+
+ * Total Number of Stations = `r nrow(seamap_west)`
+
+ * Starting in `r start_year` and continuing through `r end_year`
+
+ * Total Sapidus Caught was `r total_catch`
+
+ * Overall Frequency of Occurrence was `r overall_foa`
+
+ * Overall Mean Catch Crabs/Hectare: `r overall_mean`
+
+ * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
+
+### East + West
 
@@
 total_catch <- sum(seamap$sapidus_catch, na.rm = T)
-overall_foa <- mean(seamap$crab_presence, na.rm = TRUE) * 100
-overall_mean <- mean(seamap$cpue_towspd, na.rm = T)
+overall_foa <- round(mean(seamap$crab_presence, na.rm = TRUE), 3) * 100
+overall_mean <- round(mean(seamap$cpue_towspd, na.rm = T), 3)
 percent_zeros <- seamap %>% filter(sapidus_catch == 0) %>% count()
@@
 
-#seamap %>% group_by(survey_year) %>% summarise(foa = mean(crab_presence)) %>% arrange(foa)
-
 ```
@@
 
-**The following numbers are from the Western Gulf Dataset used in the generalized linear model**
-
-```{r seamap west stats}
-start_year <- min(as.numeric(as.character(seamap_west$survey_year)))
-end_year <- max(as.numeric(as.character(seamap_west$survey_year)))
-total_catch <- sum(seamap_west$sapidus_catch, na.rm = T)
-overall_foa <- mean(seamap_west$crab_presence, na.rm = TRUE) * 100
-overall_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
-percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
-station_count <- seamap_west %>% count()
-
-```
-
- * Total Number of Stations = `r nrow(seamap_west)`
-
- * Starting in `r start_year` and continuing through `r end_year`
-
- * Total Sapidus Caught was `r total_catch`
-
- * Overall Frequency of Occurrence was `r overall_foa`
-
- * Overall Mean Catch Crabs/Hectare: `r overall_mean`
-
- * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
-
-## Yearly Catch Plot
+## Yearly Catch Plot {.tabset}
+
+### Data Summary
 
@@
 year_sums %>% select(`Survey Year` = survey_year, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
+```
+
+### Annual Mean Catch
+
+```{r}
 
@@
 year_plot
-
+```
+
+### Annual Frequency of Occurrence
+
+```{r}
 year_foa <- year_sums %>% 
@@
 year_foa
+```
+
+### Side x Side
+
+```{r}
 
@@
 
-## Region - Season Plot
+## Region - Season Plot {.tabset}
 
@@
 
-```{r old}
+### Factor Summary
+
+```{r }
 # rs_summary <- seamap %>% 
@@
 
+```
+
+### Mean Catch by Region and Season
+
+```{r}
+
 # Plot
@@
 rs_plot
-
+```
+
+### Frequency of Occurrence
+
+```{r}
 rs_plot_2 <- rs_summary %>% 
@@
 rs_plot_2
-
+```
+
+### Side x Side
+
+```{r}
 rs_plot + rs_plot_2
@@
 
-## Seasonal Catch Plot
+## Seasonal Catch Plot {.tabset}
 
 *NOTE 2: Mean Catch (per hectare) and frequency of occurrence calculated for each year, for each season. The mean and standard error of those annual measurements are then taken*
+
+### Season Factor Summary
 
@@
 
+```
+
+### Seasonal Catch Plot
+
+```{r}
+
 season_plot <- season_summary %>% 
@@
 season_plot
+
+```
+
+### Seasonal Frequency of Occurrence
+
+```{r}
 
@@
 season_plot_2
-
+```
+
+### Side x Side
+
+```{r}
 season_plot + season_plot_2
@@
 #Name what you want to drop
-lrt_y  <- drop1(mod1a, scope = ~ year_f, test = "Chisq")
-lrt_r  <- drop1(mod1a, scope = ~ region, test = "Chisq")
-lrt_s  <- drop1(mod1a, scope = ~ season, test = "Chisq")
-lrt_yr <- drop1(mod1a, scope = ~ year_f*region, test = "Chisq")
+lrt_y  <- drop1(best_mod, scope = ~ year_f, test = "Chisq")
+lrt_r  <- drop1(best_mod, scope = ~ region, test = "Chisq")
+lrt_s  <- drop1(best_mod, scope = ~ season, test = "Chisq")
+lrt_yr <- drop1(best_mod, scope = ~ year_f*region, test = "Chisq")
 
@@
 
-## Spatial Grids  {.tabset}
-
-```{r}
+## Raster Plots  {.tabset}
+
+```{r spatial data setup}
 
@@
   st_as_sf()
+
+## Statistical Zones
+
+#Load the simplified nmfs grid
+szones <- read_sf("~/Dropbox/SEAMAP_2019/data/gis_files/nmfs_grids_clipped_rough.shp", 
+                  crs = 4326) #%>% st_simplify()
 
@@
 
+### Statistical Zones
+```{r}
+
+#Numbering for statzones
+sz_df <- tribble(
+
+~"SZ", ~"long",  ~"lat",
+21,    -96.5,     26.5,
+20,    -96.7,  27.5,
+19,    -95.75,  28.25,
+18,    -94.5,   28.8,
+17,    -93.5,   28.9,
+16,    -92.5,   28.85,
+15,    -91.5,   28.8,
+14,    -90.5,   28.75,
+13,    -89.75,  28.9,
+12,    -89.25,  29.65,
+11,    -88.5,   29.75,
+10,    -87.5,   29.80,
+ 9,    -86.5,   29.80,
+ 8,    -85.5,   29.35,
+ 7,    -84.20,   29.45,
+ 6,    -83.8,   28.50,
+ 5,    -83.5,   27.55,
+ 4,    -83.35,   26.75,
+ 3,    -83.35,   25.75,
+ 2,    -84.20,   24.55,
+ 2,    -81.55,   24.28,
+ 1,    -82.5,   24.28
+
+) %>% mutate(SZ = as.character(SZ))
+
+ggplot() +
+  geom_sf(data = szones, fill = NA) +
+  geom_sf(data = usmap) +
+  geom_sf(data = mex) +
+  geom_text(data = sz_df, aes(long, lat, label = SZ), size = 3.5) +
+  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
+  labs(x = NULL, y = NULL)  +
+  scale_y_continuous(breaks = c(25,30))
+```
+
 ### Sampling Effort
@@
   coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
+  scale_y_continuous(breaks = c(25,30)) +
   labs(x = NULL, y = NULL) +

### 2020-02-10 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
made more changes, added link to index file

@@
     toc_float: true
+  code_folding: hide
 editor_options: 
@@
 
-```{r load export}
+```{r load data}
 seamap <- read_csv(str_c("~/Dropbox/SEAMAP_2019/data/offshore/", 
@@
          Season = factor(season, levels = c("Summer", "Fall")),
-         region = factor(region, levels = c("Texas", "Louisiana", "MS Bight", "Florida"))
+         region = ifelse(region == "Louisiana", "LA West", region),
+         region = factor(region, levels = c("Texas", "LA West", "MS Bight", "Florida"))
 )
@@
 
-## Yearly Catch Plot {.tabset}
+## Annual Catch and Occurrence {.tabset}
 
@@
 
-*NOTE: Contains Data Across All Years and Regions (Including Florida)*
+*NOTE: Contains Data Only from Western-Gulf Subset*
 
 ```{r}
-year_sums <- seamap %>% 
+year_sums <- seamap_west %>% 
   group_by(survey_year) %>% 
@@
 
-year_sums %>% select(`Survey Year` = survey_year, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
+year_sums %>% 
+  select(`Survey Year` = survey_year, Stations, `Missing Obs`, 
+         `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
 ```
@@
 
-```{r}
+```{r, fig.height=4}
 
@@
   labs(x = NULL,
-       y = "Mean Catch (C. sapidus / Hectare)")
+       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))
+  )
 
@@
 
-```{r}
+```{r, fig.height=4}
 year_foa <- year_sums %>% 
@@
     geom_col(aes(survey_year, `% Occurrence`)) +
-    # geom_errorbar(aes(x = survey_year, 
-    #                   ymin = occurrence_ymin,
-    #                   ymax = occurrence_ymax),
-    #               size = .25) +
     scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = NULL, y = "Percent Occurrence")
+    labs(x = NULL, y = "Percent occurrence")
 
@@
 
-```{r}
+```{r, fig.height=4}
 
 year_plot + year_foa
+
 ```
 
-## Region - Season Plot {.tabset}
+## Region - Season Interactions {.tabset}
 
-*NOTE: Contains Data Across All Years and Regions (Including Florida)*
+*NOTE: Contains Data Only from Western-Gulf Subset*
 
-*NOTE 2: Mean Catch (per hectare) and frequency of occurrence calculated for each year, in each region, for each season. The mean and standard error of those annual measurements are then taken*
+*NOTE 2: Mean Catch (per hectare) calculated as the average crabs/hectare from each tow within a region-season grouping.
+Percent occurrence is calculated separately as the average annual percent occurrence for those same groups.*
 
@@
 ```{r }
-# rs_summary <- seamap %>% 
-#   filter(is.na(region)      == FALSE) %>% 
-#   group_by(region, season) %>% 
-#   summarise(Stations          = n(),
-#             `Missing Obs`     = sum(is.na(cpue_towspd)),
-#             `Mean Catch`      = mean(cpue_towspd, na.rm = T),
-#             `SD`              = sd(cpue_towspd, na.rm = T),
-#             `Var`             = var(cpue_towspd),
-#             `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-#             `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-#             `% Occurrence`    = mean(crab_presence, na.rm = T),
-#             `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
-#     ungroup() %>% 
-#     mutate(Season             = factor(season, levels = c("Summer", "Fall")),
-#            region             = factor(region, 
-#                                        levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
-#            #region             = fct_rev(region),
-#            catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-#            catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
-#            catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-#            occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-#            occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-#            occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-#     )
 
-# #Summary Table
-# rs_summary %>%
-#   select(Region = region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>%
-#   knitr::kable()
+#Mean CPUE for the regions within each season
+rs_summary <- seamap_west %>%
+  filter(is.na(region)      == FALSE) %>%
+  group_by(region, season) %>%
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(cpue_towspd)),
+            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
+            `SD`              = sd(cpue_towspd, na.rm = T),
+            `Var`             = var(cpue_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>%
+    ungroup() %>%
+    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
+           region             = factor(region,
+                                       levels = c("Texas", "LA West", "MS Bight", "Florida")),
+           #region             = fct_rev(region),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin)
+    )
 
-#Calaculate Annual average cpue and percent occurrence
-rs_summary <- seamap %>% 
+#Summary Table
+rs_summary %>%
+  select(Region = region, Season, Stations, `Missing Obs`, `Mean Catch`, SD, Overdispersed) %>%
+  knitr::kable()
+```
+
+Average frequency of occurrence for each region and season is calculated in two steps.
+In the first step the frequency of occurrence for each region and for both survey seasons is calculated for every year.
+In the second step those annual means are averaged to get an overall measure for each region for each season, and a measure of error around them is calculated to represent the inter-annual variation in the frequency of occurrence.
+
+```{r}
+
+#Calaculate Annual average percent occurrence
+rs_foa <- seamap_west %>% 
   group_by(survey_year, region, season) %>% 
-  summarise(cpue = mean(cpue_towspd, na.rm = T),
-            percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
+  summarise(percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
   group_by(region, season) %>% 
   summarise(nyears = n(),
-            avg_annual_cpue = mean(cpue, na.rm = T),
-            annual_cpue_se = sd(cpue, na.rm = T) / sqrt(nyears),
             avg_percent_occurrence = mean(percent_occurrence, na.rm = T),
@@
     mutate(Season             = factor(season, levels = c("Summer", "Fall")),
-           region             = factor(region, levels = c("Texas", "Louisiana", 
+           region             = factor(region, levels = c("Texas", "LA West", 
                                                           "MS Bight", "Florida")),
-           catch_ymin         = avg_annual_cpue - (2 * annual_cpue_se),
-           catch_ymax         = avg_annual_cpue + (2 * annual_cpue_se),
-           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
            occurrence_ymin    = avg_percent_occurrence - (2 * po_se),
@@
 
+rs_foa %>% 
+  select(Region = region, Season, `N Years` = nyears, 
+         `% Occurrence` = avg_percent_occurrence, `% Occurrence SE` = po_se) %>%
+  knitr::kable()
+
 ```
@@
 rs_plot <- rs_summary %>% 
-  ggplot(aes(region, avg_annual_cpue, fill = season)) +
+  ggplot(aes(region, `Mean Catch`, fill = Season)) +
     geom_col(position = "dodge") +
@@
   labs(x = NULL,
-       y = "Mean Catch (C. sapidus / Hectare)") + 
+       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
   theme(
@@
 
-```{r}
-rs_plot_2 <- rs_summary %>% 
+```{r, fig.height=4}
+rs_plot_2 <- rs_foa %>% 
   ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
@@
   labs(x = NULL,
-       y = "Percent Occurrence") + theme(
+       y = "Percent occurrence") + theme(
     legend.position = c(1, .95),
@@
 
-```{r}
+```{r fig.height=4}
 rs_plot + rs_plot_2
 
-```
-
-## Seasonal Catch Plot {.tabset}
-
-*NOTE 2: Mean Catch (per hectare) and frequency of occurrence calculated for each year, for each season. The mean and standard error of those annual measurements are then taken*
-
-### Season Factor Summary
-
-```{r}
-# season_summary <- seamap %>% 
-#   group_by(survey_year, season) %>% 
-#   summarise(Stations          = n(),
-#             `Missing Obs`     = sum(is.na(cpue_towspd)),
-#             `Mean Catch`      = mean(cpue_towspd, na.rm = T),
-#             `SD`              = sd(cpue_towspd, na.rm = T),
-#             `Var`             = var(cpue_towspd),
-#             `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
-#             `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
-#             `% Occurrence`    = mean(crab_presence, na.rm = T),
-#             `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
-#     ungroup() %>% 
-#     mutate(survey_year        = factor(survey_year),
-#            # StatZone         = factor(StatZone),
-#            # StatZone         = fct_rev(StatZone),
-#            catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
-#            catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
-#            catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-#            occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
-#            occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
-#            occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
-#          )
-# 
-# season_summary %>% select(`Survey Year` = survey_year, Season = season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()
-
-#Calaculate Annual average cpue and percent occurrence
-season_summary <- seamap %>% 
-  group_by(survey_year, season) %>% 
-  summarise(cpue = mean(cpue_towspd, na.rm = T),
-            percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
-  group_by(season) %>% 
-  summarise(nyears = n(),
-            avg_annual_cpue = mean(cpue, na.rm = T),
-            annual_cpue_se = sd(cpue, na.rm = T) / sqrt(nyears),
-            avg_percent_occurrence = mean(percent_occurrence, na.rm = T),
-            po_se = sd(percent_occurrence, na.rm = T) / sqrt(nyears)) %>% 
-    ungroup() %>%
-    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
-           catch_ymin         = avg_annual_cpue - (2 * annual_cpue_se),
-           catch_ymax         = avg_annual_cpue + (2 * annual_cpue_se),
-           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
-           occurrence_ymin    = avg_percent_occurrence - (2 * po_se),
-           occurrence_ymax    = avg_percent_occurrence + (2 * po_se),
-           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin),
-           occurrence_ymax    = ifelse(occurrence_ymax > 1, 1, occurrence_ymax)
-    )
-
-```
-
-### Seasonal Catch Plot
-
-```{r}
-
-season_plot <- season_summary %>% 
-  ggplot(aes(season, avg_annual_cpue, fill = season)) +
-    geom_col() +
-    geom_errorbar(aes(ymin = catch_ymin,
-                      ymax = catch_ymax),
-                  size = .25) +
-  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
-  labs(x = NULL,
-       y = "Mean Catch (C. sapidus / Hectare)") + theme(
-    legend.position = c(1, .95),
-    legend.justification = c("right", "top"),
-    legend.box.just = "right",
-    legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA))
-
-season_plot
-
-```
-
-### Seasonal Frequency of Occurrence
-
-```{r}
-
-season_plot_2 <- season_summary %>% 
-  ggplot(aes(season, avg_percent_occurrence, fill = season)) +
-    geom_col(position = "dodge") +
-    geom_errorbar(aes(ymin = occurrence_ymin,
-                      ymax = occurrence_ymax),
-                  size = .25) +
-  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
-  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
-  labs(x = NULL,
-       y = "Percent Occurrence") + theme(
-    legend.position = c(1, .95),
-    legend.justification = c("right", "top"),
-    legend.box.just = "right",
-    legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA))
-
-season_plot_2
-```
-
-### Side x Side
-
-```{r}
-season_plot + season_plot_2
 ```

### 2020-02-15 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
figure changes

@@
 #Format ggplot for rest of document
-theme_set(theme_bw() + theme(panel.grid.major = element_blank(), 
+theme_set(theme_bw() + 
+          theme(panel.grid.major = element_blank(), 
             panel.grid.minor = element_blank(), 
@@
             axis.text = element_text(size = 12, color = "black"),
-                             axis.title = element_text(size = 14, color = "black")))
+            axis.title = element_text(size = 12, color = "black"),
+            legend.text = element_text(size = 12, color = "black"),
+            legend.background = element_rect(fill = NA))
+          )
 
@@
 
+west_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
+
 year_plot <- year_sums %>% 
@@
   ggplot() +
-    geom_col(aes(survey_year, `Mean Catch`)) +
+    geom_col(aes(survey_year, `Mean Catch`), fill = "gray35") +
     geom_errorbar(aes(x = survey_year, 
@@
                   size = .25) +
+  geom_hline(yintercept = west_mean, 
+             linetype = "dashed") +
   labs(x = NULL,
@@
 ```{r, fig.height=4}
+west_foa <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3)
+
 year_foa <- year_sums %>% 
@@
     geom_col(aes(survey_year, `% Occurrence`)) +
+    geom_hline(yintercept = west_foa, 
+               linetype = "dashed") +
     scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
@@
                   size = .25) +
-  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
   labs(x = NULL,
@@
     legend.box.just = "right",
-    legend.margin = margin(0, 6, 2, 2),
-    legend.background = element_rect(fill = NA))
+    legend.margin = margin(0, 6, 2, 2))
 
@@
                   size = .25) +
-  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
   scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
   labs(x = NULL,
-       y = "Percent occurrence") + theme(
+       y = "Percent occurrence") + 
+  theme(
     legend.position = c(1, .95),
@@
 ```{r fig.height=4}
+rs_plot <- rs_plot + theme(legend.position = "none")
 rs_plot + rs_plot_2
@@
 
-## Catch per Hectare Plot
+## Catch per Hectare Plot {.tabset .tabset-pills}
+
+### Seasonal Prediction Differences
 
@@
 best_mod_dat <- best_mod_dat %>% 
-  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL))
+  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL),
+         season = factor(season, levels = c("Summer", "Fall")),
+         region = factor(region, levels = c("Texas", "LA West", "MS Bight")))
 
@@
       geom_point(aes(year_n, response, color = season, shape = season)) +
-      scale_color_grey(start = 0.2, end = 0.6) + 
+      scale_color_grey(start = 0.35, end = 0.7) + 
       labs(
         x = NULL, 
-        y = "Crabs per Hectare",
-        title = "Model Estimates and Yearly observed means") +
+        y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) +
       facet_grid(region ~ .) +
@@
     legend.title = element_blank())
+p
+
+```
+
+### Observed vs. Predicted Data
+
+```{r}
+#Observed data
+mean_obs <- mean(seamap_west$cpue_towspd)
+obs_timeline <- seamap_west %>% 
+  group_by(survey_year, region, season) %>% 
+  summarise(Nobs = n(),
+            PercentPos = mean(crab_presence),
+            Mean_CPUE = mean(cpue_towspd)) %>% 
+  ungroup() %>% 
+  mutate(season = factor(season, levels = c("Summer", "Fall")),
+         region = factor(region, levels = c("Texas", "LA West", "MS Bight")),
+         Index_Obs = Mean_CPUE/mean_obs)
+
+#Overall group means
+panel_means <- seamap_west %>% 
+  group_by(region, season) %>% 
+  summarise(Mean_CPUE = mean(cpue_towspd))
+
+#ggplot of standardized index of abundance
+p <- best_mod_dat %>% 
+  mutate(year_n = as.numeric(as.character(year_f))) %>% 
+  ggplot(aes(year_n, response)) +
+    geom_hline(data = panel_means, 
+               aes(yintercept = Mean_CPUE), alpha = 0.5) +
+    # geom_ribbon(aes(year_n, 
+    #                 ymin = asymp.LCL, 
+    #                 ymax = asymp.UCL), 
+    #             fill = "gray80") +
+    geom_line(aes(x = year_n, 
+                  y = response, 
+                  group = 1, 
+                  col = "Predicted")) +
+    geom_point(aes(x = year_n, 
+                   y = response, 
+                   col = "Predicted")) +
+    # Observed Data
+    geom_line(data = obs_timeline, 
+            aes(x = survey_year, 
+                y = Mean_CPUE, 
+                group = region, 
+                col = "Observed"), linetype = 2) +
+    geom_point(data = obs_timeline, 
+               aes(x = survey_year, 
+                   y = Mean_CPUE, 
+                   group = region, 
+                   col = "Observed")) +
+    #Theme changes
+    #scale_color_grey(start = 0.35, end = 0.7) + 
+    scale_color_manual(values = c("gray35", "royalblue")) + 
+    labs(
+      x = NULL, 
+      y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) +
+  theme(legend.position = c(1, .98),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2),
+    legend.background = element_rect(fill = NA),
+    legend.title = element_blank()) +
+  facet_grid(season~region)
 p
@@
                                barwidth = 10)) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom", 
+        legend.text = element_text(size  = 12), 
+        legend.title = element_text(size = 12))
 ```
@@
                                barwidth = 10)) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom", 
+        legend.text = element_text(size  = 12), 
+        legend.title = element_text(size = 12))
 

### 2020-02-18 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
figure alterations

@@
 #packages
+library(ggspatial)
 library(MASS)
@@
 library(sf)
+
 conflicted::conflict_prefer("select", "dplyr")
@@
             legend.text = element_text(size = 12, color = "black"),
-            legend.background = element_rect(fill = NA))
+            legend.background = element_rect(fill = NA),
+            strip.text = element_text(size = 12, color = "black"))
           )
@@
   ggplot() +
-    geom_col(aes(survey_year, `Mean Catch`), fill = "gray35") +
+    geom_col(aes(survey_year, `Mean Catch`), fill = "gray50") +
     geom_errorbar(aes(x = survey_year, 
@@
   ggplot() +
-    geom_col(aes(survey_year, `% Occurrence`)) +
+    geom_col(aes(survey_year, `% Occurrence`), fill = "gray50") +
     geom_hline(yintercept = west_foa, 
@@
   knitr::kable()
+
+####  Full Gulf Summaries  ####
+#Mean CPUE for the regions within each season
+rs_summary_full <- seamap %>%
+  filter(is.na(region)      == FALSE) %>%
+  group_by(region, season) %>%
+  summarise(Stations          = n(),
+            `Missing Obs`     = sum(is.na(cpue_towspd)),
+            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
+            `SD`              = sd(cpue_towspd, na.rm = T),
+            `Var`             = var(cpue_towspd),
+            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
+            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>%
+    ungroup() %>%
+    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
+           region             = factor(region,
+                                       levels = c("Texas", "LA West", "MS Bight", "Florida")),
+           #region             = fct_rev(region),
+           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
+           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
+           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin)
+    )
+#Calaculate Annual average percent occurrence
+rs_foa_full <- seamap %>% 
+  group_by(survey_year, region, season) %>% 
+  summarise(percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
+  group_by(region, season) %>% 
+  summarise(nyears = n(),
+            avg_percent_occurrence = mean(percent_occurrence, na.rm = T),
+            po_se = sd(percent_occurrence, na.rm = T) / sqrt(nyears)) %>% 
+    ungroup() %>%
+    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
+           region             = factor(region, levels = c("Texas", "LA West", 
+                                                          "MS Bight", "Florida")),
+           occurrence_ymin    = avg_percent_occurrence - (2 * po_se),
+           occurrence_ymax    = avg_percent_occurrence + (2 * po_se),
+           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin),
+           occurrence_ymax    = ifelse(occurrence_ymax > 1, 1, occurrence_ymax)
+    )
+
 ```
@@
 
-```{r}
+```{r west summs}
 
@@
 
-```{r, fig.height=4}
+```{r west fig, fig.height=4}
 
@@
 
+```{r full fig, fig.height=4}
+
+# Plot
+rs_plot_3 <- rs_summary_full %>% 
+  ggplot(aes(region, `Mean Catch`, fill = Season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = catch_ymin,
+                      ymax = catch_ymax),
+                  position = "dodge", 
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
+  labs(x = NULL,
+       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
+  theme(
+    legend.position = c(1, .95),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2))
+
+rs_plot_3
+```
+
 ### Frequency of Occurrence
 
-```{r, fig.height=4}
+```{r west foa, fig.height=4}
 rs_plot_2 <- rs_foa %>% 
@@
 
+```{r full foa, fig.height=4}
+rs_plot_4 <- rs_foa_full %>% 
+  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
+    geom_col(position = "dodge") +
+    geom_errorbar(aes(ymin = occurrence_ymin,
+                      ymax = occurrence_ymax),
+                  position = "dodge",
+                  size = .25) +
+  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
+  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
+  labs(x = NULL,
+       y = "Percent occurrence") + 
+  theme(
+    legend.position = c(1, .95),
+    legend.justification = c("right", "top"),
+    legend.box.just = "right",
+    legend.margin = margin(0, 6, 2, 2))
+
+rs_plot_4
+```
+
 ### Side x Side
@@
 
+rs_plot_full <- rs_plot_3 + theme(legend.position = "none")
+rs_plot_full + rs_plot_4
 ```
@@
   group_by(region, season) %>% 
-  summarise(Mean_CPUE = mean(cpue_towspd))
+  summarise(Mean_CPUE = mean(cpue_towspd)) %>% 
+  ungroup() %>% 
+  mutate(season = factor(season, levels = c("Summer", "Fall")),
+         region = factor(region, levels = c("Texas", "LA West", "MS Bight")))
 
@@
   ggplot(aes(year_n, response)) +
-    geom_hline(data = panel_means, 
-               aes(yintercept = Mean_CPUE), alpha = 0.5) +
-    # geom_ribbon(aes(year_n, 
-    #                 ymin = asymp.LCL, 
-    #                 ymax = asymp.UCL), 
-    #             fill = "gray80") +
+    geom_ribbon(aes(year_n,
+                    ymin = asymp.LCL,
+                    ymax = asymp.UCL),
+                fill = "gray80") +
     geom_line(aes(x = year_n, 
@@
                    col = "Observed")) +
+    #Group Means
+    # geom_hline(data = panel_means, 
+    #            aes(yintercept = Mean_CPUE), alpha = 0.5, linetype = 1, color = "darkred") +
     #Theme changes
     #scale_color_grey(start = 0.35, end = 0.7) + 
-    scale_color_manual(values = c("gray35", "royalblue")) + 
+    scale_color_manual(values = c("royalblue", "black")) + 
     labs(
@@
   labs(x = NULL, y = NULL)  +
-  scale_y_continuous(breaks = c(25,30))
+  scale_y_continuous(breaks = c(25,30)) +
+  annotation_north_arrow(
+    height = unit(0.4, "in"),
+    location = "bl", 
+    which_north = "true", 
+    pad_x = unit(0, "in"), 
+    pad_y = unit(0, "in"),
+    style = north_arrow_fancy_orienteering) +
+  annotation_scale(
+    pad_x = unit(0.5, "in"))
 ```
@@
         legend.text = element_text(size  = 12), 
-        legend.title = element_text(size = 12))
+        legend.title = element_text(size = 12)) +
+  annotation_north_arrow(
+    height = unit(0.4, "in"),
+    location = "bl", 
+    which_north = "true", 
+    pad_x = unit(0, "in"), 
+    pad_y = unit(0, "in"),
+    style = north_arrow_fancy_orienteering) +
+  annotation_scale(
+    pad_x = unit(0.5, "in"))
 ```
@@
         legend.text = element_text(size  = 12), 
-        legend.title = element_text(size = 12))
+        legend.title = element_text(size = 12)) +
+  annotation_north_arrow(
+    height = unit(0.4, "in"),
+    location = "bl", 
+    which_north = "true", 
+    pad_x = unit(0, "in"), 
+    pad_y = unit(0, "in"),
+    style = north_arrow_fancy_orienteering) +
+  annotation_scale(
+    pad_x = unit(0.5, "in"))
 

### 2020-02-18 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
tilted axis labels

@@
 
-```{r, fig.height=4}
+```{r, fig.height = 4}
 
@@
 
-```{r, fig.height=4}
+```{r, fig.height = 4}
 west_foa <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3)
@@
 
-```{r west fig, fig.height=4}
+```{r west fig, fig.height = 4, eval = F}
 
@@
 
-```{r full fig, fig.height=4}
+```{r full fig, fig.height = 4}
 
@@
     legend.box.just = "right",
-    legend.margin = margin(0, 6, 2, 2))
+    legend.margin = margin(0, 6, 2, 2),
+    axis.text.x = element_text(angle = 45, hjust = 1, vjust = .8))
 
@@
 
-```{r west foa, fig.height=4}
+```{r west foa, fig.height = 4, eval = F}
 rs_plot_2 <- rs_foa %>% 
@@
 
-```{r full foa, fig.height=4}
+```{r full foa, fig.height = 4}
 rs_plot_4 <- rs_foa_full %>% 
@@
 
-```{r fig.height=4}
+```{r fig.height = 4, eval = FALSE}
 rs_plot <- rs_plot + theme(legend.position = "none")
 rs_plot + rs_plot_2
+```
+
+```{r fig.height = 4}
 

### 2020-03-06 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
changed statzon 10 to be included with Florida

@@
 
+**NOTE: Statzone 10 donated to Florida**
+
 ```{r load data}
@@
          Season = factor(season, levels = c("Summer", "Fall")),
+         region = ifelse(statzone == 10, "Florida", region),
          region = ifelse(region == "Louisiana", "LA West", region),
@@
 overall_foa   <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3) * 100
-overall_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
 percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
 station_count <- seamap_west %>% count()
+overall_mean  <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
+overall_se    <- round(sd(seamap_west$cpue_towspd, na.rm = T) / sqrt(station_count), 3)
 
@@
 
+ * Overall Standard Error `r overall_se`
+
  * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%
@@
 station_count <- seamap %>% count()
+overall_se    <- round(sd(seamap$cpue_towspd, na.rm = T) / sqrt(station_count), 3)
 
@@
  * Overall Mean Catch Crabs/Hectare: `r overall_mean`
+
+ * Overall Standard Error `r overall_se`
 

### 2020-03-06 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
put manuscript figures in folder

@@
 
-year_plot + year_foa
+figure_4 <- year_plot + year_foa
 
+figure_4
+
+ggsave(figure_4, 
+       filename = here::here("2019_edits/R/offshore_analyses/final_analyses/manuscript_figs", "Figure4.tiff"), 
+       height = 4, 
+       device = "tiff")
 ```
@@
 rs_plot_full <- rs_plot_3 + theme(legend.position = "none")
-rs_plot_full + rs_plot_4
+figure_3 <- rs_plot_full + rs_plot_4
+
+figure_3
+
+ggsave(figure_3, 
+       filename = here::here("2019_edits/R/offshore_analyses/final_analyses/manuscript_figs", "Figure3.tiff"), 
+       height = 4, 
+       device = "tiff")
 ```
@@
 
+#Savie it
+ggsave(p, 
+       filename = here::here("2019_edits/R/offshore_analyses/final_analyses/manuscript_figs", "Figure5.tiff"), 
+       device = "tiff")
+
 ```
@@
 
-ggplot() +
+sz_plot <- ggplot() +
   geom_sf(data = szones, fill = NA) +
@@
     pad_x = unit(0.5, "in"))
+
+sz_plot
+
+# Export
+ggsave(sz_plot, 
+       filename = here::here("2019_edits/R/offshore_analyses/final_analyses/manuscript_figs", "Figure1.tiff"), 
+       height = 4, 
+       device = "tiff")
 ```
